### 2018-01-23 article.tex
1添加了标题和作者信息 2添加了摘要

\documentclass[preprint,12pt]{elsarticle}

\usepackage{amssymb}

\journal{Nuclear Physics B}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{A novel 1000MW double reheat ultra supercritical system with turbine–extraction-heated air preheaters and low temperature economizers}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \address[label1]{}
%% \address[label2]{}

\author[rvt]{Lei Zhang}
\ead{zhanglei@ncst.edu.cn}	
\author[focal]{Tao Yang\corref{cor1}}
\ead{taoyang@hust.edu.cn}

\address[rvt]{River Valley Technologies, SJP Building,Cotton Hills, Trivandrum, Kerala, India 695014}
\address[focal]{River Valley Technologies, 9, Browns Court,Kennford, Exeter, United Kingdom}
\cortext[cor1]{Corresponding authors}

\begin{abstract}
%% Text of abstract
Herein, an optimization system of a 1000\,MW double-reheat ultra-supercritical (USC) unit with turbine–extraction-heated air preheaters (EAPHs), which use turbine extractions as heat sources of air preheaters while economizer outlet flue gas’ heat absorbed by low-pressure economizers (LPEs), is designed based on a 1000-MW double-reheat USC unit (reference system). The energetic performance analyses of the USC system with EAPH and reference system are used to compare their major parameters. In addition, thermodynamic analyses under partial load operation conditions are presented . The results show that the proposed system reduced the exergy loss in the air-heating and flue gas-cooling processes. Furthermore, the optimization system increases the temperature of secondary air and reduces the overall superheat degree of several extractions. Theoretically, the proposed system reduces the standard coal equivalent (SCE) consumption by nearly 5.5\,g/kWh under THA load when the temperature of the flue gas entering the electrostatic precipitator is set to 95$^\circ$C. Moreover, the proposed system can still reduce SCE consumption by 2.9\,g/kWh under the condition of 50\% THA load. Our findings indicate that system with APOB could improves the performance of the unit and may provide a theoretical basis for the optimization of double-reheat USC units.
\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword

%% PACS codes here, in the form: \PACS code \sep code

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
Double reheat \sep Ultra-supercritical power plant \sep Exergy analysis \sep System Optimization \sep Thermodynamic analyses
\end{keyword}

\end{frontmatter}

%% \linenumbers

%% main text
\section{section1}
dsadsadsadadsas\cite{Brooks1983CHARMM}
\label{}

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

%% If you have bibdatabase file and want bibtex to generate the
%% bibitems, please use
%%
%%  \bibliographystyle{elsarticle-harv} 
%%  \bibliography{<your bibdatabase>}

%% else use the following coding to input the bibitems directly in the
%% TeX file.

%\begin{thebibliography}{00}

%% \bibitem[Author(year)]{label}
%% Text of bibliographic item

%
\section{References}
\section*{Acknowledgement}
This is the 
\clearpage
\section*{References}
\bibliographystyle{elsarticle-num}
\bibliography{1}
%\end{thebibliography}
\end{document}

\endinput
%%
%% End of file `elsarticle-template-harv.tex'.

### 2018-01-25 article.tex
1完善到table2 2系统介绍部分的用分析删除，以后修改成更清晰的热力学第一定律分析方式 3添加了很多elsver的package和前定义，但被注释掉了

@@
 
-\usepackage{amssymb}
+\usepackage{amssymb,hyperref,booktabs,multirow}
+% \usepackage{graphicx}%插入图片
 
-\journal{Nuclear Physics B}
+% \usepackage{amssymb}%数学符号
+
+% \usepackage{amsthm}%数学定理
+
+% \usepackage{amsmath}%数学公式、矩阵、积分求和等
+
+% \usepackage{lineno}%显示行号
+
+% \usepackage{txfonts}%默认字体times new roman
+
+% \usepackage{enumitem}%项目编号
+
+% \usepackage{multirow}%多行合并
+
+% \usepackage{caption}%改变图表标题
+
+% \usepackage{array}%调用公式宏包的命令应放在调用宏包命令之前，也能控制表格
+
+% \usepackage{booktabs}%调整表格线与上下内容的间隔
+
+% \usepackage{longtable}%调用跨页表格
+
+% \usepackage{bm}%数学字体加粗
+
+% \usepackage{setspace}%调整一段文字的行间距
+
+% \usepackage{natbib}%参考文献管理包​
+% \biboptions{sort&compress}%参考文献可以压缩显示比例​
+
+% \allowdisplaybreaks[4]%允许公式跨页
+
+% \captionsetup[figure]{font=small,labelfont=bf,labelsep=period}%修改标题文字格式
+
+% \renewcommand{\figurename}{Fig.}%修改标题样式
+
+% \newcommand{\tabincell}[2]{}%让表格内容自动换行，但仍然需要用到换行\\
+
+\journal{Energy Conversation and Management}
 
@@
 
-%% Title, authors and addresses
+\title{A novel 1000\,\,MW double-reheat ultra supercritical system with turbine-extraction-heated air preheaters and low temperature economizers}
 
-%% use the tnoteref command within \title for footnotes;
-%% use the tnotetext command for theassociated footnote;
-%% use the fnref command within \author or \address for footnotes;
-%% use the fntext command for theassociated footnote;
-%% use the corref command within \author for corresponding author footnotes;
-%% use the cortext command for theassociated footnote;
-%% use the ead command for the email address,
-%% and the form \ead[url] for the home page:
-%% \title{Title\tnoteref{label1}}
-%% \tnotetext[label1]{}
-%% \author{Name\corref{cor1}\fnref{label2}}
-%% \ead{email address}
-%% \ead[url]{home page}
-%% \fntext[label2]{}
-%% \cortext[cor1]{}
-%% \address{Address\fnref{label3}}
-%% \fntext[label3]{}
+\author[hust,ncst]{Lei Zhang}
+\ead{zhanglei@ncst.edu.cn}	
+\author[hust]{Tao Yang\corref{cor1}}
+\ead{hust\_yt@hust.edu.cn}
 
-\title{A novel 1000MW double reheat ultra supercritical system with turbine–extraction-heated air preheaters and low temperature economizers}
-
-%% use optional labels to link authors explicitly to addresses:
-%% \author[label1,label2]{}
-%% \address[label1]{}
-%% \address[label2]{}
-
-\author[rvt]{Lei Zhang}
-\ead{zhanglei@ncst.edu.cn}	
-\author[focal]{Tao Yang\corref{cor1}}
-\ead{taoyang@hust.edu.cn}
-
-\address[rvt]{River Valley Technologies, SJP Building,Cotton Hills, Trivandrum, Kerala, India 695014}
-\address[focal]{River Valley Technologies, 9, Browns Court,Kennford, Exeter, United Kingdom}
+\address[hust]{School of Energy and Power Engineering, Huazhong University of Science and Technology, Wuhan 430074,China}
+\address[ncst]{College of Metallurgy and Energy, NorthChina University of Scienceand and Technology, Tangshan 063009,China}
 \cortext[cor1]{Corresponding authors}
@@
 \begin{abstract}
-%% Text of abstract
-Herein, an optimization system of a 1000\,MW double-reheat ultra-supercritical (USC) unit with turbine–extraction-heated air preheaters (EAPHs), which use turbine extractions as heat sources of air preheaters while economizer outlet flue gas’ heat absorbed by low-pressure economizers (LPEs), is designed based on a 1000-MW double-reheat USC unit (reference system).
-The energetic performance analyses of the USC system with EAPH and reference system are used to compare their major parameters.
-In addition, thermodynamic analyses under partial load operation conditions are presented .
-The results show that the proposed system reduced the exergy loss in the air-heating and flue gas-cooling processes.
-Furthermore, the optimization system increases the temperature of secondary air and reduces the overall superheat degree of several extractions.
-Theoretically, the proposed system reduces the standard coal equivalent (SCE) consumption by nearly 5.5\,g/kWh under THA load when the temperature of the flue gas entering the electrostatic precipitator is set to 95$^\circ$C.
-Moreover, the proposed system can still reduce SCE consumption by 2.9\,g/kWh under the condition of 50\% THA load.
-Our findings indicate that system with APOB could improves the performance of the unit and may provide a theoretical basis for the optimization of double-reheat USC units.
+Herein, an novel system of a 1000\,\,MW double-reheat ultra-supercritical (USC) unit with turbine-extraction-heated air preheaters (EAPHs), which use turbine extractions as heat sources of air preheaters while economizer outlet flue gas’ heat absorbed by low pressure economizers (LPEs), is designed based on reference system of a 1000\,\,MW double-reheat USC unit.
+The energetic performance analyses of the novel system and reference system are used to compare their major parameters. 
+In addition, thermodynamic analyses under partial load operation conditions are presented. 
+The results show that the proposed novel system reduced the exergy loss in the air-heating processes.
+Furthermore, the novel system increases the temperature of secondary air and reduces the overall superheat degree of several extractions.
+ Theoretically, the novel system reduces the SCE consumption by nearly 5.5\,g/kWh under THA load when the temperature of the flue gas entering the electrostatic precipitator is set to 95$^\circ$C.
+ Moreover, the novel system can still has advantages in coal saving under partial load condition.
+ Our findings indicate that system with EAPH could improves the performance of the unit and may provide a theoretical basis for the novel of double-reheat USC units.
 \end{abstract}
@@
 \begin{keyword}
-%% keywords here, in the form: keyword \sep keyword
-
-%% PACS codes here, in the form: \PACS code \sep code
-
-%% MSC codes here, in the form: \MSC code \sep code
-%% or \MSC[2008] code \sep code (2000 is the default)
-Double reheat \sep Ultra-supercritical power plant \sep Exergy analysis \sep System Optimization \sep Thermodynamic analyses
+Double reheat \sep Ultra-supercritical power plant \sep Exergy analysis \sep System novel \sep Thermodynamic analyses
 \end{keyword}
@@
 
-%% \linenumbers
+\section{Introduction}
+\label{sec:1}
+Coal is still the main fossil fuel resources for electricity production in the world according to~\cite{Ouedraogo2013Energy}. 
+In China, coal –fired power generation accounts for more than 70\% of the total electricity generation and subsequently contribute almost 50\%, 37\%, 33\% and 55\% to the SO$_X$, NO$_X$, dust and CO$_X$ emission volumes respectively~\cite{Zhang2010Analysis}.
+Statics show that China has been the largest producer and consumer of energy all over the world since 2013 [??]. 
+For 2016 as a whole, Chinese coal production fell by 7.9\% and the price of steam coal increased by over 60\%[??]. 
+Improve system efficiency and reducing coal consumption is still the main task of power plant design.
+Nowadays, ultra-supercritical (USC) power plants with large capacity and high parameter are considered to be feasible means to save energy and have rapidly developed word-wide.
+The double reheat USC unit is a new generation of USC unit which can improve the thermal performance compared with single reheat units~\cite{Zhao2017Exergy}. 
+According to Ref.~\cite{Yaxiu2013Thermal}, a double reheat unit with the inlet parameter 30.0\,MPa/600/620/620$^\circ$C improves the heat efficiency by 2.4\%-2.6\%, compared with a common used USC unit with the inlet parameter 25.0\,MPa/600/600$^\circ$C.
+ The U.S. built the first double reheat unit with main parameter 34.4 MPa/649/566/566$^\circ$C in 1960s.
+ Two 700 MW double reheat USC units in Japan were put into operation in 1990. 
+ The Taizhou power plant in China began to build double reheat USC units in 2012, and put it into operation in 2015.
+ Over the past few decades, the double reheat USC units have received more and more attention for its rapid development all over the world.
+Zhao Z et al.~\cite{Zhao2017Exergy} studied the exergy distribution system for a 1000\,MW double reheat USC power plant and provided the main reasons that led to exergy loss on the steam turbine.
+ Rashidi et al.~\cite{Rashidi2014Thermodynamic} investigated the thermodynamic analysis of a double reheat steam power plant.
+ According to Ref.~\cite{Wu2014Component}, component and process based exergy evaluation was performed on a coal-fired power plant in China, which provides guidance for energy-saving strategies.
+ It pointed out that the exergy loss in the heat transfer process accounts for the largest proportion.
 
-%% main text
-\section{section1}
-dsadsadsadadsas\cite{Brooks1983CHARMM}
-\label{}
+ Though the high live steam pressure and temperature of USC unit improves its efficiency, there are still some imperfections which limit the improvement of its performance .
 
-%% The Appendices part is started with the command \appendix;
-%% appendix sections are then done as normal sections
-%% \appendix
+For example, the double-reheat system causes great superheat degree of the first several extractions and the boiler exhaust temperature is extremely high, which leads to unreasonable energy-level matching and great exergy loss.
 
-%% \section{}
-%% \label{}
+To reduce the superheat degree of the extractions, Liu et al.
+[??] investigated the thermal performance of the steam and water cycle with single reheat after the installation of an additional outer steam cooler (AOC).
+Results show that the AOC is an effective method to reduce the superheat degree and improve the efficiency of the unit.
+Besides, Kjaer~\cite{Kjaer2010A} proposed a regenerative steam turbine to utilize the superheat degree of the extractions.
+In this design, part of the extraction from the high pressure turbine enters the additional regenerative steam turbine not the regenerative heater.
+Extractions from the intermediate pressure turbine are replaced by those from the regenerative steam turbine.
+The superheat degree of the extraction is significantly reduced in this design, and the exergy destruction of regenerative heaters is reduced, which results in an overall improvement in efficiency.
 
-%% If you have bibdatabase file and want bibtex to generate the
-%% bibitems, please use
-%%
-%%  \bibliographystyle{elsarticle-harv} 
-%%  \bibliography{<your bibdatabase>}
+To reuse the energy of the exhaust flue gas Ref.~\cite{Xu2013Techno} proposed a low pressure economizer (LPE) based on the data of some 1000\,MW typical power generation units in China and four possible arrangements of the LPE installation were proposed to compare its energy-saving effects.
+Results indicated that LPE connected with higher temperature section of the condensate line brings more reduction of standard coal equivalent (SCE).
+Wang et al.~\cite{Wang2012Application} investigated the energy and water saving and the reduction of CO$_2$ after the installation of LPE.
+Results show that the optimized measures can bring a reduction of SCE by 2-4\,g/kWh.
+Stevanovic et al.~\cite{Stevanovic2014Efficiency} proposed an additional high pressure economizer installed at a long term running lignite-fired power plant.
+Results show that more than 30\,MW of the flue gas waste heat is recovered, which brings an improvement in gross efficiency by 0.53\% and 9.4\,MW extra output power.
+In Ref. [??], the air preheater is divided into two stages to reduce the temperature difference in heat transfer process.
+Besides, a LPE is installed between the two air preheaters to obtain an appropriate flue gas temperature range.
+Thermodynamic and Technic-economic analysis are conducted to reveal the performance improvement.
+It was found that the SCE consumption can be reduced by 6.7\,g/kWh.
 
-%% else use the following coding to input the bibitems directly in the
-%% TeX file.
+Due to arrangement of boiler heating surface and design of regenerative system belong to deferent research area, researches concentrate more on the optimization of these two systems respectively, and ignored the joint optimization of boiler tail flue heating surface and regenerative system to achieve energy cascade utilization and improve system efficiency.
+To reduce both systems' exergy loses, a theoretical optimization design of cascaded utilization of energy for a 1000\,MW double reheat USC unit (novel system) is proposed.
+Variations and energy saving effects of a double reheat ultra-supercritical thermal system (reference system) and the novel system are analyzed to evaluate their performance.
 
-%\begin{thebibliography}{00}
+\section{Reference system introduction and analysis}
+\label{sec:2}
+\subsection{Introduction of reference system} % (fold)
+\label{sub2:intro}
 
-%% \bibitem[Author(year)]{label}
-%% Text of bibliographic item
+% subsection subsection_name (end)
 
-%
-\section{References}
-\section*{Acknowledgement}
-This is the 
-\clearpage
+A typical coal-fired double reheat USC power plant in operation is chosen as the reference unit.
+The parameter settings that maximize continuous power are 310\,bar/600$^\circ$Cfor the main steam, 610$^\circ$C for the reheat steam pressure, 33.5\% for the proportion of the single reheat steam pressure to the main steam pressure, and 33\% for the proportion of the double reheat steam pressure to the single reheat steam pressure[6].
+The output power of the double reheat unit under the condition of THA load is 1000 MW.
+The unit consists of one super high pressure turbine (VHP), one high pressure turbine (HP), one intermediate pressure turbine (IP), and two low pressure turbines (LP).
+10-stage regenerative system with four high pressure regenerative heaters (HRH), five low pressure regenerative heaters (LRH), and one deaerator (DEA) are adopted.
+Besides two additional outer steam coolers (AOC1, AOC2) are used to cool two extractions due to its high super-heating degree.
+The exhaust steam pressure of the steam turbine is set 4.5\,kPa.
+The simplified schematic of the unit is presented in Fig~\ref{fig:reference_system}.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=0.9\textwidth]{fig/reference_system}
+\caption{Schematic of the reference system} 
+\label{fig:reference_system}
+\end{figure}
+%从参考系统的锅炉虽然仍然采用Π型布置，但其内部受热面和传统一次再热锅炉有较大区别。
+Furnace layout shown in Fig~\ref{fig:boiler_surface}, the boiler furnace is composited by the membrane wall, along flue gas flow direction lays low-temperature superheater (Lts) screen tube, cold segment of high-temperature ﬁrst reheater (Csf), cold segment of high-temperature second reheater (Csf), High temperature super-heater (Hts), hot segment of high-temperature ﬁrst reheater (Hsf), hot segment of high-temperature second reheater (Hss).
+After Hsf and Hss the flue gas channel is divided into the front-duct flue and the back-duct flue.
+The front duct arranges low-temperature first reheater (Ltfr) and the front-duct economizerz (Feco), the back duct arranges a low-temperature second reheater (Ltsr) and back-duct economizer (Beco).
+The rear flue is equipped with an air preheater(APH).
+% 从锅炉受热面布置可以看出，锅炉主要受热面布置在炉膛之中，而水平烟道和竖井烟道中仅布置有空气预热设备。所以锅炉可以分成两部分:炉膛内完成水/蒸汽吸热的boiler，和尾部烟道内 完成空气预热的APH。
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=0.5\textwidth]{fig/boiler_surface}
+\caption{Boiler internal heat exchangers layout} 
+\label{fig:boiler_surface}
+\end{figure}
+
+\subsection{Thermal performance evaluation of reference system} % (fold)
+\label{sub2:eval}
+The main  parameters of the reference system are shown in Table~\ref{tab:ref input}.
+
+\begin{table}[htbp]
+\caption{The main input parameter of reference system }
+\label{tab:ref input}
+\centering
+
+\begin{tabular}{lll}
+\toprule 
+Items & Unit & Value\tabularnewline
+\midrule
+Live steam mass flow rate          	&t/h  &2533  			\\
+Second reheater  		&Mass flow   	&2002\,t/h \tabularnewline
+                     	& Pressure 	     &311.4\,bar 			&Second reheater inlet	&Pressure     	&3.29\,bar \tabularnewline
+                     	& Temperature    &605$^\circ$C      	&  						&Temperature  	&433$^\circ$C \tabularnewline
+First reheater      	&Mass flow       &2318\,t/h  			&Second reheater outlet	&Pressure     	&3.05\,bar \tabularnewline
+First reheater inlet	& Pressure       &105.3\,bar 			&  						&Temperature  	&613$^\circ$C \tabularnewline
+                     	&Temperature     &427$^\circ$C      	&Feedwater  			&Temperature 	&314$^\circ$C \tabularnewline
+First reheater outlet	&Pressure        &103.2\,bar 			&Turbine exhaust 		&pressure 		&4.5 kPa \tabularnewline
+                     	& Temperature    &6137$^\circ$C 		& 						&  				& \tabularnewline
+\bottomrule
+\end{tabular}	
+\end{table}
+
+Table 2 gives the temperature profiles and exergy efficiency of regenerative heaters and the air preheater, revealing the energy match level of heat exchangers.
+For the air preheater, the temperature of flue gas at the inlet of the air preheater is 376$^\circ$C under THA condition, while the temperature of the air to be heated by the flue is 25$^\circ$C, leading to the exergy loss of 27.17\,MW.
+The temperature difference of the air preheater is calculated to be 72$^\circ$C, and average temperature of the air is 177$^\circ$C, causing the exergy efficiency of 77.16\%.
+\begin{table}[htbp]
+\caption{fluid parameters of heat exchangers and air preheater}
+\label{tab:reheater parameter}
+\centering
+\small
+\begin{tabular}{ccccc}
+\toprule 
+\multirow{2}{2cm}{Components} & \multirow{2}{2cm}{Hot fluid pressure(bar)} &\multirow{2}{2.5cm}{Hot fluid temperature($^\circ$C)} & \multirow{2}{2.5cm}{Cold fluid temperature($^\circ$C)} & \multirow{2}{3.5cm}{Fluid temperature difference($^\circ$C)}\tabularnewline
+&&&&\tabularnewline
+\midrule
+APH &  & 376．00 & 23.00 & 353.00\tabularnewline
+AOC1 &  & 526.56 & 304.51 & 222.05\tabularnewline
+AOC2 &  & 527.48 & 304.51 & 222.97\tabularnewline
+HRH1 &  & 417.07 & 273.62 & 143.45\tabularnewline
+HRH2 &  & 314.53 & 240.73 & 73.8\tabularnewline
+HRH3 &  & 434.54 & 205.89 & 228.65\tabularnewline
+HRH4 &  & 316.51 & 186.48 & 130.03\tabularnewline
+DEA &  & 447.37 & 163.63 & 283.74\tabularnewline
+LRH6 &  & 394.01 & 140.46 & 253.55\tabularnewline
+LRH7 &  & 313.17 & 104.49 & 208.68\tabularnewline
+LRH8 &  & 191.84 & 82.42 & 109.42\tabularnewline
+LRH9 &  & 116.61 & 59.25 & 	57.36\tabularnewline
+\bottomrule
+\end{tabular}
+\end{table}
+\normalsize
+
 \section*{References}
 \bibliographystyle{elsarticle-num}
-\bibliography{1}
-%\end{thebibliography}
+
+\bibliography{bib/reference.bib}
+
 \end{document}
@@
 \endinput
-%%
-%% End of file `elsarticle-template-harv.tex'.
+\%\%
+\%\% End of file `article.tex'.

### 2018-01-25 article.tex
1修改了文章的结构改为先介绍两个系统 ，再建模 2完成到用分析部分

@@
 \usepackage{amssymb,hyperref,booktabs,multirow}
+\usepackage{enumerate}
+
 % \usepackage{graphicx}%插入图片
@@
 
-% \usepackage{amsmath}%数学公式、矩阵、积分求和等
+ \usepackage{amsmath}%数学公式、矩阵、积分求和等
 
@@
 \section{Introduction}
-\label{sec:1}
+\label{sec1:intro}
 Coal is still the main fossil fuel resources for electricity production in the world according to~\cite{Ouedraogo2013Energy}. 
@@
 
-\section{Reference system introduction and analysis}
-\label{sec:2}
-\subsection{Introduction of reference system} % (fold)
-\label{sub2:intro}
-
-% subsection subsection_name (end)
-
+\section{System optimization of double reheat USC system}
+\label{sec2:system intro}
+\subsection{reference system on operation} % (fold)
+\label{sub2:ref intro}
 A typical coal-fired double reheat USC power plant in operation is chosen as the reference unit.
@@
 
-\subsection{Thermal performance evaluation of reference system} % (fold)
-\label{sub2:eval}
 The main  parameters of the reference system are shown in Table~\ref{tab:ref input}.
@@
 \centering
-
 \begin{tabular}{lll}
@@
  Live steam mass flow rate 	    	&t/h 			&2533 \\
-Second reheater  		&Mass flow   	&2002\,t/h \tabularnewline
-                     	& Pressure 	     &311.4\,bar 			&Second reheater inlet	&Pressure     	&3.29\,bar \tabularnewline
-                     	& Temperature    &605$^\circ$C      	&  						&Temperature  	&433$^\circ$C \tabularnewline
-First reheater      	&Mass flow       &2318\,t/h  			&Second reheater outlet	&Pressure     	&3.05\,bar \tabularnewline
-First reheater inlet	& Pressure       &105.3\,bar 			&  						&Temperature  	&613$^\circ$C \tabularnewline
-                     	&Temperature     &427$^\circ$C      	&Feedwater  			&Temperature 	&314$^\circ$C \tabularnewline
-First reheater outlet	&Pressure        &103.2\,bar 			&Turbine exhaust 		&pressure 		&4.5 kPa \tabularnewline
-                     	& Temperature    &6137$^\circ$C 		& 						&  				& \tabularnewline
+ Live steam pressure 		    	&bar 			&310\\
+ Live steam temperature		     	&$^\circ$C		&600		\\
+ First reheat steam pressure    	&bar			&100.9		\\
+ First reheat steam temperature  	&$^\circ$C		&610		\\
+ Second reheat steam pressure    	&bar			&30.8		\\
+ Second reheat steam temperature 	&$^\circ$C		&610		\\
+ Power generation output 			&MW				&1000		\\
 \bottomrule
@@
 \end{table}
-
 Table 2 gives the temperature profiles and exergy efficiency of regenerative heaters and the air preheater, revealing the energy match level of heat exchangers.
@@
 \centering
-\small
-\begin{tabular}{ccccc}
+\begin{tabular}{cccc}
 \toprule 
-\multirow{2}{2cm}{Components} & \multirow{2}{2cm}{Hot fluid pressure(bar)} &\multirow{2}{2.5cm}{Hot fluid temperature($^\circ$C)} & \multirow{2}{2.5cm}{Cold fluid temperature($^\circ$C)} & \multirow{2}{3.5cm}{Fluid temperature difference($^\circ$C)}\tabularnewline
-&&&&\tabularnewline
+\multirow{2}{2cm}{Components} &\multirow{2}{2.7cm}{Hot fluid temperature($^\circ$C)}  & \multirow{2}{2.7cm}{Cold fluid temperature($^\circ$C)}&  \multirow{2}{2.5cm}{LMTD($^\circ$C)}\tabularnewline
+&&&\tabularnewline
 \midrule
-APH &  & 376．00 & 23.00 & 353.00\tabularnewline
-AOC1 &  & 526.56 & 304.51 & 222.05\tabularnewline
-AOC2 &  & 527.48 & 304.51 & 222.97\tabularnewline
-HRH1 &  & 417.07 & 273.62 & 143.45\tabularnewline
-HRH2 &  & 314.53 & 240.73 & 73.8\tabularnewline
-HRH3 &  & 434.54 & 205.89 & 228.65\tabularnewline
-HRH4 &  & 316.51 & 186.48 & 130.03\tabularnewline
-DEA &  & 447.37 & 163.63 & 283.74\tabularnewline
-LRH6 &  & 394.01 & 140.46 & 253.55\tabularnewline
-LRH7 &  & 313.17 & 104.49 & 208.68\tabularnewline
-LRH8 &  & 191.84 & 82.42 & 109.42\tabularnewline
-LRH9 &  & 116.61 & 59.25 & 	57.36\tabularnewline
+APH  &  376.00 	& 23.00  & 72.4\tabularnewline
+AOC1 &   526.56 & 304.51 & 69.75\tabularnewline
+AOC2 &  527.48 	& 304.51 & 60.81\tabularnewline
+HRH1 &   417.07 & 273.62 & 10.64\tabularnewline
+HRH2 &   314.53 & 240.73 & 10.77\tabularnewline
+HRH3 &   434.54 & 205.89 & 12.68\tabularnewline
+HRH4 &   316.51 & 186.48 & 6.88\tabularnewline
+LRH6 &  394.01 	& 140.46 & 13.19\tabularnewline
+LRH7 &   313.17 & 104.49 & 15.87\tabularnewline
+LRH8 &   191.84 & 82.42  & 9.82\tabularnewline
+LRH9 &   116.61 & 59.25  & 10.03\tabularnewline
 \bottomrule
@@
 \end{table}
-\normalsize
 
+Compared with the air preheater, the regenerative heaters have lower logarithm mean temperature difference (LMTD).
+However, it is found that the temperature difference between the hot and cold stream at the inlet high temperature regenerative heaters is also relatively large, which causes irreversible loss.
+To reduce the superheat degree of the 2nd and 4th extractions and to heat feedwater, two additional outer steam coolers are installed.
+Results show that the inlet temperature difference of HRH2 and HRH4 is greatly reduced, and the exergy efficiency is improved correspondingly.
+However, the inlet temperature difference between the cold and hot stream of other high temperature regenerative heaters remains very high.
+Moreover, because of the material restriction of the water wall, the temperature of feedwater at the inlet of boiler is restricted to 315$^\circ$C. 
+In the reference system, the first extraction has to be throttled to ensure the temperature of feedwater not exceeding the restriction.
+The pressure of the first extraction is throttled from 106.70 bar to 88.56 bar, and the temperature is decreased from 425.60$^\circ$C to 413.77$^\circ$C.
+The throttling of the first extraction will certainly cause extra irreversible loss.
+%2.2
+\subsection{Proposal of a novel system with EAPH and LPE}
+\label{sub2:prop novel sys}
+
+The  layout of the optimization system is presented in Fig~\ref{fig:novel_system}.
+In the optimization system, the air is not heated by flue gas in the conventional air preheater, and 8 new air preheaters (APH1\-APH8) using several extractions to heat the air is adopted.
+The new air preheater is similar with regenerative heaters in function.
+As shown in Fig~ the extracted steam is sent to the regenerative heater to heat the condensate or feedwater, and then the drainage from the air preheater joins with that of corresponding regenerative heater.
+It should be mentioned that not all the extractions are available for air heating
+For the last two stage extractions, their pressure is much lower than barometric pressure which makes it extremely difficult to maintain such low pressure environment inside the heat exchangers, and APH8 shall be shut down under low load for the same reason.
+Besides, to reduce the superheat degree of extractions entering the heat exchangers and to improve the air temperature, four additional outer steam coolers (AOC1- AOC4) are installed at the outlet of APH1.
+Since extractions from the 2nd to the 5th have superheat degree, they are sent to AOCs in the order of temperature level.
+For example, the 2nd extraction has the highest temperature, and is applied to heat the air in the 1st AOC, and then the cooled steam from AOC1 is sent to HRH2 and air APH2 to heat the water and air respectively.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=0.9\textwidth]{fig/novel_system}
+\caption{Schematic of the novel system} 
+\label{fig:novel_system}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=0.3\textwidth]{fig/extraction_heat_APH}
+\caption{Process flow diagram of RH and APH} 
+\label{fig:extraction_heat_APH}
+\end{figure}
+As shown in Fig~\ref{fig:novel_system}, the flue gas at the outlet of economizer is utilized to heat the condensate and feed water by four LPEs, which are paralleled to HRH2, HRH4, LRH6, and LRH8 respectively.
+Part of the condensate and feed water at the inlet of regenerative heater are sent to the LPE, then the heated water join with the main feedwater/condensate. 
+Considering the acid dew point temperature, the flue gas temperature at the outlet of the last LPE is set 95℃. 
+The temperature of heated water from LPE is set little higher than the feedwater from the corresponding regenerative heater.%
+
+\section{Model establishment and thermodynamic evaluation} % (fold)
+\label{sec3:modle est and eval}
+\subsection{Model description and system analysis method} % (fold)
+\label{ssub:model_establishment_and_system_analysis_method}
+
+\subsubsection{Model establish method and main assumption}
+\label{ssub3:modle description}
+In this paper, the thermodynamic cycle of the thermal system under different loads are simulated with EBSILON® Professional for its flexibility and level of detail. 
+EBSILON is a power plant simulation tool which can calculate thermodynamic quantities. 
+The simulation model gives the detailed data with high degree of reliability to calculate the thermodynamic state.
+EBSIOLON's simulation and parameter calculation of the equipment is based on experimental characteristics of units during the process of modeling design and off-design conditions.
+However, only some characteristic curves of turbine can actually be obtained, while boiler and heat exchanger data cannot be obtained, which can only use the system built-in data as an alternative.
+It’s needed to assume that the difference between the built-in data and the actual data to meet the error requirements.
+The following assumptions need to be made in order to be able to simulate correctly.
+\begin{enumerate}[(1)]
+\item Both novel and reference systems are operated in stable condition
+\item The thermal efficiency of the equipment is calculated from the thermal balance of the input and output parameters of the components, assuming that the calculation error requirement can be met.
+\item According to the heat map, set the upper and lower end difference of the heat exchanger as a fixed value, and do not change among different condition.
+\item  Do not take the pips' complexity and equipment’s installation difficulty of the novel system as consideration.
+\end{enumerate}
+
+\subsubsection{System analysis method} %(fold)
+\label{ssub3:analsys method} 
+%为了能够对优化系统与参考系统进行评估，揭示系统优化的内在机理，本文引入热力学第二定律的分析方法即用分析方法。
+Exergy analysis, is adopted to reveal the location, the magnitude and the sources of thermodynamic inefficiencies of the unit.
+Usually, exergy loss and exergy efficiency are chosen as evaluation indices of the thermal system or an individual component, 
+The general exergy balance of component can be expressed in the following form:
+\begin{equation}
+\dot{I}=\sum\dot{E}{}_{in}-\sum\dot{E}{}_{out}+\sum\dot{W}{}_{in}-\sum\dot{W}{}_{out}
+\end{equation}
+\begin{equation}
+\eta=\frac{\dot{E}{}_{earned}}{\dot{E}{}_{cost}}
+\end{equation}
+
+% subsubsection subsubsection_name (end)
 \section*{References}

### 2018-01-25 article.tex
用效率表格还未完成

@@
 \label{sec2:system intro}
-\subsection{reference system on operation} % (fold)
+\subsection{Reference system on operation} % (fold)
 \label{sub2:ref intro}
@@
 \begin{equation}
+\label{equation:1}
 \dot{I}=\sum\dot{E}{}_{in}-\sum\dot{E}{}_{out}+\sum\dot{W}{}_{in}-\sum\dot{W}{}_{out}
 \end{equation}
+Exergy efficiency can be calculated in the following form:
 \begin{equation}
+\label{equation:2}
 \eta=\frac{\dot{E}{}_{earned}}{\dot{E}{}_{cost}}
 \end{equation}
+For different equipment under stable operating conditions, equation~\ref{equation:1}~\ref{equation:2} have different forms as shown in Table 5~\cite{}
+For flue gas, air, water and steam, the specific exergy can be calculated by equation~\ref{equation:3}.
+
+\begin{equation}{}
+\label{equation:3}
+e=h-h_{0}-T_{0}\left(s-s_{0}\right)
+\end{equation}
+Then the total exergy rate associated with ﬂuid stream becomes:
+\begin{equation}
+\dot{E}=\dot{m}e=\dot{m}\left[h-h_{0}-T_{0}\left(s-s_{0}\right)\right]{}
+\end{equation}
+The fuel speciﬁc exergy is calculated as[?]: 
+\begin{equation}
+e_{fuel}=LHV\left(1.0064+0.1519\frac{H}{C}+0.0616\frac{O}{C}+0.0429\frac{N}{C}\right)
+\end{equation}
+Where LHV refer to lower heating value of fuel, C, H, O, N refer to mass fractions of carbon, hydrogen, oxygen, nitrogen by element analysis.
+\begin{table}
+\caption{The exergy destruction rate and exergy efficiency equations for plant
+components}
+\label{table:exergy equation}
+\centering{}%
+\begin{tabular}{ccc}
+\toprule {}
+ & Exergy destruction rate & Exergy efficiency\tabularnewline
+\midrule
+Boiler &  & \tabularnewline
+Pumps &  & \tabularnewline
+Heaters &  & \tabularnewline
+Turbine &  & \tabularnewline
+Condenser &  & \tabularnewline
+Cycle &  & \tabularnewline
+\bottomrule
+\end{tabular}
+\end{table}
 

### 2018-01-26 article.tex
1添加了用分析公式表 2添加了新旧系统热力学参数对比表，表格调成左对齐模式

@@
 \centering
-\begin{tabular}{cccc}
+\begin{tabular}{llll}
 \toprule 
@@
 \end{equation}
-For different equipment under stable operating conditions, equation~\ref{equation:1}~\ref{equation:2} have different forms as shown in Table 5~\cite{}
+For different equipment under stable operating conditions, equation~\ref{equation:1}~\ref{equation:2} have different forms as shown in Table~\ref{tab:exergy equation}~\cite{Aljundi2009Energy}
 For flue gas, air, water and steam, the specific exergy can be calculated by equation~\ref{equation:3}.
@@
 \begin{table}
-\caption{The exergy destruction rate and exergy efficiency equations for plant
-components}
-\label{table:exergy equation}
-\centering{}%
-\begin{tabular}{ccc}
-\toprule {}
+\caption{Exergy analysis equations for plant components}
+\label{tab:exergy equation}
+\centering
+\begin{tabular}{lll}
+\toprule 
  & Exergy destruction rate  & Exergy efficiency\tabularnewline
 \midrule
-Boiler &  & \tabularnewline
-Pumps &  & \tabularnewline
-Heaters &  & \tabularnewline
-Turbine &  & \tabularnewline
-Condenser &  & \tabularnewline
-Cycle &  & \tabularnewline
+Boiler & $\dot{I}_{boiler}=\dot{E}{}_{fuel}+\dot{E}{}_{in}-\dot{E}{}_{out}$ & $\eta_{\uppercase\expandafter{\romannumeral2},boiler}=\frac{\dot{E}{}_{out}-\dot{E}{}_{in}}{\dot{E}{}_{fuel}}$\tabularnewline
+Pump & $\dot{I}_{pump}=\dot{E}{}_{in}-\dot{E}{}_{out}+\dot{W}{}_{pump}$ & $\eta_{\uppercase\expandafter{\romannumeral2},pump}=1-\frac{\dot{I}_{pump}}{\dot{W}{}_{pump}}$\tabularnewline
+Heater & $\dot{I}_{heater}=\dot{E}{}_{in}-\dot{E}{}_{out}$ & $\eta_{\uppercase\expandafter{\romannumeral2},heater}=1-\frac{\dot{I}_{heater}}{\dot{E}{}_{in}}$\tabularnewline
+Turbine & $\dot{I}_{turbine}=\dot{E}{}_{in}-\dot{E}{}_{out}-\dot{W}{}_{el}$ & $\eta_{\uppercase\expandafter{\romannumeral2},turbine}=1-\frac{\dot{I}_{turbine}}{\dot{E}{}_{in}-\dot{E}{}_{out}}$\tabularnewline
+Condenser & $\dot{I}_{condenser}=\dot{E}{}_{in}-\dot{E}{}_{out}+\dot{W}{}_{p}$ & $\eta_{\uppercase\expandafter{\romannumeral2},boiler}=\frac{\dot{E}{}_{out}}{\dot{E}{}_{in}+\dot{W}{}_{p}}$\tabularnewline
+Cycle & $\dot{I}_{cycle}=\sum_{all}\dot{I}_{i}$ & $\eta_{\uppercase\expandafter{\romannumeral2},cycle}=\frac{\dot{W}{}_{net,out}}{\dot{E}{}_{fuel}}$\tabularnewline
 \bottomrule
@@
 \end{table}
+
+\subsection{Thermodynamic performance evaluation} % (fold)
+\label{sub:Thermodynamic_evaluation}
+Based on the analysis of the reference system, the temperature difference of the heat exchangers is very high and exergy efficiency is rather low.
+Using turbine extractions to heat air can realize the reduce the heat transfer temperature difference and improve efficiency.
+The economizer outlet flue gas is used to heat low-temperature economizer can also reduce the loss of regenerative system.
+% In order to complete the heat balance calculation of the thermodynamic system, the key parameters in the novel system need to be set.
+% The novel system’s parameters are based on reference system, so the main parameters must be the same.
+The main parameters settled are including: superheat steam’s mass flow, pressure and temperature; First/second reheater’s inlet and outlet pressure and temperature; Turbine Exhaust pressure and temperature; turbine extraction’s pressure and temperature/ specific enthalpy etc.
+The main parameters settled under THA situation can be found in Table 1 and Table 4 .
+The results of exergy analysis of the optimization system are presented in Table 5.
+It is found that the optimization system has an improvement in exergetic performance.
+The total exergy loss of the cascaded utilization system is 1096.52 MW, which is 32.28 MW lower than the original.
+The new system also brings the improvement from 46.98\% to 47.99\%.
+Results show that the exergy loss of boiler is 855.72 MW, leading to the increment of exergy efficiency by 0.18\%.
+In addition, there is almost no change of the exergy parameters of the steam turbines, generator and condenser.
+For the air heating system and regenerative system, great change happens compared with the formal system, and detailed analysis will be carried out next.
+
+\begin{table}
+\caption{Thermodynamic performance of the reference and novel systems}
+\label{table:thermal performance compare}
+\centering
+\begin{tabular}{p{7.5cm}p{1.75cm}p{1.75cm}}
+\toprule 
+Items & Reference system & Novel system\tabularnewline
+\midrule
+Net generating power (MW) & 999.10 & 1011.19\tabularnewline
+Generating efficiency (\%) & 47.69 & 48.73\tabularnewline
+Addition in generating efficiency (\%) &  & 1.04\tabularnewline
+Standard coal consumption rate (g/kWh) & 257.59 & 252.10\tabularnewline
+Reduction in standard coal consumption rate (g/kWh) &  & 5.49\tabularnewline
+Exergy efficiency (\%) & 46.51 & 47.52\tabularnewline
+Addition in generating efficiency (\%) &  & 1.01\tabularnewline
+\bottomrule
+\end{tabular}
+\end{table}
+
+% subsubsection subsubsection_name (end)
 

### 2018-01-26 article.tex
修改到系统分析部分，接下来分析空预器 对分析部分进行修改1把系统间部件用损失对比从损失百分比换成损失量2把抽汽对比换成表、 对分析部分思路是：分析抽汽变化后分析空预系统和回热系统的参数损失变化 1空预系统和原系统的总损失和效率进行对比，指出最后一级空预器效率低的原因，并贴出烟温对比图 回热系统 2回热系统采用累计柱状图对其进行对，指出总用损失变化不大但是部分用损失有区别

@@
 \toprule 
-\multirow{2}{2cm}{Components} &\multirow{2}{2.7cm}{Hot fluid temperature($^\circ$C)}  & \multirow{2}{2.7cm}{Cold fluid temperature($^\circ$C)}&  \multirow{2}{2.5cm}{LMTD($^\circ$C)}\tabularnewline
+\multirow{2}{2cm}{Components} &\multirow{2}{2.7cm}{Hot fluid temperature($^\circ$C)}  & \multirow{2}{3.2cm}{Cold fluid temperature ($^\circ$C)}&\multirow{2}{2.5cm}{LMTD ($^\circ$C)}\tabularnewline
 &&&\tabularnewline
@@
 The main parameters settled under THA situation can be found in Table 1 and Table 4 .
-The results of exergy analysis of the optimization system are presented in Table 5.
-It is found that the optimization system has an improvement in exergetic performance.
-The total exergy loss of the cascaded utilization system is 1096.52 MW, which is 32.28 MW lower than the original.
-The new system also brings the improvement from 46.98\% to 47.99\%.
-Results show that the exergy loss of boiler is 855.72 MW, leading to the increment of exergy efficiency by 0.18\%.
-In addition, there is almost no change of the exergy parameters of the steam turbines, generator and condenser.
-For the air heating system and regenerative system, great change happens compared with the formal system, and detailed analysis will be carried out next.
+% 对于新旧系统表格的热力参数进行分析，下面这段话太少
 
@@
 \end{table}
+% 根据用损失对比表从新进行分析，从为什么锅炉空预器效率提高，其他不变或者降低说起
+The results of exergy analysis of the optimization system are presented in Table~\ref{table:system exergy campare}. 
+It is found that the optimization system has an improvement in exergetic performance.
+ The total exergy loss of the cascaded utilization system is 1096.52 MW, which is 32.28 MW lower than the original. 
+ The new system also brings the improvement from 46.98\% to 47.99\%. 
+ Results show that the exergy loss of boiler is 855.72 MW, leading to the increment of exergy efficiency by 0.18\%.
+In addition, there is almost no change of the exergy parameters of the steam turbines, generator and condenser.
+ For the air heating system and regenerative system, great change happens compared with the formal system, and detailed analysis will be carried out next.
 
+\begin{table}
+\caption{Systems' exergy destruction rate comparison }
+\label{table:system exergy campare}
+\centering
+\begin{tabular}{lll}
+\toprule 
+Items & Reference System\,(MW) & Novel System\,(MW)\tabularnewline
+\midrule 
+Boiler(without AP) & 883.26 & 872.22\tabularnewline
+Turbine & 63.33 & 63.97\tabularnewline
+Air Preheater  & 27.39 & 16.55\tabularnewline
+Regenerative system & 22.53 & 21.56\tabularnewline
+Other & 131.03 & 142.42 \tabularnewline
+Total & 1116.72 & 1127.54\tabularnewline
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}
+\label{table:extraction compare}
+\caption{Systems' extractions comparison}
+\begin{centering}
+\begin{tabular}{llll}
+\toprule 
+\multirow{2}{*}{Extractions} & \multirow{2}{2.5cm}{Reference system (kg/s)} & \multicolumn{2}{c}{Novel system (kg/s)}\tabularnewline
+\cmidrule{3-4} 
+ &  & to RHs & to APHs\tabularnewline
+\midrule
+1st & 54.47 & 43.79 & 15.42\tabularnewline
+2nd & 52.18 & 18.52 & 13.5\tabularnewline
+3rd & 37.86 & 31.71 & 14.62\tabularnewline
+4th & 20.53 & 5.66 & 9.5\tabularnewline
+5th & 11.95 & 9.78 & 5.67\tabularnewline
+6th & 19.94 & 9.88 & 7.83\tabularnewline
+7th & 30.19 & 14.16 & 12.85\tabularnewline
+8th & 16.31 & 3.11 & 27.1\tabularnewline
+9th & 18.93 & 18.93 & 0\tabularnewline
+10th & 20.61 & 20.6 & 0\tabularnewline
+Total & 282.97 & 176.14 & 106.49\tabularnewline
+\bottomrule
+\end{tabular}
+\par\end{centering}
+\end{table}
 % subsubsection subsubsection_name (end)

### 2018-01-27 article.tex
插入俩个图片

@@
 
+\usepackage{graphicx,float}
 % \usepackage{graphicx}%插入图片
@@
 
+Through the analysis of the reference system and the optimization system, it can be seen that the exergy efficiency of the optimization system is improved and the exergy loss is reduced.
+Comparing the proportion of different components in the total exergy loss between the two systems, we can see that in addition to the turbine, the exergy loss of all components is reduced. 
+Among them, the air preheating system efficiency is the most obviously improved，to 38.94\%.
+
 \begin{table}
@@
 \end{table}
-% subsubsection subsubsection_name (end)
+% 下面两段话需要根据图修改
+The variation of mass flow rate of extractions is presented in Fig 6.
+ Mass flow rate of the 1st, 3rd, 5th and 8th extractions of the optimization system is more than that of the base model, and the rest extractions except the last two, has the opposite variation. 
+ The impact of system optimization on extraction is twofold. 
+ Air is heated by extractions, which will cause an increment in mass flow. 
+ And the use of LPE can saves extractions.so the total extraction keeps unchanged.
+ Turbine total extraction steam volume change affect its exergy efficiency by 2.03\%.
+
+The air is heated by the staged air preheaters and additional outer steam coolers in the cascaded utilization system.
+ It can be seen from Table 5 that the total exergy loss of the air heating system is 16.35 MW, 10.82 MW lower than that of the original air preheater which is 27.17 MW. 
+ Fig 7 shows that the exergy efficiency of APHs and AOCs is higher than 82\%, except APH8.
+ For the air preheaters, the improvement in performance results from more reasonable energy utilization and the heat transform method. 
+ In the conventional air preheater, the air is heated by high temperature flue gas through convection. 
+ The working principle of the staged air preheaters in the optimization system is the same as regenerative heaters. 
+ The superheated vapor is firstly cooled to saturated steam through convection, then to saturated water through phase change heat transfer, and the latter process accounts for the main part. 
+ In this case, the temperature difference is greatly reduced, causing the improvement in performance.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=0.6\textwidth]{fig/APH_temper_compare.tif}
+\caption{T-q diagram of Air preheat subsystems} 
+\label{fig:APH_temper_compare}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=0.6\textwidth]{fig/novel_APH_exergy.tif}
+\caption{Exergy destruction and efficiency of air preheat subsystem of novel system} 
+\label{fig:novel_APH_exergy}
+\end{figure}
 

### 2018-01-27 article.tex
把visor图和origin图文件夹4进行合并
把变工况连个图给画完了。并保存了fig文件夹

@@
 
-\usepackage{graphicx,float}
+\usepackage{float}
+\usepackage{graphics}
 % \usepackage{graphicx}%插入图片
@@
 In addition, thermodynamic analyses under partial load operation conditions are presented. 
-The results show that the proposed novel system reduced the exergy loss in the air-heating processes.
+The results show that the proposed novel system reduced the exergy destruction in the air-heating processes.
 Furthermore, the novel system increases the temperature of secondary air and reduces the overall superheat degree of several extractions.
@@
  Over the past few decades, the double reheat USC units have received more and more attention for its rapid development all over the world.
-Zhao Z et al.~\cite{Zhao2017Exergy} studied the exergy distribution system for a 1000\,MW double reheat USC power plant and provided the main reasons that led to exergy loss on the steam turbine.
+Zhao Z et al.~\cite{Zhao2017Exergy} studied the exergy distribution system for a 1000\,MW double reheat USC power plant and provided the main reasons that led to exergy destruction on the steam turbine.
  Rashidi et al.~\cite{Rashidi2014Thermodynamic} investigated the thermodynamic analysis of a double reheat steam power plant.
  According to Ref.~\cite{Wu2014Component}, component and process based exergy evaluation was performed on a coal-fired power plant in China, which provides guidance for energy-saving strategies.
- It pointed out that the exergy loss in the heat transfer process accounts for the largest proportion.
+ It pointed out that the exergy destruction in the heat transfer process accounts for the largest proportion.
 
@@
 
-For example, the double-reheat system causes great superheat degree of the first several extractions and the boiler exhaust temperature is extremely high, which leads to unreasonable energy-level matching and great exergy loss.
+For example, the double-reheat system causes great superheat degree of the first several extractions and the boiler exhaust temperature is extremely high, which leads to unreasonable energy-level matching and great exergy destruction.
 
@@
 Table 2 gives the temperature profiles and exergy efficiency of regenerative heaters and the air preheater, revealing the energy match level of heat exchangers.
-For the air preheater, the temperature of flue gas at the inlet of the air preheater is 376$^\circ$C under THA condition, while the temperature of the air to be heated by the flue is 25$^\circ$C, leading to the exergy loss of 27.17\,MW.
+For the air preheater, the temperature of flue gas at the inlet of the air preheater is 376$^\circ$C under THA condition, while the temperature of the air to be heated by the flue is 25$^\circ$C, leading to the exergy destruction of 27.17\,MW.
 The temperature difference of the air preheater is calculated to be 72$^\circ$C, and average temperature of the air is 177$^\circ$C, causing the exergy efficiency of 77.16\%.
@@
 \centering
-\includegraphics[width=0.3\textwidth]{fig/extraction_heat_APH}
+\includegraphics[width=0.3\textwidth]{fig/extraction_heat_APH}%extraction_heat_APH
 \caption{Process flow diagram of RH and APH} 
@@
 \begin{enumerate}[(1)]
-\item Both novel and reference systems are operated in stable condition
+\item Both novel and reference systems are operated in stable condition.
 \item The thermal efficiency of the equipment is calculated from the thermal balance of the input and output parameters of the components, assuming that the calculation error requirement can be met.
@@
 Exergy analysis, is adopted to reveal the location, the magnitude and the sources of thermodynamic inefficiencies of the unit.
-Usually, exergy loss and exergy efficiency are chosen as evaluation indices of the thermal system or an individual component, 
+Usually, exergy destruction and exergy efficiency are chosen as evaluation indices of the thermal system or an individual component, 
 The general exergy balance of component can be expressed in the following form:
@@
 It is found that the optimization system has an improvement in exergetic performance.
- The total exergy loss of the cascaded utilization system is 1096.52 MW, which is 32.28 MW lower than the original. 
+ The total exergy destruction of the cascaded utilization system is 1096.52 MW, which is 32.28 MW lower than the original. 
  The new system also brings the improvement from 46.98\% to 47.99\%. 
- Results show that the exergy loss of boiler is 855.72 MW, leading to the increment of exergy efficiency by 0.18\%.
+ Results show that the exergy destruction of boiler is 855.72 MW, leading to the increment of exergy efficiency by 0.18\%.
 In addition, there is almost no change of the exergy parameters of the steam turbines, generator and condenser.
@@
 
-Through the analysis of the reference system and the optimization system, it can be seen that the exergy efficiency of the optimization system is improved and the exergy loss is reduced.
-Comparing the proportion of different components in the total exergy loss between the two systems, we can see that in addition to the turbine, the exergy loss of all components is reduced. 
+Through the analysis of the reference system and the optimization system, it can be seen that the exergy efficiency of the optimization system is improved and the exergy destruction is reduced.
+Comparing the proportion of different components in the total exergy destruction between the two systems, we can see that in addition to the turbine, the exergy destruction of all components is reduced.
 Among them, the air preheating system efficiency is the most obviously improved，to 38.94\%.
@@
 The air is heated by the staged air preheaters and additional outer steam coolers in the cascaded utilization system.
- It can be seen from Table 5 that the total exergy loss of the air heating system is 16.35 MW, 10.82 MW lower than that of the original air preheater which is 27.17 MW. 
+ It can be seen from Table 5 that the total exergy destruction of the air heating system is 16.35 MW, 10.82 MW lower than that of the original air preheater which is 27.17 MW. 
  Fig 7 shows that the exergy efficiency of APHs and AOCs is higher than 82\%, except APH8.
@@
 \centering
-\includegraphics[width=0.6\textwidth]{fig/APH_temper_compare.tif}
-\caption{T-q diagram of Air preheat subsystems} 
+\includegraphics[width=0.6\textwidth]{fig/APH_temper_compare.png}
+\caption{T-Q diagram of Air preheat subsystems} 
 \label{fig:APH_temper_compare}
@@
 \centering
-\includegraphics[width=0.6\textwidth]{fig/novel_APH_exergy.tif}
+\includegraphics[width=0.8\textwidth]{fig/novel_APH_exergy.png}
 \caption{Exergy destruction and efficiency of air preheat subsystem of novel system} 
 \label{fig:novel_APH_exergy}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=0.6\textwidth]{fig/regenerative_subsys_compare.png}
+\caption{Exergy destruction comparison of regenerative subsystems} 
+\label{fig:regenerative_subsys_compare}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=0.6\textwidth]{fig/partload_efficiency.png}
+\caption{Exergy efficiency in off-design conditions} 
+\label{fig:partload_efficiency}
 \end{figure}

### 2018-01-28 article.tex
加入子系统变工况用损率分析图
1修改新系统图 2完成latex转换

@@
 \centering
-\includegraphics[width=0.9\textwidth]{fig/reference_system}
+\includegraphics[width=1\textwidth]{fig/reference_system}
 \caption{Schematic of the reference system} 
@@
 \centering
-\includegraphics[width=0.9\textwidth]{fig/novel_system}
+\includegraphics[width=1\textwidth]{fig/novel_system.png}
 \caption{Schematic of the novel system} 
@@
 \label{sub:Thermodynamic_evaluation}
+
+\subsubsection{Thermodynamic comparison in design condition}
+\label{ssub:desing_compare}
 Based on the analysis of the reference system, the temperature difference of the heat exchangers is very high and exergy efficiency is rather low.
@@
 \begin{table}
-\caption{Thermodynamic performance of the reference and novel systems}
+\caption{Thermodynamic performance of reference and novel systems}
 \label{table:thermal performance compare}
@@
 \begin{table}
-\caption{Systems' exergy destruction rate comparison }
+\caption{Exergy destruction rate comparison of reference and novel systems }
 \label{table:system exergy campare}
@@
 \label{table:extraction compare}
-\caption{Systems' extractions comparison}
+\caption{Extractions comparison of reference and novel systems}
 \begin{centering}
@@
 % 下面两段话需要根据图修改
+%对于新系统优化可二次再热后蒸汽的抽汽，使8th抽汽量增加
 The variation of mass flow rate of extractions is presented in Fig 6.
@@
 \end{figure}
-
+% 在空气预热开始时，在第8级空预器出换热量和换热温差均较大，使之成为用损最大的换热器，随着空气预热的继续进行，换热温差降低，低1-7级空预器的用损减小。当空气进入AOC时，由于抽汽温度较高，所以换热温差增大，但由于换热量较小，造成在AOC中的用损失较小。
 \begin{figure}[htbp]
@@
 \centering
+\includegraphics[width=0.6\textwidth]{fig/LPE_exergy_LMTD.png}
+\caption{Exergy efficiency and LMTD of LPEs} 
+\label{fig:LPE_exergy_LMDT}
+\end{figure}
+
+\subsubsection{Thermodynamic comparison in off-design conditions}
+\label{ssub:0ffdesing_compare}
+\begin{figure}[htbp]
+\centering
 \includegraphics[width=0.6\textwidth]{fig/partload_efficiency.png}
-\caption{Exergy efficiency in off-design conditions} 
+\caption{Exergy efficiency comparison in off-design conditions} 
 \label{fig:partload_efficiency}
@@
 
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=0.6\textwidth]{fig/partload_subsys_exergyrate.png}
+\caption{Exergy destruction rate difference of subsystems in off-design conditions} 
+\label{fig:partload_subsys_exergyrate}
+\end{figure}
+
 % subsubsection subsubsection_name (end)
+
+\section{Conclusion}
+This study presents an optimization design of cascaded utilization of energy for a 1000 MW double reheat ultra-supercritical unit.
+ Thermodynamic analysis is conducted to reveal the comprehensive effects of the optimization measures. 
+ The optimization system is found to be effective in overcoming the imperfections, and may provide an effective method for the optimization of a double reheat system in USC unit.
+  The following conclusions are drawn from this study:
+
+ \begin{enumerate}[(1)]
+\item The thermodynamic analysis indicates that the cascaded utilization system decreases the temperature difference of in air heating and flue gas cooling process which achieves the cascaded utilization of energy, and the superheat degree of the 3rd and 5th is reduced greatly.
+Besides, more exhaust heat of the flue gas is recovered since the LPE cools the flue gas to lower temperature. 
+\item The layout in the cascaded utilization system changes the mass flow rates of extractions, which causes increment of output power of the generator and increment of the cold source loss.
+\item The optimization system improves the temperature of secondary air, which improves the fire condition in the combustion chamber.
+ The temperature of secondary air under full load in the optimization model is 365 ℃, which is 34 ℃ higher than the design value.
+\item For the first extraction, throttling loss is not existed while the feedwater of boiler improves little.  
+\item The optimization system theoretically brings remarkable energy saving effects.
+The simulation results show that the optimization system can reduce the SCE consumption by 5.6 g/kWh under full load, and can even bring a reduction of 2.9 g/kWh under 50\% THA load .
+\end{enumerate}
+
 \section*{References}

### 2018-01-30 article.tex
1加了变量命名文件，详细的可以看张成的github 2添加了论文完成还需要进行的工作

@@
 \documentclass[preprint,12pt]{elsarticle}
-
-\usepackage{amssymb,hyperref,booktabs,multirow}
+\usepackage{caption} 
+%\renewcommand{\captionlabeldelim}{.}
+\usepackage{color}%临时添加,
+\usepackage{amssymb,hyperref,booktabs,multirow,multicol,ifthen}
 \usepackage{enumerate}
-
+\usepackage{nomencl}
 \usepackage{float}
 \usepackage{graphics}
+\usepackage{framed}
+
+\renewcommand{\nomgroup}[1]
+{%
+\ifthenelse{\equal{#1}{C}}{\item[\textbf{Constants}]}{%
+\ifthenelse{\equal{#1}{V}}{\item[\textbf{Variables}]}{%
+\ifthenelse{\equal{#1}{S}}{\item[\textbf{sets}]}{}}}
+}
+\makenomenclature
+
 % \usepackage{graphicx}%插入图片
@@
 
-% \usepackage{bm}%数学字体加粗
+\usepackage{bm}%数学字体加粗
 
@@
 
-% \captionsetup[figure]{font=small,labelfont=bf,labelsep=period}%修改标题文字格式
+\captionsetup[figure]{font=small,labelfont=bf,labelsep=period}%修改标题文字格式
 
-% \renewcommand{\figurename}{Fig.}%修改标题样式
+\renewcommand{\figurename}{Fig.}%修改标题样式
 
-% \newcommand{\tabincell}[2]{}%让表格内容自动换行，但仍然需要用到换行\\
+%\newcommand{\tabincell}[2]{}%让表格内容自动换行，但仍然需要用到换行\\
 
@@
 
+\printnomenclature[1.5cm]{}
+
 \section{Introduction}
@@
 Coal is still the main fossil fuel resources for electricity production in the world according to~\cite{Ouedraogo2013Energy}. 
-In China, coal –fired power generation accounts for more than 70\% of the total electricity generation and subsequently contribute almost 50\%, 37\%, 33\% and 55\% to the SO$_X$, NO$_X$, dust and CO$_X$ emission volumes respectively~\cite{Zhang2010Analysis}.
+In China, coal–fired power generation accounts for more than 70\% of the total electricity generation and subsequently contribute almost 50\%, 37\%, 33\% and 55\% to the SO$_X$, NO$_X$, dust and CO$_X$ emission volumes respectively~\cite{Zhang2010Analysis}
 Statics show that China has been the largest producer and consumer of energy all over the world since 2013 [??]. 
@@
 Variations and energy saving effects of a double reheat ultra-supercritical thermal system (reference system) and the novel system are analyzed to evaluate their performance.
-
 \section{System optimization of double reheat USC system}
@@
 After Hsf and Hss the flue gas channel is divided into the front-duct flue and the back-duct flue.
-The front duct arranges low-temperature first reheater (Ltfr) and the front-duct economizerz (Feco), the back duct arranges a low-temperature second reheater (Ltsr) and back-duct economizer (Beco).
-The rear flue is equipped with an air preheater(APH).
-% 从锅炉受热面布置可以看出，锅炉主要受热面布置在炉膛之中，而水平烟道和竖井烟道中仅布置有空气预热设备。所以锅炉可以分成两部分:炉膛内完成水/蒸汽吸热的boiler，和尾部烟道内 完成空气预热的APH。
+The front duct arranges low-temperature first reheater (Ltfr) and the front-duct economizerz (中，而水平烟道和竖井烟道中仅布置有空气预热设备。所以锅炉可以分成两部分:炉膛内完成水/蒸汽吸热的boiler，和尾部烟道内 完成空气预热的APH。
 \begin{figure}[htbp]
@@
 \end{figure}
+Feco), the back duct arranges a low-temperature second reheater (Ltsr) and back-duct economizer (Beco). The rear flue is equipped with an air preheater(APH).
+% 从锅炉受热面布置可以看出，锅炉主要受热面布置在炉膛之
 
@@
 \end{table}
-Table 2 gives the temperature profiles and exergy efficiency of regenerative heaters and the air preheater, revealing the energy match level of heat exchangers.
-For the air preheater, the temperature of flue gas at the inlet of the air preheater is 376$^\circ$C under THA condition, while the temperature of the air to be heated by the flue is 25$^\circ$C, leading to the exergy destruction of 27.17\,MW.
+Table~\ref{tab:reheater parameter}gives the temperature profiles and exergy efficiency of regenerative heaters and the air preheater, revealing the energy match level of heat exchangers.
+For the air preheater, the temperature of flue gas at the inlet of the air preheater is 376$^\circ$C under THA condition, while the temperature of the air to be heated by the flue is 23$^\circ$C, leading to the exergy destruction of 27.17\,MW.
 The temperature difference of the air preheater is calculated to be 72$^\circ$C, and average temperature of the air is 177$^\circ$C, causing the exergy efficiency of 77.16\%.
 \begin{table}[htbp]
-\caption{fluid parameters of heat exchangers and air preheater}
+\caption{Fluid parameters of heat exchangers and air preheater}
 \label{tab:reheater parameter}
@@
 \toprule 
-\multirow{2}{2cm}{Components} &\multirow{2}{2.7cm}{Hot fluid temperature($^\circ$C)}  & \multirow{2}{3.2cm}{Cold fluid temperature ($^\circ$C)}&\multirow{2}{2.5cm}{LMTD ($^\circ$C)}\tabularnewline
+\multirow{2}{2cm}{Components} &\multirow{2}{2.7cm}{Hot fluid temperature($^\circ$C)}  & \multirow{2}{3.2cm}{Cold fluid temperature ($^\circ$C)}&\multirow{2}{2.2cm}{LMTD ($^\circ$C)}\tabularnewline
 &&&\tabularnewline
@@
 The throttling of the first extraction will certainly cause extra irreversible loss.
-%2.2
 \subsection{Proposal of a novel system with EAPH and LPE}
@@
 
-\section{Model establishment and thermodynamic evaluation} % (fold)
-\label{sec3:modle est and eval}
-\subsection{Model description and system analysis method} % (fold)
+% \section{Model establishment and thermodynamic evaluation} % (fold)
+% \label{sec3:modle est and eval}
+\section{Model description and Thermodynamic metric}
 \label{ssub:model_establishment_and_system_analysis_method}
 
-\subsubsection{Model establish method and main assumption}
+\subsection{Model establish method and main assumption}
 \label{ssub3:modle description}
+\textcolor{red}{!novel model established based on the reference which parameters change and which not! }
+%对模型中如何基于现有系统进行的改造，和哪些数据不发生变化进行说明
 In this paper, the thermodynamic cycle of the thermal system under different loads are simulated with EBSILON® Professional for its flexibility and level of detail. 
@@
 
-\subsubsection{System analysis method} %(fold)
+\subsection{Thermodynamic metric} %(fold)
 \label{ssub3:analsys method} 
@@
 \end{equation}
+\nomenclature[Cp]{$E$}{The number of angels per unit area}%
+
+\nomenclature[Vo]{$W$}{The number of angels per needle point}%
+
+\nomenclature[so]{$I$}{The area of the needle point}%
+
 Exergy efficiency can be calculated in the following form:
@@
 Where LHV refer to lower heating value of fuel, C, H, O, N refer to mass fractions of carbon, hydrogen, oxygen, nitrogen by element analysis.
+More details of exergy  efficiency calculation can be found in Ref~\cite{G2016Exergy}
+
+%系统主要4个子系统和other部分的用损失如何计算，主要提出other包含的内容和反平衡计算方法
+
 \begin{table}
@@
 Condenser & $\dot{I}_{condenser}=\dot{E}{}_{in}-\dot{E}{}_{out}+\dot{W}{}_{p}$ & $\eta_{\uppercase\expandafter{\romannumeral2},boiler}=\frac{\dot{E}{}_{out}}{\dot{E}{}_{in}+\dot{W}{}_{p}}$\tabularnewline
-Cycle & $\dot{I}_{cycle}=\sum_{all}\dot{I}_{i}$ & $\eta_{\uppercase\expandafter{\romannumeral2},cycle}=\frac{\dot{W}{}_{net,out}}{\dot{E}{}_{fuel}}$\tabularnewline
+Cycle &$\dot{I}_{cycle}=\dot{E}{}_{fuel}-\dot{W}{}_{net,out}$ & $\eta_{\uppercase\expandafter{\romannumeral2},cycle}=\frac{\dot{W}{}_{net,out}}{\dot{E}{}_{fuel}}$\tabularnewline
 \bottomrule
@@
 
-\subsection{Thermodynamic performance evaluation} % (fold)
+\section{Thermodynamic performance evaluation} % (fold)
 \label{sub:Thermodynamic_evaluation}
-
-\subsubsection{Thermodynamic comparison in design condition}
+%对word版本的分布进行了较大的改动，需要继续调节
+\subsection{Thermodynamic comparison in design condition}
 \label{ssub:desing_compare}
-Based on the analysis of the reference system, the temperature difference of the heat exchangers is very high and exergy efficiency is rather low.
-Using turbine extractions to heat air can realize the reduce the heat transfer temperature difference and improve efficiency. 
-The economizer outlet flue gas is used to heat low-temperature economizer can also reduce the loss of regenerative system.
-% In order to complete the heat balance calculation of the thermodynamic system, the key parameters in the novel system need to be set.
-% The novel system’s parameters are based on reference system, so the main parameters must be the same.
-The main parameters settled are including: superheat steam’s mass flow, pressure and temperature; First/second reheater’s inlet and outlet pressure and temperature; Turbine Exhaust pressure and temperature; turbine extraction’s pressure and temperature/ specific enthalpy etc.
-The main parameters settled under THA situation can be found in Table 1 and Table 4 .
-% 对于新旧系统表格的热力参数进行分析，下面这段话太少
+%表四
+The comparison of thermal dynamic performance between these two systems is given in Table~\ref{table:thermal performance compare}. 
+Under design condition, the novel system brings an improvement of net generating power by 11.02 MW, and a reduction of SCE consumption by 5.5\,g/kWh.
+The power generation efficiency reaches 48.73\%, 1.04\% higher then that of reference system.
+Meanwhile, the exergy efficiency of novel system is 1.01\% higher, showing good exergy-saving effect.
 
@@
 Exergy efficiency (\%) & 46.51 & 47.52\tabularnewline
-Addition in generating efficiency (\%) &  & 1.01\tabularnewline
+Addition in exergy efficiency (\%) &  & 1.01\tabularnewline
 \bottomrule
@@
 % 根据用损失对比表从新进行分析，从为什么锅炉空预器效率提高，其他不变或者降低说起
-The results of exergy analysis of the optimization system are presented in Table~\ref{table:system exergy campare}. 
-It is found that the optimization system has an improvement in exergetic performance.
- The total exergy destruction of the cascaded utilization system is 1096.52 MW, which is 32.28 MW lower than the original. 
- The new system also brings the improvement from 46.98\% to 47.99\%. 
+Table~\ref{table:system exergy campare} gives the results of subsystem exergy analysis of the two system. 
+It is found that the novel system has an improvement in exergetic performance by an decrease of 10.82\,MW of total exergy destruction rate.
+Exergy destruction rate of boiler accounts for the highest proportion and decrease most (11.04\,MW).
+Air preheat subsystem's exergy destruction rate of novel system changes from 27.39\,MW to 16.55\,MW, having a 10.84\,MW decreasmen
  Results show that the exergy destruction of boiler is 855.72 MW, leading to the increment of exergy efficiency by 0.18\%.
@@
 Turbine & 63.33 & 63.97\tabularnewline
-Air Preheater  & 27.39 & 16.55\tabularnewline
-Regenerative system & 22.53 & 21.56\tabularnewline
+Air preheat subsystem  & 27.39 & 16.55\tabularnewline
+Regenerative subsystem & 22.53 & 21.56\tabularnewline
 Other & 131.03 & 142.42 \tabularnewline
@@
 \begin{table}
-\label{table:extraction compare}
 \caption{Extractions comparison of reference and novel systems}
+\label{table:extraction_compare}
 \begin{centering}
@@
 % 下面两段话需要根据图修改
-%对于新系统优化可二次再热后蒸汽的抽汽，使8th抽汽量增加
-The variation of mass flow rate of extractions is presented in Fig 6.
+
+%本文是针对空预系统和回热系统的联合优化改造，所以本文将新系统和参考系统中的差变化，系统中设备的效率和用损变化进行了分析。
+The variation of mass flow rate of extractions is presented in Table~\ref{table:extraction_compare}.
 Mass flow rate of the 1st, 3rd, 5th and 8th extractions of the optimization system is more than that of the base model, and the rest extractions except the last two, has the opposite variation. 
@@
  Air is heated by extractions, which will cause an increment in mass flow. 
- And the use of LPE can saves extractions.so the total extraction keeps unchanged.
- Turbine total extraction steam volume change affect its exergy efficiency by 2.03\%.
+ And the use of LPE can saves extractions.
+ so the total extraction mass flow keeps almost unchanged.
+%新系统优化可二次再热后蒸汽的抽汽，使8th抽汽量增加
 
 The air is heated by the staged air preheaters and additional outer steam coolers in the cascaded utilization system.
- It can be seen from Table 5 that the total exergy destruction of the air heating system is 16.35 MW, 10.82 MW lower than that of the original air preheater which is 27.17 MW. 
- Fig 7 shows that the exergy efficiency of APHs and AOCs is higher than 82\%, except APH8.
+It can be seen from Table 5 that the total exergy destruction of the air heating system is 16.35 MW, 10.82 MW lower than that of the original air preheater which is 27.17\,MW.
+
+%插入对QT图的解释和分析
+
+Fig.~\ref{fig:APH_temper_compare} shows that the exergy efficiency of APHs and AOCs is higher than 82\%, except APH8.
 For the air preheaters, the improvement in performance results from more reasonable energy utilization and the heat transform method. 
@@
 \end{figure}
+%插入对于回热系统的分析
+
+% The total exergy loss of the LPEs is 10.73MW, and the overall exergy efficiency is 91.62%, much higher than that of air preheater.
+As shown in Fig.6, the temperature difference of the LPEs is between 23 ℃ to 42 ℃, less than that of the original air preheater.
+The LPE1 and LPE4 have the greatest exergy loss of all the LPEs, which mainly results from their great heat transfer rate.
+Besides the exergetic performance of the LPEs keeps falling along the flow direction of flue gas.
+This is because the higher temperature of the cold stream, the greater exergy efficiency, for the temperature difference changes little in heat transfer process.
+% The layout of the optimization system also changes the exergetic performance of regenerative heaters, shown in Fig.7.
+The total exergy loss of regenerative heaters is 11.60 MW, which is greatly reduced compared with that of the base model.
+On the one hand, owing to the heat injected by flue gas, less extracted steam is needed for the HRH2, HRH4, LRH6, and LRH8 which are paralleled with LPEs, which causes less exergy loss of corresponding regenerative heater.
+On the other hand, the LPEs heat condensate and feedwater to higher temperature level than the regenerative heaters, leading to less heat transfer rate of HRH1, HRH3, DEA and LRH7, which will also reduce the exergy loss.
+%There are three factors causing the improvement in exergetic performance.
+Firstly, for HRH1, HRH3, DEA and LRH7, due to higher temperature level of the water from LPE, the exergy of the inlet feedwater e_(c,i) increases, leading to the efficiency improvement.
+Secondly, the installation of AOCs causes the reduction of the superheat degree of the extracted steam entering the HRH3 and DEA, and reduce its exergy, namely e_(h,i).
+At last, compared the original regenerative heaters, an extral part of drainage from corresponding air preheater of optimization system is used to heat the feedwater.
+Compared with the extracted steam, the drainage from air preheaters has lower exergy, which reduce the irreversible loss to some extent.
 
@@
 \end{figure}
+%对锅炉、汽轮机、和other系统的用效率进行分析
 
-\subsubsection{Thermodynamic comparison in off-design conditions}
+\subsection{Thermodynamic comparison in off-design conditions}
 \label{ssub:0ffdesing_compare}
+Considering that large USC power plants' operation under partial load conditions, it is necessary to study the thermal performance of double reheat USC power plants under off-design conditions.
+Four typical operation conditions, THA load, 75\% THA load, 50\% THA load, and 40\% THA load conditions, were chosen for thermodynamic analyses. 
+Fig.~\ref{fig:partload_efficiency} shows novel and reference systems' exergy efficiency under different load conditions.The exergy efficiencies of both systems decrease as the load decrease.
+The exergy efficiencies of both systems are 47.52\% and 46.51\% under THA load condition.
+Compared with reference system, novel system's exergy efficiency has the increment of 1.01 percentage points, and reduces SCE consumption by 5.5\,g/kWh.
+Under the 75\% THA condition, the optimized system was 46.56\% and the reference system was 45.90\%, the exergy
+efficiency decrease to 0.66\%. 
+When the load is equal to 50\% THA, the efficiency difference is 0.43\%.
+This implies that the novel system can increase exergy efficiency under partial load, but it has more advantages for double reheat power plant undertaking base load.
+
 \begin{figure}[htbp]
@@
 \end{figure}
+  exergy destruction ratio (y$_{D}$) is used to measure the exergy destruction of 1\,MW power generation of unit by a subsystem, and its calculate formula is as follow:
+\begin{equation}
+y_{D}=\frac{\dot{I}}{P}
+\end{equation}
+
+% 用损率差大表明该子系统的节能效果更显著，同时对整个系统的节能效果贡献更大。
+% 由图10可以得到新系统引起节能效果从大到小依次为：锅炉、空预系统、回热系统和汽轮机。
+% 当负荷从THA逐渐降低可以看到，降负荷对锅炉影响最大，而负荷变化对汽轮机系统影响接近于零。
+% 负荷降低到40%，四个子系统优化效果虽然降低但累计值依然优于参考系统，但由于符合降低引起的oher系统用损失的升高导致优化系统相对与参考系统效率增加为0.01%，几乎没有优化效果
+% 同时需要指出，由于锅炉本身的用损失很大，所以变负荷对锅炉本身用效率影响很小,而对空预子系统的影响较大。
+A large exergy destruction ratio value indicates that the subsystem has more significant energy-saving effects and contributes more to the exergy-saving effect of the entire system.
+Fig.~\ref{fig:partload_subsys_exergyrate} shows the  exergy destruction ratio difference ($y_{D,refere}-y_{D,novel}$) between reference system and novel system.
+It indicates that the contribution of energy-saving effect decrease as follows: the boiler, air preheat subsystem, regenerative subsystem and steam turbine.
+As the load decreases from THA load condition, it can be seen that the load change has the greatest effect on the boiler, while the change of load condition barely affects the steam turbine.
+While the load is reduced to 40\%THA, the four subsystems of the novel system are still have lower exergy destruction rate than those of the reference system.
+However the calculated value of these subsystem decrease and exergy destruction rate increase of other uncalculated components make the novel system's exergy-saving effect decrease.
+According to the data of Table~\ref{table:system exergy campare}, it should be pointed out that due to the great exergy destruction of the boiler, the decrease of load has little effect on the exergy efficiency of it.But the air preheat subsystem is most effected.
 
@@
 \includegraphics[width=0.6\textwidth]{fig/partload_subsys_exergyrate.png}
-\caption{Exergy destruction rate difference of subsystems in off-design conditions} 
+\caption{!!!!Exergy destruction rate difference of subsystems in off-design conditions!!!!} 
 \label{fig:partload_subsys_exergyrate}
@@
 \section{Conclusion}
-This study presents an optimization design of cascaded utilization of energy for a 1000 MW double reheat ultra-supercritical unit.
+%文章干了什么
+\textcolor{red}{This study presents an optimization design of cascaded utilization of energy for a 1000 MW double reheat ultra-supercritical unit.}
 Thermodynamic analysis is conducted to reveal the comprehensive effects of the optimization measures. 
@@
 The following conclusions are drawn from this study: 
-
  \begin{enumerate}[(1)]

### 2018-01-30 article.tex
完成了系统和子系统用分析，对论文需要添加部分进行了中文注释

@@
 \renewcommand{\nomgroup}[1]
-{%
-\ifthenelse{\equal{#1}{C}}{\item[\textbf{Constants}]}{%
-\ifthenelse{\equal{#1}{V}}{\item[\textbf{Variables}]}{%
-\ifthenelse{\equal{#1}{S}}{\item[\textbf{sets}]}{}}}
+{%Mathematical symbols
+\ifthenelse{\equal{#1}{G}}{\item[\textbf{Greek letters}]}{%
+\ifthenelse{\equal{#1}{S}}{\item[\textbf{Subscripts}]}{%
+\ifthenelse{\equal{#1}{U}}{\item[\textbf{Superscripts}]}{
+\ifthenelse{\equal{#1}{C}}{\item[\textbf{Constants}]}{
+\ifthenelse{\equal{#1}{M}}{\item[\textbf{Mathematical symbols}]}{
+}%几个类别需要几个括号
 }
+}
+}
+}%几个类别需要几个括号
+}%对应1]
 \makenomenclature
@@
 
-\begin{abstract}
+\begin{abstract}%修改到300字以内
 Herein, an novel system of a 1000\,\,MW double-reheat ultra-supercritical (USC) unit with turbine-extraction-heated air preheaters (EAPHs), which use turbine extractions as heat sources of air preheaters while economizer outlet flue gas’ heat absorbed by low pressure economizers (LPEs), is designed based on reference system of a 1000\,\,MW double-reheat USC unit.
@@
 Furnace layout shown in Fig~\ref{fig:boiler_surface}, the boiler furnace is composited by the membrane wall, along flue gas flow direction lays low-temperature superheater (Lts) screen tube, cold segment of high-temperature ﬁrst reheater (Csf), cold segment of high-temperature second reheater (Csf), High temperature super-heater (Hts), hot segment of high-temperature ﬁrst reheater (Hsf), hot segment of high-temperature second reheater (Hss).
-After Hsf and Hss the flue gas channel is divided into the front-duct flue and the back-duct flue.
-The front duct arranges low-temperature first reheater (Ltfr) and the front-duct economizerz (中，而水平烟道和竖井烟道中仅布置有空气预热设备。所以锅炉可以分成两部分:炉膛内完成水/蒸汽吸热的boiler，和尾部烟道内 完成空气预热的APH。
+After Hsf and Hss the flue gas channel is divided into the front-duct flue and the back-duct flue. The front duct arranges low-temperature first reheater (Ltfr) and the front-duct economizerz 
+(%中，而水平烟道和竖井烟道中仅布置有空气预热设备。所以锅炉可以分成两部分:炉膛内完成水/蒸汽吸热的boiler，和尾部烟道内 完成空气预热的APH。Feco), the back duct arranges a low-temperature second reheater (Ltsr) and back-duct economizer (Beco).
+The rear flue is equipped with an air preheater(APH).
+% 从锅炉受热面布置可以看出，锅炉主要受热面布置在炉膛之
 \begin{figure}[htbp]
@@
 \end{figure}
-Feco), the back duct arranges a low-temperature second reheater (Ltsr) and back-duct economizer (Beco). The rear flue is equipped with an air preheater(APH).
-% 从锅炉受热面布置可以看出，锅炉主要受热面布置在炉膛之
 
@@
 \label{sub2:prop novel sys}
-
+%添加为什么进行这种设计的解释，为什么设置LPE AOC APH的级数
 The  layout of the optimization system is presented in Fig~\ref{fig:novel_system}.
@@
 %对模型中如何基于现有系统进行的改造，和哪些数据不发生变化进行说明
+%添加模型中基本部件的特性 添加个表格
 In this paper, the thermodynamic cycle of the thermal system under different loads are simulated with EBSILON® Professional for its flexibility and level of detail. 
@@
 \end{equation}
-\nomenclature[Cp]{$E$}{The number of angels per unit area}%
-
-\nomenclature[Vo]{$W$}{The number of angels per needle point}%
-
-\nomenclature[so]{$I$}{The area of the needle point}%
 
@@
 The comparison of thermal dynamic performance between these two systems is given in Table~\ref{table:thermal performance compare}. 
-Under design condition, the novel system brings an improvement of net generating power by 11.02 MW, and a reduction of SCE consumption by 5.5\,g/kWh.
+Under design condition, the novel system brings an improvement of net generating power by 11.02 MW, and reduces SCE consumption by 5.5\,g/kWh.
 The power generation efficiency reaches 48.73\%, 1.04\% higher then that of reference system.
@@
 Exergy destruction rate of boiler accounts for the highest proportion and decrease most (11.04\,MW).
-Air preheat subsystem's exergy destruction rate of novel system changes from 27.39\,MW to 16.55\,MW, having a 10.84\,MW decreasmen
- Results show that the exergy destruction of boiler is 855.72 MW, leading to the increment of exergy efficiency by 0.18\%.
-In addition, there is almost no change of the exergy parameters of the steam turbines, generator and condenser.
- For the air heating system and regenerative system, great change happens compared with the formal system, and detailed analysis will be carried out next.
+Air preheat subsystem's exergy destruction rate changes from 27.39\,MW to 16.55\,MW, having a 10.84\,MW decrement, having the largest Optimization ratio.
+In the mean time, turbines and regenerative subsystem have a relatively small change at about 1\,MW.
 
-Through the analysis of the reference system and the optimization system, it can be seen that the exergy efficiency of the optimization system is improved and the exergy destruction is reduced.
-Comparing the proportion of different components in the total exergy destruction between the two systems, we can see that in addition to the turbine, the exergy destruction of all components is reduced.
-Among them, the air preheating system efficiency is the most obviously improved，to 38.94\%.
+The item "other" of novel system is higher then reference system, showing that the uncalculated components of systems have a increment of exergy destruction rate.
+Among the uncalculated components, the pips' amount increasing and work fluid mixing with parameters not match are the mainly reason why that party has a increment in exergy destruction rate.
 
@@
 
+\nomenclature[M]{$\dot{I}$}{Exergy destruction rate (MW)}%
+\nomenclature[S]{$in$}{inlet}%
+\nomenclature[S]{$out$}{outlet}%
+\nomenclature{AOC}{additional outer steam cooler}
+
 \end{document}

### 2018-01-31 article.tex
修改到回热部分，图和部件说法 文章中需要统一，并简洁化

@@
 %添加为什么进行这种设计的解释，为什么设置LPE AOC APH的级数
-The  layout of the optimization system is presented in Fig~\ref{fig:novel_system}.
-In the optimization system, the air is not heated by flue gas in the conventional air preheater, and 8 new air preheaters (APH1\-APH8) using several extractions to heat the air is adopted.
+\textcolor{red}{The  layout of the optimization system is presented in Fig~\ref{fig:novel_system}.
+In the optimization system, the air is not heated by flue gas in the conventional air preheater, and 8 new air preheaters (APH1\~APH8) using several extractions to heat the air is adopted.
 The new air preheater is similar with regenerative heaters in function.
@@
 For example, the 2nd extraction has the highest temperature, and is applied to heat the air in the 1st AOC, and then the cooled steam from AOC1 is sent to HRH2 and air APH2 to heat the water and air respectively.
+}
 
@@
 Part of the condensate and feed water at the inlet of regenerative heater are sent to the LPE, then the heated water join with the main feedwater/condensate. 
-Considering the acid dew point temperature, the flue gas temperature at the outlet of the last LPE is set 95℃. 
+Considering the acid dew point temperature, the flue gas temperature at the outlet of the last LPE is set 95$^	rc$C. 
 The temperature of heated water from LPE is set little higher than the feedwater from the corresponding regenerative heater.%
@@
 \label{equation:1}
-\dot{I}=\sum\dot{E}{}_{in}-\sum\dot{E}{}_{out}+\sum\dot{W}{}_{in}-\sum\dot{W}{}_{out}
+\dot{I}=\sum\dot{X}{}_{in}-\sum\dot{X}{}_{out}+\sum\dot{W}{}_{in}-\sum\dot{W}{}_{out}
 \end{equation}
@@
 \label{equation:2}
-\eta=\frac{\dot{E}{}_{earned}}{\dot{E}{}_{cost}}
+\eta=\frac{\dot{X}{}_{earned}}{\dot{X}{}_{cost}}
 \end{equation}
-For different equipment under stable operating conditions, equation~\ref{equation:1}~\ref{equation:2} have different forms as shown in Table~\ref{tab:exergy equation}~\cite{Aljundi2009Energy}
-For flue gas, air, water and steam, the specific exergy can be calculated by equation~\ref{equation:3}.
-
-\begin{equation}{}
-\label{equation:3}
-e=h-h_{0}-T_{0}\left(s-s_{0}\right)
-\end{equation}
-Then the total exergy rate associated with ﬂuid stream becomes:
-\begin{equation}
-\dot{E}=\dot{m}e=\dot{m}\left[h-h_{0}-T_{0}\left(s-s_{0}\right)\right]{}
-\end{equation}
-The fuel speciﬁc exergy is calculated as[?]: 
-\begin{equation}
-e_{fuel}=LHV\left(1.0064+0.1519\frac{H}{C}+0.0616\frac{O}{C}+0.0429\frac{N}{C}\right)
-\end{equation}
-Where LHV refer to lower heating value of fuel, C, H, O, N refer to mass fractions of carbon, hydrogen, oxygen, nitrogen by element analysis.
-More details of exergy  efficiency calculation can be found in Ref~\cite{G2016Exergy}
-
-%系统主要4个子系统和other部分的用损失如何计算，主要提出other包含的内容和反平衡计算方法
+For different equipment under stable operating conditions, equation~\ref{equation:1}, ~\ref{equation:2} have different forms as shown in Table~\ref{tab:exergy equation}~\cite{Aljundi2009Energy}
 
@@
 \midrule
-Boiler & $\dot{I}_{boiler}=\dot{E}{}_{fuel}+\dot{E}{}_{in}-\dot{E}{}_{out}$ & $\eta_{\uppercase\expandafter{\romannumeral2},boiler}=\frac{\dot{E}{}_{out}-\dot{E}{}_{in}}{\dot{E}{}_{fuel}}$\tabularnewline
-Pump & $\dot{I}_{pump}=\dot{E}{}_{in}-\dot{E}{}_{out}+\dot{W}{}_{pump}$ & $\eta_{\uppercase\expandafter{\romannumeral2},pump}=1-\frac{\dot{I}_{pump}}{\dot{W}{}_{pump}}$\tabularnewline
-Heater & $\dot{I}_{heater}=\dot{E}{}_{in}-\dot{E}{}_{out}$ & $\eta_{\uppercase\expandafter{\romannumeral2},heater}=1-\frac{\dot{I}_{heater}}{\dot{E}{}_{in}}$\tabularnewline
-Turbine & $\dot{I}_{turbine}=\dot{E}{}_{in}-\dot{E}{}_{out}-\dot{W}{}_{el}$ & $\eta_{\uppercase\expandafter{\romannumeral2},turbine}=1-\frac{\dot{I}_{turbine}}{\dot{E}{}_{in}-\dot{E}{}_{out}}$\tabularnewline
-Condenser & $\dot{I}_{condenser}=\dot{E}{}_{in}-\dot{E}{}_{out}+\dot{W}{}_{p}$ & $\eta_{\uppercase\expandafter{\romannumeral2},boiler}=\frac{\dot{E}{}_{out}}{\dot{E}{}_{in}+\dot{W}{}_{p}}$\tabularnewline
-Cycle &$\dot{I}_{cycle}=\dot{E}{}_{fuel}-\dot{W}{}_{net,out}$ & $\eta_{\uppercase\expandafter{\romannumeral2},cycle}=\frac{\dot{W}{}_{net,out}}{\dot{E}{}_{fuel}}$\tabularnewline
+Boiler & $\dot{I}_{boiler}=\dot{X}{}_{fuel}+\dot{X}{}_{in}-\dot{X}{}_{out}$ & $\eta_{\uppercase\expandafter{\romannumeral2},boiler}=\frac{\dot{X}{}_{out}-\dot{X}{}_{in}}{\dot{X}{}_{fuel}}$\tabularnewline
+Pump & $\dot{I}_{pump}=\dot{X}{}_{in}-\dot{X}{}_{out}+\dot{W}{}_{pump}$ & $\eta_{\uppercase\expandafter{\romannumeral2},pump}=1-\frac{\dot{I}_{pump}}{\dot{W}{}_{pump}}$\tabularnewline
+Heater & $\dot{I}_{heater}=\dot{X}{}_{in}-\dot{X}{}_{out}$ & $\eta_{\uppercase\expandafter{\romannumeral2},heater}=1-\frac{\dot{I}_{heater}}{\dot{X}{}_{in}}$\tabularnewline
+Turbine & $\dot{I}_{turbine}=\dot{X}{}_{in}-\dot{X}{}_{out}-\dot{W}{}_{el}$ & $\eta_{\uppercase\expandafter{\romannumeral2},turbine}=1-\frac{\dot{I}_{turbine}}{\dot{X}{}_{in}-\dot{X}{}_{out}}$\tabularnewline
+Condenser & $\dot{I}_{condenser}=\dot{X}{}_{in}-\dot{X}{}_{out}+\dot{W}{}_{p}$ & $\eta_{\uppercase\expandafter{\romannumeral2},boiler}=\frac{\dot{X}{}_{out}}{\dot{X}{}_{in}+\dot{W}{}_{p}}$\tabularnewline
+Cycle &$\dot{I}_{total}=\dot{X}{}_{fuel}-\dot{W}{}_{net,out}$ & $\eta_{\uppercase\expandafter{\romannumeral2},total}=\frac{\dot{W}{}_{net,out}}{\dot{X}{}_{fuel}}$\tabularnewline
 \bottomrule
@@
 \end{table}
+
+For flue gas, air, water and steam, the specific exergy can be calculated by equation~\ref{equation:3}.
+
+\begin{equation}{}
+\label{equation:3}
+x=h-h_{0}-T_{0}\left(s-s_{0}\right)
+\end{equation}
+Then the total exergy rate associated with ﬂuid stream becomes:
+\begin{equation}
+\dot{X}=\dot{m}e=\dot{m}\left[h-h_{0}-T_{0}\left(s-s_{0}\right)\right]{}
+\end{equation}
+The fuel specific exergy calculate method~\cite{Yan2016The} can be expressed as.
+\begin{equation}
+x_{fuel}=LHV\left(1.0064+0.1519\frac{H}{C}+0.0616\frac{O}{C}+0.0429\frac{N}{C}\right)
+\end{equation}
+Where LHV refer to lower heating value of fuel, C, H, O, N refer to mass fractions of carbon, hydrogen, oxygen, nitrogen by element analysis.
+More details of power plant equipments' exergy  efficiency calculation can be found in Ref~\cite{G2016Exergy}
+
+In order to clearly analyze the effect of system optimization, this paper divides the double-reheat USC system into four main subsystems and a sum of all other equipments, valves and pips named "other".
+The four main subsystems are boiler with out APH, turbines, air preheat subsystem, regenerative subsystem.
+The equations mentioned above can also be used into of exergy analysis these four main subsystems.
+For the "other" part, this paper used counter balance analysis method to calculate its exergy destruction rate, which means subtract the share of the four main subsystems from the total.
+ The exergy destruction rate can be calculated by using equation as follows:
+
+\begin{equation}
+\dot{I}_{other}=\dot{I}{}_{total}-\sum\dot{I}{}_{subsystems}
+\end{equation}
+
+%系统主要4个子系统和other部分的用损失如何计算，主要提出other包含的内容和反平衡计算方法
 
@@
 The item "other" of novel system is higher then reference system, showing that the uncalculated components of systems have a increment of exergy destruction rate.
-Among the uncalculated components, the pips' amount increasing and work fluid mixing with parameters not match are the mainly reason why that party has a increment in exergy destruction rate.
+Among the uncalculated components, the pips' amount increasing and work fluid mixing with parameters not match are the mainly reason why that part has a increment in exergy destruction rate.
 
@@
 
+% 下面两段话需要根据图修改
+
+%本文是针对空预系统和回热系统的联合优化改造，所以本文将新系统和参考系统中的差变化，系统中设备的效率和用损变化进行了分析。
+To conduct in-depth analysis of both systems, research of the mainly optimized subsystems, air preheat subsystem and regenerative subsystem was conducted.
+Table~\ref{table:extraction_compare} gives the variation of mass flow rate of extractions.
+As illustrated in Table~\ref{table:extraction_compare}, mass flow rate of the 1st, 3rd, 5th and 8th extractions of the novel system is more than that of the reference system, and the rest extractions except the last two, has the opposite variation.
+It can be found that the impact of system optimization on extraction is twofold: air is heated by extractions, which will cause an increment in mass flow, and the use of LPE can saves extractions so the total extraction mass flow keeps almost unchanged.
+
+The sum of 4th to 10th extractions mass flow increases from 138.46 kg/s to 145.07 kg/s, and the 8th extraction increase 13.9 kg/s.
+The mass flow increase of low pressure extractions implies that novel system can modify the quantity distribution of extractions.
+
+%新系统优化可二次再热后蒸汽的抽汽，使8th抽汽量增加
 \begin{table}
@@
 \end{table}
-% 下面两段话需要根据图修改
-
-%本文是针对空预系统和回热系统的联合优化改造，所以本文将新系统和参考系统中的差变化，系统中设备的效率和用损变化进行了分析。
-The variation of mass flow rate of extractions is presented in Table~\ref{table:extraction_compare}.
-Mass flow rate of the 1st, 3rd, 5th and 8th extractions of the optimization system is more than that of the base model, and the rest extractions except the last two, has the opposite variation. 
- The impact of system optimization on extraction is twofold. 
- Air is heated by extractions, which will cause an increment in mass flow. 
- And the use of LPE can saves extractions.
- so the total extraction mass flow keeps almost unchanged.
-%新系统优化可二次再热后蒸汽的抽汽，使8th抽汽量增加
-
-The air is heated by the staged air preheaters and additional outer steam coolers in the cascaded utilization system.
-It can be seen from Table 5 that the total exergy destruction of the air heating system is 16.35 MW, 10.82 MW lower than that of the original air preheater which is 27.17\,MW.
 
 %插入对QT图的解释和分析
-
-Fig.~\ref{fig:APH_temper_compare} shows that the exergy efficiency of APHs and AOCs is higher than 82\%, except APH8.
-For the air preheaters, the improvement in performance results from more reasonable energy utilization and the heat transform method. 
- In the conventional air preheater, the air is heated by high temperature flue gas through convection. 
- The working principle of the staged air preheaters in the optimization system is the same as regenerative heaters. 
- The superheated vapor is firstly cooled to saturated steam through convection, then to saturated water through phase change heat transfer, and the latter process accounts for the main part. 
- In this case, the temperature difference is greatly reduced, causing the improvement in performance.
+Air is heated by the EAPHs and AOCs in novel system from 23$^\circ$C to 363.33$^\circ$C. 
+A majority of outlet air of EAPH6 is send to miler as primary air, and rest of air is heated to 363.33$^\circ$C.
+Fig.~\ref{fig:APH_temper_compare} shows air preheat process' temperature difference between hot and cold fluid of novel and reference systems.
+The red triangle and red hollow triangle instead for steam average temperature of EAPH and AOC. 
+In order to simplify the diagram, using saturate temperature of steam instead of EAPH's average temperature and using mean value of inlet and outlet temperature as AOC's average temperature.
+The figure indicates that  temperature difference of EAPHs is lower than that of APH, which makes exergy efficiency's improvement.
+The AOCs' temperature difference is high, but heat exchange is relatively small and so does the exergy destruction. 
+So the air preheat subsystem  of novel system has a smaller exergy destruction rate and improvement on exergy efficiency.
+One the other hand, The total heat exchange  and secondary air temperature of novel system is higher then these of reference system, which make the boiler's exergy efficiency's improvement.
 
@@
 % 在空气预热开始时，在第8级空预器出换热量和换热温差均较大，使之成为用损最大的换热器，随着空气预热的继续进行，换热温差降低，低1-7级空预器的用损减小。当空气进入AOC时，由于抽汽温度较高，所以换热温差增大，但由于换热量较小，造成在AOC中的用损失较小。
+
+Fig.~\ref{fig:APH_temper_compare} shows EAPHs and AOCs's exergy analysis results. 
+Except EAPH8，the exergy efficiency of EAPHs and AOCs is higher than 82\%, and the APH8 has the greatest exergy loss and lowest efficiency of all the air preheaters. 
+It also indicates that, although the AOCs have large heat transfer temperature difference, their exergy efficiencies are still high and low exergy destruction rate, which have less impact on the total exergy efficiency.
+Combing Fig.~\ref{fig:APH_temper_compare} andFig.~\ref{fig:novel_APH_exergy},the reason why the novel system's air preheat subsystem have a higher exergy efficiency and lower exergy destruction rate can be drawn.
+For the novel system's air preheat subsystem, the improvement in performance results from lower heat transfer temperature difference and reasonable extractions' superheat degree using.
+
 \begin{figure}[htbp]
@@
 \includegraphics[width=0.8\textwidth]{fig/novel_APH_exergy.png}
-\caption{Exergy destruction and efficiency of air preheat subsystem of novel system} 
+\caption{Exergy destruction and efficiency of air preheat subsystem of novel system} %图中的纵坐标需要修改
 \label{fig:novel_APH_exergy}
@@
 % The total exergy loss of the LPEs is 10.73MW, and the overall exergy efficiency is 91.62%, much higher than that of air preheater.
-As shown in Fig.6, the temperature difference of the LPEs is between 23 ℃ to 42 ℃, less than that of the original air preheater.
+As shown in Fig.6, the temperature difference of the LPEs is between 23 $^	rc$C to 42 $^	rc$C, less than that of the original air preheater.
 The LPE1 and LPE4 have the greatest exergy loss of all the LPEs, which mainly results from their great heat transfer rate.
@@
 \subsection{Thermodynamic comparison in off-design conditions}
-\label{ssub:0ffdesing_compare}
+\label{ssub:offdesing_compare}
 Considering that large USC power plants' operation under partial load conditions, it is necessary to study the thermal performance of double reheat USC power plants under off-design conditions.
@@
 \item The optimization system improves the temperature of secondary air, which improves the fire condition in the combustion chamber.
- The temperature of secondary air under full load in the optimization model is 365 ℃, which is 34 ℃ higher than the design value.
+ The temperature of secondary air under full load in the optimization model is 365 $^	rc$C, which is 34 $^	rc$C higher than the design value.
 \item For the first extraction, throttling loss is not existed while the feedwater of boiler improves little.  

### 2018-02-02 article.tex
1 文章基本做完，但需要修改格式 语言和缩写统一，文章前后的词语统一，文献增加

@@
 
-\journal{Energy Conversation and Management}
+\journal{Energy Conversion and Management}
 
@@
 
-\title{A novel 1000\,\,MW double-reheat ultra supercritical system with turbine-extraction-heated air preheaters and low temperature economizers}
+\title{A novel 1000\,MW double-reheat ultra supercritical system with turbine-extraction-heated air preheaters and low temperature economizers}
 
@@
 \address[hust]{School of Energy and Power Engineering, Huazhong University of Science and Technology, Wuhan 430074,China}
-\address[ncst]{College of Metallurgy and Energy, NorthChina University of Scienceand and Technology, Tangshan 063009,China}
+\address[ncst]{College of Metallurgy and Energy, NorthChina University of Science and and Technology, Tangshan 063009,China}
 \cortext[cor1]{Corresponding authors}
@@
 \begin{abstract}%修改到300字以内
-Herein, an novel system of a 1000\,\,MW double-reheat ultra-supercritical (USC) unit with turbine-extraction-heated air preheaters (EAPHs), which use turbine extractions as heat sources of air preheaters while economizer outlet flue gas’ heat absorbed by low pressure economizers (LPEs), is designed based on reference system of a 1000\,\,MW double-reheat USC unit.
-The energetic performance analyses of the novel system and reference system are used to compare their major parameters. 
-In addition, thermodynamic analyses under partial load operation conditions are presented. 
-The results show that the proposed novel system reduced the exergy destruction in the air-heating processes.
+Double-reheat ultra-supercritical (USC) unit has received extensive attention for its high efficiency and energy-saving effect.
+The optimal design of its thermal system is still under study.
+Herein, an optimized system for reasonable fluid heat transfer temperature matching and higher efficiency was proposed.
+The novel system used turbine extractions as heat sources of air preheaters and low-pressure economizers to absorb economizer outlet flue gas’ heat, which realized the join optimization of air preheat process and regenerative system.
+Models were built to compare energetic performance of the novel system and reference system.
+In addition, thermodynamic analyses under partial load operation conditions was conducted. 
+Exergy analysis method was used to identify exergy destruction changes of transformed parts and analyze the cause of the change.
+Result shows the novel system can largely decrease exergy destruction rate of air preheat process and improve the system's thermal performance.
 Furthermore, the novel system increases the temperature of secondary air and reduces the overall superheat degree of several extractions.
- Theoretically, the novel system reduces the SCE consumption by nearly 5.5\,g/kWh under THA load when the temperature of the flue gas entering the electrostatic precipitator is set to 95$^\circ$C.
+Theoretically, the novel system with a overall exergy efficiency of 48.73\%  and reduces the SCE consumption by nearly 5.5\,g/kWh under THA load when the temperature of the flue gas entering the electrostatic precipitator is set to 95$^\circ$C.
 Moreover, the novel system can still has advantages in coal saving under partial load condition.
- Our findings indicate that system with EAPH could improves the performance of the unit and may provide a theoretical basis for the novel of double-reheat USC units.
+
 \end{abstract}
@@
 \begin{keyword}
-Double reheat \sep Ultra-supercritical power plant \sep Exergy analysis \sep System novel \sep Thermodynamic analyses
+Double reheat \sep Ultra-supercritical power plant \sep Exergy analysis \sep air preheat process \sep Thermodynamic analyses
 \end{keyword}
@@
 Coal is still the main fossil fuel resources for electricity production in the world according to~\cite{Ouedraogo2013Energy}. 
-In China, coal–fired power generation accounts for more than 70\% of the total electricity generation and subsequently contribute almost 50\%, 37\%, 33\% and 55\% to the SO$_X$, NO$_X$, dust and CO$_X$ emission volumes respectively~\cite{Zhang2010Analysis}
-Statics show that China has been the largest producer and consumer of energy all over the world since 2013 [??]. 
-For 2016 as a whole, Chinese coal production fell by 7.9\% and the price of steam coal increased by over 60\%[??]. 
+In China, coal–fired power generation accounts for more than 70\% of the total electricity generation and subsequently contribute almost 50\%, 37\%, 33\% and 55\% to the SO$_X$, NO$_X$, dust and CO$_X$ emission volumes respectively~\cite{Zhang2010Analysis}.
+Statics show that China has been the largest producer and consumer of energy all over the world since 2013~\cite{Petroleum2014BP}. 
+For 2016 as a whole, Chinese coal production fell by 7.9\% and the price of steam coal increased by over 60\%~\cite{Petroleum2017BP}. 
 Improve system efficiency and reducing coal consumption is still the main task of power plant design.
@@
 The double reheat USC unit is a new generation of USC unit which can improve the thermal performance compared with single reheat units~\cite{Zhao2017Exergy}. 
-According to Ref.~\cite{Yaxiu2013Thermal}, a double reheat unit with the inlet parameter 30.0\,MPa/600/620/620$^\circ$C improves the heat efficiency by 2.4\%-2.6\%, compared with a common used USC unit with the inlet parameter 25.0\,MPa/600/600$^\circ$C.
+According to Ref.~\cite{Zhao2017Exergy}, a double reheat unit with the inlet parameter 30.0\,MPa/600/620/620$^\circ$C improves the heat efficiency by 2.4\%-2.6\%, compared with a common used USC unit with the inlet parameter 25.0\,MPa/600/600$^\circ$C.
  The U.S. built the first double reheat unit with main parameter 34.4 MPa/649/566/566$^\circ$C in 1960s.
  Two 700 MW double reheat USC units in Japan were put into operation in 1990. 
- The Taizhou power plant in China began to build double reheat USC units in 2012, and put it into operation in 2015.
+ Since 2012, five  double reheat USC units  began to build in China, and three of them put it into operation in 2015.
  Over the past few decades, the double reheat USC units have received more and more attention for its rapid development all over the world.
-Zhao Z et al.~\cite{Zhao2017Exergy} studied the exergy distribution system for a 1000\,MW double reheat USC power plant and provided the main reasons that led to exergy destruction on the steam turbine.
+
+ Though the high live steam pressure and temperature of USC unit improves its efficiency, there are still some imperfections which limit the improvement of its performance . 
+In order to make an in-depth analysis of the system, Zhao Z et al.~\cite{Zhao2017Exergy} studied the exergy distribution system for a 1000\,MW double reheat USC power plant and provided the main reasons that led to exergy destruction on the steam turbine.
  Rashidi et al.~\cite{Rashidi2014Thermodynamic} investigated the thermodynamic analysis of a double reheat steam power plant.
@@
 
- Though the high live steam pressure and temperature of USC unit improves its efficiency, there are still some imperfections which limit the improvement of its performance .
+Compared with common USC system, double-reheat system has some characteristic problems, such as double reheat ratio chose and great superheat degree of the first several extractions.
+And some common problems, such as the high boiler exhaust temperature, which leads to unreasonable energy-level matching and great exergy destruction.
 
-For example, the double-reheat system causes great superheat degree of the first several extractions and the boiler exhaust temperature is extremely high, which leads to unreasonable energy-level matching and great exergy destruction.
+To chose a reasonable reheat parameters, Zhou et al.~\cite{Zhou2016Parametric} carried out parametric analysis and system optimization in double reheat ultra-supercritical power plants based on exergy analysis and economic analysis.
+The result shows reasonable reheat parameters and reheat stage number can improve  double reheat system's performance.
 
-To reduce the superheat degree of the extractions, Liu et al.
-[??] investigated the thermal performance of the steam and water cycle with single reheat after the installation of an additional outer steam cooler (AOC).
+To reduce the superheat degree of the extractions, Xu et al.~\cite{Xu2015Optimum} investigated the thermal performance of the steam and water cycle with single reheat after the installation of an additional outer steam cooler (AOC).
 Results show that the AOC is an effective method to reduce the superheat degree and improve the efficiency of the unit.
+Li et al.~\cite{Li2014Thermodynamic} proposed a system adopting 10-stage extractions and two outer steam coolers. 
+The result of thermodynamic and techno-economic analyses shows this system can reduce cost of electricity to 55.89 USD/MWh.
 Besides, Kjaer~\cite{Kjaer2010A} proposed a regenerative steam turbine to utilize the superheat degree of the extractions.
@@
 
-To reuse the energy of the exhaust flue gas Ref.~\cite{Xu2013Techno} proposed a low pressure economizer (LPE) based on the data of some 1000\,MW typical power generation units in China and four possible arrangements of the LPE installation were proposed to compare its energy-saving effects.
+To reuse the energy of the exhaust flue gas, Xu et al.~\cite{Xu2013Techno} proposed a low pressure economizer (LPE) based on the data of some 1000\,MW typical power generation units in China and four possible arrangements of the LPE installation were proposed to compare its energy-saving effects.
 Results indicated that LPE connected with higher temperature section of the condensate line brings more reduction of standard coal equivalent (SCE).
@@
 Results show that more than 30\,MW of the flue gas waste heat is recovered, which brings an improvement in gross efficiency by 0.53\% and 9.4\,MW extra output power.
-In Ref. [??], the air preheater is divided into two stages to reduce the temperature difference in heat transfer process.
+Xu et al~\cite{Xu2013A} made the air preheater divided into two stages to reduce the temperature difference in heat transfer process.
 Besides, a LPE is installed between the two air preheaters to obtain an appropriate flue gas temperature range.
@@
 A typical coal-fired double reheat USC power plant in operation is chosen as the reference unit.
-The parameter settings that maximize continuous power are 310\,bar/600$^\circ$Cfor the main steam, 610$^\circ$C for the reheat steam pressure, 33.5\% for the proportion of the single reheat steam pressure to the main steam pressure, and 33\% for the proportion of the double reheat steam pressure to the single reheat steam pressure[6].
-The output power of the double reheat unit under the condition of THA load is 1000 MW.
+The parameter settings that maximize continuous power are 310\,bar/600$^\circ$C for the main steam, 610$^\circ$C for the reheat steam pressure, 33.5\% for the proportion of the single reheat steam pressure to the main steam pressure, and 33\% for the proportion of the double reheat steam pressure to the single reheat steam pressure[6].
+The output power of the double reheat unit under the design condition is 1000 MW.
 The unit consists of one super high pressure turbine (VHP), one high pressure turbine (HP), one intermediate pressure turbine (IP), and two low pressure turbines (LP).
@@
 %从参考系统的锅炉虽然仍然采用Π型布置，但其内部受热面和传统一次再热锅炉有较大区别。
-Furnace layout shown in Fig~\ref{fig:boiler_surface}, the boiler furnace is composited by the membrane wall, along flue gas flow direction lays low-temperature superheater (Lts) screen tube, cold segment of high-temperature ﬁrst reheater (Csf), cold segment of high-temperature second reheater (Csf), High temperature super-heater (Hts), hot segment of high-temperature ﬁrst reheater (Hsf), hot segment of high-temperature second reheater (Hss).
-After Hsf and Hss the flue gas channel is divided into the front-duct flue and the back-duct flue. The front duct arranges low-temperature first reheater (Ltfr) and the front-duct economizerz 
-(%中，而水平烟道和竖井烟道中仅布置有空气预热设备。所以锅炉可以分成两部分:炉膛内完成水/蒸汽吸热的boiler，和尾部烟道内 完成空气预热的APH。Feco), the back duct arranges a low-temperature second reheater (Ltsr) and back-duct economizer (Beco).
-The rear flue is equipped with an air preheater(APH).
-% 从锅炉受热面布置可以看出，锅炉主要受热面布置在炉膛之
+Furnace layout shown in Fig~\ref{fig:boiler_surface}, the boiler furnace is composited by the membrane wall, along flue gas flow direction lays low-temperature superheater (Lts) screen tube, cold segment of high-temperature first reheater (Csf), cold segment of high-temperature second reheater (Csf), High temperature super-heater (Hts), hot segment of high-temperature first reheater (Hsf), hot segment of high-temperature second reheater (Hss).
+After Hsf and Hss the flue gas channel is divided into the front-duct flue and the back-duct flue. The front duct arranges low-temperature first reheater (Ltfr) and the front-duct economizers.
+APH is arranged in vertical shaft.
+
+From the arrangement of heating surfaces of boiler, it can be seen that most heating surfaces of boiler is arranged in the furnace, while the horizontal flue and vertical shaft are only equipped with air preheating equipment.
+So the boiler can be divided into two parts: the boiler achieving heat absorption of water/steam in the furnace, and the APH to complete the air preheating.
 \begin{figure}[htbp]
@@
 \end{table}
-Table~\ref{tab:reheater parameter}gives the temperature profiles and exergy efficiency of regenerative heaters and the air preheater, revealing the energy match level of heat exchangers.
-For the air preheater, the temperature of flue gas at the inlet of the air preheater is 376$^\circ$C under THA condition, while the temperature of the air to be heated by the flue is 23$^\circ$C, leading to the exergy destruction of 27.17\,MW.
-The temperature difference of the air preheater is calculated to be 72$^\circ$C, and average temperature of the air is 177$^\circ$C, causing the exergy efficiency of 77.16\%.
+
 \begin{table}[htbp]
@@
 
-Compared with the air preheater, the regenerative heaters have lower logarithm mean temperature difference (LMTD).
+Table~\ref{tab:reheater parameter} gives the temperature profiles and exergy efficiency of regenerative heaters and the air preheater, revealing the energy match level of heat exchangers.
+For the APH, the temperature of flue gas at the inlet is 376$^\circ$C under design condition, while the temperature of the air to be heated by the flue is 23$^\circ$C.
+The logarithm mean temperature difference (LMTD) of the APH is calculated to be 72$^\circ$C.
+Compared with the air preheater, the regenerative heaters have lower LMTD.
 However, it is found that the temperature difference between the hot and cold stream at the inlet high temperature regenerative heaters is also relatively large, which causes irreversible loss. 
@@
 The throttling of the first extraction will certainly cause extra irreversible loss.
+
 \subsection{Proposal of a novel system with EAPH and LPE}
@@
 %添加为什么进行这种设计的解释，为什么设置LPE AOC APH的级数
-\textcolor{red}{The  layout of the optimization system is presented in Fig~\ref{fig:novel_system}.
-In the optimization system, the air is not heated by flue gas in the conventional air preheater, and 8 new air preheaters (APH1\~APH8) using several extractions to heat the air is adopted.
+
+To reduce the energy loss caused by APH, a novel system is proposed, in which air is not heated by flue gas in the conventional air preheater, and 8 turbine-extraction-heated air preheaters (EAPH1-EAPH8) are adopted.
+The  layout of the optimization system is presented in Fig.~\ref{fig:novel_system}.
+
 The new air preheater is similar with regenerative heaters in function.
-As shown in Fig~ the extracted steam is sent to the regenerative heater to heat the condensate or feedwater, and then the drainage from the air preheater joins with that of corresponding regenerative heater.
-It should be mentioned that not all the extractions are available for air heating
-For the last two stage extractions, their pressure is much lower than barometric pressure which makes it extremely difficult to maintain such low pressure environment inside the heat exchangers, and APH8 shall be shut down under low load for the same reason.
-Besides, to reduce the superheat degree of extractions entering the heat exchangers and to improve the air temperature, four additional outer steam coolers (AOC1- AOC4) are installed at the outlet of APH1.
-Since extractions from the 2nd to the 5th have superheat degree, they are sent to AOCs in the order of temperature level.
+As shown in Fig.~\ref{fig:extraction_heat_APH} the extracted steam is sent to the regenerative heater to heat the condensate or feedwater, and then the drainage from the air preheater joins with that of corresponding regenerative heater.
+It should be mentioned that not all the extractions are available for air heating.
+The last two stage extractions' pressure are much lower than barometric pressure which makes it extremely difficult to maintain such low pressure environment inside the heat exchangers, and APH8 shall be shut down under low load for the same reason.
+Besides, to reduce the superheat degree of extractions entering the heat exchangers and to improve the air temperature, four additional outer steam coolers (AOC1-AOC4) are installed at the air side outlet of APH1.
+Since extractions from the 2nd to the 5th have great superheat degree, they are sent to AOCs in the order of temperature level.
 For example, the 2nd extraction has the highest temperature, and is applied to heat the air in the 1st AOC, and then the cooled steam from AOC1 is sent to HRH2 and air APH2 to heat the water and air respectively.
-}
 
@@
 \end{figure}
+
+Cause removing of the APH originally installed in the vertical shaft, the flue gas's heat needs to be absorbed by other means.
 As shown in Fig~\ref{fig:novel_system}, the flue gas at the outlet of economizer is utilized to heat the condensate and feed water by four LPEs, which are paralleled to HRH2, HRH4, LRH6, and LRH8 respectively.
 Part of the condensate and feed water at the inlet of regenerative heater are sent to the LPE, then the heated water join with the main feedwater/condensate. 
-Considering the acid dew point temperature, the flue gas temperature at the outlet of the last LPE is set 95$^	rc$C. 
+Considering the acid dew point temperature, the flue gas temperature at the outlet of the last LPE is set 95$^\circ$C. 
 The temperature of heated water from LPE is set little higher than the feedwater from the corresponding regenerative heater.%
@@
 \label{ssub3:modle description}
-\textcolor{red}{!novel model established based on the reference which parameters change and which not! }
 %对模型中如何基于现有系统进行的改造，和哪些数据不发生变化进行说明
 %添加模型中基本部件的特性 添加个表格
-In this paper, the thermodynamic cycle of the thermal system under different loads are simulated with EBSILON® Professional for its flexibility and level of detail. 
-EBSILON is a power plant simulation tool which can calculate thermodynamic quantities. 
+In this paper, the thermodynamic cycle of the thermal system under different loads are simulated with EBSILON® Professional.
+EBSILON is a power plant simulation tool which can calculate thermodynamic quantities and widely used in power plant system model establishment and analysis~\cite{Li2015Integrated,Yao2017Multi}. 
 The simulation model gives the detailed data with high degree of reliability to calculate the thermodynamic state.
-EBSIOLON's simulation and parameter calculation of the equipment is based on experimental characteristics of units during the process of modeling design and off-design conditions.
-However, only some characteristic curves of turbine can actually be obtained, while boiler and heat exchanger data cannot be obtained, which can only use the system built-in data as an alternative.
+While use this software simulating systems, main equipments work flow parameters and some basic properties need to be settled.
+Cause designed based on the reference system, the novel system's main input parameters(such as live steam parameters, fist/second reheat steam parameters and turbine extractions parameters) keeps the same as reference system, which can be find in Table~\ref{tab:ref input} and Table~\ref{table:extractions_parameter}.
+Based on the practice, the upper temperature differences of novel systems' LPE, AOC and EAPH are settled to 30℃, 20℃ and 5℃. 
+And other main components model details are give in Table~\ref{table:model_details}.
+
+\begin{table}
+\caption{Model details of main components}
+\label{table:model_details}
+\begin{centering}
+\begin{tabular}{ll}
+\toprule 
+Components 				& Model details\tabularnewline
+\midrule
+Boiler         			& Economizer out let flu temperature =376\textcelsius ;\tabularnewline
+ 						& Slag temperature =850\textcelsius ;\tabularnewline
+ 						& Combustion efficiency =0.99.\tabularnewline
+Turbine 				& Isentropic efficiencies are from 0.83 to 0.93, \tabularnewline
+ 						& calculated from thermal equilibrium diagram.\tabularnewline
+Condenser 				& Upper terminal temperature difference=5\textcelsius .\tabularnewline
+Regenerative reheats 	& Upper terminal temperature differences are from -1.7\textcelsius{}to 2.2\textcelsius , \tabularnewline
+ 						& calculated from thermal equilibrium diagram.\tabularnewline
+\bottomrule
+\end{tabular}
+\par\end{centering}
+\end{table}
+
+On the off-design conditions, EBSIOLON's simulation and parameter calculation of the equipment, such as turbine, is based on experimental characteristics of units.
+However, only turbine's off-design characteristic curves can actually be obtained,and boiler's and heat exchangers' data can not be gotten.
+It has to be replaced by built-in data.
 It’s needed to assume that the difference between the built-in data and the actual data to meet the error requirements.
@@
 \item The thermal efficiency of the equipment is calculated from the thermal balance of the input and output parameters of the components, assuming that the calculation error requirement can be met.
-\item According to the heat map, set the upper and lower end difference of the heat exchanger as a fixed value, and do not change among different condition.
+\item According to the heat map, set the upper and lower end difference of the heat exchanger as a fixed value, and do not change during different load conditions' simulation.
 \item Do not take the pips' complexity and equipment’s installation difficulty of the novel system as consideration.
 \end{enumerate}
+More detail descriptions of the thermaldynamic model of involved components can be found in Ref.~\cite{Yao2017Multi}.
+
+\begin{table}
+\caption{The turbine extractions parameters on design condition}
+\label{table:extractions_parameter}
+\begin{centering}
+\begin{tabular}{cccccc}
+\toprule 
+\multirow{2}{*}{Extractions} & Pressure & Temperature & \multirow{2}{*}{Extractions} & Pressure & Temperature\tabularnewline
+ & (bar) & (℃) &  & (bar) & (℃)\tabularnewline
+\midrule
+1st & 107.89  & 429.00 & 6th & 7.15  & 394.01 \tabularnewline
+2nd & 61.89 & 528.30  & 7th & 3.90  & 313.17\tabularnewline
+3rd & 34.34 & 435.20  & 8th & 1.23  & 191.84\tabularnewline
+4th & 17.56  & 526.55  & 9th & 0.57  & 116.61\tabularnewline
+5th & 10.35  & 447.37 & 10th & 0.21 & 62.57\tabularnewline
+\bottomrule
+\end{tabular}
+\par\end{centering}
+\end{table}
 
@@
 \begin{equation}
-\dot{X}=\dot{m}e=\dot{m}\left[h-h_{0}-T_{0}\left(s-s_{0}\right)\right]{}
+\dot{X}=\dot{m}x=\dot{m}\left[h-h_{0}-T_{0}\left(s-s_{0}\right)\right]{}
 \end{equation}
@@
 Where LHV refer to lower heating value of fuel, C, H, O, N refer to mass fractions of carbon, hydrogen, oxygen, nitrogen by element analysis.
-More details of power plant equipments' exergy  efficiency calculation can be found in Ref~\cite{G2016Exergy}
+More details of power plant equipments' exergy  efficiency calculation can be found in Ref.~\cite{G2016Exergy}
 
 In order to clearly analyze the effect of system optimization, this paper divides the double-reheat USC system into four main subsystems and a sum of all other equipments, valves and pips named "other".
-The four main subsystems are boiler with out APH, turbines, air preheat subsystem, regenerative subsystem.
-The equations mentioned above can also be used into of exergy analysis these four main subsystems.
-For the "other" part, this paper used counter balance analysis method to calculate its exergy destruction rate, which means subtract the share of the four main subsystems from the total.
+The four main subsystems are : boiler with out APH, turbines, air preheat subsystem and regenerative subsystem.
+The equations mentioned above can also be used into exergy analysis of these four main subsystems.
+For the "other" part, this paper used counter balance analysis method to calculate its exergy destruction rate, which means subtract the share of the four main subsystems from the total exergy destruction.
 The exergy destruction rate can be calculated by using equation as follows:
@@
 \end{equation}
-
-%系统主要4个子系统和other部分的用损失如何计算，主要提出other包含的内容和反平衡计算方法
 
@@
 \end{figure}
-% 在空气预热开始时，在第8级空预器出换热量和换热温差均较大，使之成为用损最大的换热器，随着空气预热的继续进行，换热温差降低，低1-7级空预器的用损减小。当空气进入AOC时，由于抽汽温度较高，所以换热温差增大，但由于换热量较小，造成在AOC中的用损失较小。
 
@@
 Except EAPH8，the exergy efficiency of EAPHs and AOCs is higher than 82\%, and the APH8 has the greatest exergy loss and lowest efficiency of all the air preheaters. 
-It also indicates that, although the AOCs have large heat transfer temperature difference, their exergy efficiencies are still high and low exergy destruction rate, which have less impact on the total exergy efficiency.
-Combing Fig.~\ref{fig:APH_temper_compare} andFig.~\ref{fig:novel_APH_exergy},the reason why the novel system's air preheat subsystem have a higher exergy efficiency and lower exergy destruction rate can be drawn.
-For the novel system's air preheat subsystem, the improvement in performance results from lower heat transfer temperature difference and reasonable extractions' superheat degree using.
+According with Fig.~\ref{fig:APH_temper_compare}, the heat transfer temperature difference of EAPH8 is 26.95 $^\circ$C,and it has a larger heat exchanging quantity, both of which cause higher exergy destruction and exergy efficiency.
+It also indicates that, although the AOCs have large heat transfer temperature difference, their exergy efficiencies are still high and low exergy destruction rate.
+
+Combing Fig.~\ref{fig:APH_temper_compare}  .~\ref{fig:novel_APH_exergy},the reason why the novel system's air preheat subsystem have a higher exergy efficiency and lower exergy destruction rate can be drawn，that the novel system's air preheat subsystem has a lower heat transfer temperature difference and reasonable extractions' superheat degree using.
 
@@
 %插入对于回热系统的分析
-
+% 新系统总体用损失有所降低，内部损失分配发生了较大变化，deh损失由---到---，加热器由---到---。对于加热器和deh，由图（加入）于换热器其效率不变，但进入加热器工质减少导致损失减少。减少的水由lpe加热，lpe换热由图所示，效率较高，设计合理
 % The total exergy loss of the LPEs is 10.73MW, and the overall exergy efficiency is 91.62%, much higher than that of air preheater.
@@
 
+The regenerative subsystem of novel system uses LEPS paralleled connected with EAPH to absorb economizer outlet flu heat, and eliminates the AOCs originally used to heat feedwater.
+LPE inlet water are heated to the outlet temperature of corresponding outlet temperature of regenerative heater to mix up.
+With the extractions' parameters keeping still, the average heat transfer temperature difference of regenerative heaters change little.
+So their exergy efficiency keeps the same with reference system.
+
+Fig.~\ref{fig:regenerative_subsys_compare} shows the regenerative subsystem's exergy destruction rate distribution comparison between the two systems.
+It can be found that the novel system' exergy destruction rate has a decrease and great changes have taken place in the destruction's distribution.
+In consequence of the follow diverting effects of LEPs, the exergy destruction rate of regenerative reheaters and DEA changes from 20.16 MW to 11.303 MW.
+The LEPs exergy destruction rate reach to 10.25 MW, and Fig.~\ref{fig:LPE_exergy_LMDT} shows the LEPs' exergy efficiency and heat transfer LMTD.
+ As shown in Fig.~\ref{fig:LPE_exergy_LMDT}, the highest efficiency one is LPE1 with 93.50\%, and the lowest efficiency one is LPE4 with 87.44\%. 
+The LEPs' overall exergy efficiency is 91.62\%, much higher than that of flu-air heat transfer of reference system, and the temperature difference of the LPEs is between 23$^\circ$C to 42$^\circ$C.
+
 \begin{figure}[htbp]
@@
 \end{figure}
-%对锅炉、汽轮机、和other系统的用效率进行分析
 

### 2018-02-04 article.tex
基本修改完成 提交杨涛老师

@@
 \usepackage{caption} 
-%\renewcommand{\captionlabeldelim}{.}
 \usepackage{color}%临时添加,
@@
 
-% \usepackage{graphicx}%插入图片
+ \usepackage{amsmath}%
 
-% \usepackage{amssymb}%数学符号
+ \usepackage{lineno}%
 
-% \usepackage{amsthm}%数学定理
+\usepackage{bm}%
 
- \usepackage{amsmath}%数学公式、矩阵、积分求和等
+\captionsetup[figure]{font=small,labelfont=bf,labelsep=period}%
 
-% \usepackage{lineno}%显示行号
-
-% \usepackage{txfonts}%默认字体times new roman
-
-% \usepackage{enumitem}%项目编号
-
-% \usepackage{multirow}%多行合并
-
-% \usepackage{caption}%改变图表标题
-
-% \usepackage{array}%调用公式宏包的命令应放在调用宏包命令之前，也能控制表格
-
-% \usepackage{booktabs}%调整表格线与上下内容的间隔
-
-% \usepackage{longtable}%调用跨页表格
-
-\usepackage{bm}%数学字体加粗
-
-% \usepackage{setspace}%调整一段文字的行间距
-
-% \usepackage{natbib}%参考文献管理包​
-% \biboptions{sort&compress}%参考文献可以压缩显示比例​
-
-% \allowdisplaybreaks[4]%允许公式跨页
-
-\captionsetup[figure]{font=small,labelfont=bf,labelsep=period}%修改标题文字格式
-
-\renewcommand{\figurename}{Fig.}%修改标题样式
-
-%\newcommand{\tabincell}[2]{}%让表格内容自动换行，但仍然需要用到换行\\
+\renewcommand{\figurename}{Fig.}%
 
@@
 Moreover, the novel system can still has advantages in coal saving under partial load condition.
+Results indicate that the novel system could improves the performance of double-reheat USC unit and may provide a theoretical basis for its optimization.
 
@@
 
+\begin{multicols}{2}
 \printnomenclature[1.5cm]{}
+\end{multicols}
 
@@
 
-Due to arrangement of boiler heating surface and design of regenerative system belong to deferent research area, researches concentrate more on the optimization of these two systems respectively, and ignored the joint optimization of boiler tail flue heating surface and regenerative system to achieve energy cascade utilization and improve system efficiency.
-To reduce both systems' exergy loses, a theoretical optimization design of cascaded utilization of energy for a 1000\,MW double reheat USC unit (novel system) is proposed.
-Variations and energy saving effects of a double reheat ultra-supercritical thermal system (reference system) and the novel system are analyzed to evaluate their performance.
+Due to  boiler design and thermal system design belong to deferent research area, boiler has been studied as a whole and ignored the joint optimization of boiler heat transfer process and regenerative process.
+
+In this paper, a novel system based on a 1000\,MW double reheat USC reference system  is proposed to realize boiler and regenerative system energy cascade utilization. 
+The novel system realized reasonable temperature matching of flue gas, air, extraction steam and condensate water by using turbine-extraction-heating air preheaters (EAPHs) and LPEs.
+Specifically, the main works of this study include: (1)Modeling the novel system and reference system with EBSILON® Professional; (2) Using exergy analysis to compare both systems' exergy efficiency , exergy destruction distribution and subsystems performance change;(3) Analyzing both systems' thermal performance under off-design conditions.
+
 \section{System optimization of double reheat USC system}
@@
 A typical coal-fired double reheat USC power plant in operation is chosen as the reference unit.
-The parameter settings that maximize continuous power are 310\,bar/600$^\circ$C for the main steam, 610$^\circ$C for the reheat steam pressure, 33.5\% for the proportion of the single reheat steam pressure to the main steam pressure, and 33\% for the proportion of the double reheat steam pressure to the single reheat steam pressure[6].
-The output power of the double reheat unit under the design condition is 1000 MW.
-The unit consists of one super high pressure turbine (VHP), one high pressure turbine (HP), one intermediate pressure turbine (IP), and two low pressure turbines (LP).
-10-stage regenerative system with four high pressure regenerative heaters (HRH), five low pressure regenerative heaters (LRH), and one deaerator (DEA) are adopted.
-Besides two additional outer steam coolers (AOC1, AOC2) are used to cool two extractions due to its high super-heating degree.
+The parameter settings at maximize continuous power are 310\,bar/600$^\circ$C for the main steam, 610$^\circ$C for the reheat steam pressure, 33.5\% for the proportion of the single reheat steam pressure to the main steam pressure, and 33\% for the proportion of the double reheat steam pressure to the single reheat steam pressure~\cite{Zhao2017Exergy}.
+The output power of the reference system under the design condition is 1000 MW.
+The unit consists of one super high pressure cylinder (VHP), one high pressure cylinder (HP), one intermediate pressure cylinder (IP), and two low pressure cylinders (LPs).
+Regenerative system with four high pressure regenerative heaters (HRHs), five low pressure regenerative heaters (LRHs), and one deaerator (DEA) are adopted.
+Besides, two additional outer steam coolers (AOC1, AOC2) are used to cool two extractions due to its high super-heating degree.
 The exhaust steam pressure of the steam turbine is set 4.5\,kPa.
-The simplified schematic of the unit is presented in Fig~\ref{fig:reference_system}.
+The simplified schematic of it is presented in Fig~\ref{fig:reference_system}.
 
@@
 %从参考系统的锅炉虽然仍然采用Π型布置，但其内部受热面和传统一次再热锅炉有较大区别。
-Furnace layout shown in Fig~\ref{fig:boiler_surface}, the boiler furnace is composited by the membrane wall, along flue gas flow direction lays low-temperature superheater (Lts) screen tube, cold segment of high-temperature first reheater (Csf), cold segment of high-temperature second reheater (Csf), High temperature super-heater (Hts), hot segment of high-temperature first reheater (Hsf), hot segment of high-temperature second reheater (Hss).
-After Hsf and Hss the flue gas channel is divided into the front-duct flue and the back-duct flue. The front duct arranges low-temperature first reheater (Ltfr) and the front-duct economizers.
-APH is arranged in vertical shaft.
+The system's boiler heat transfer surfaces arrangement is shown in Fig~\ref{fig:boiler_surface}. 
+The boiler furnace is composited by the membrane wall, along flue gas flow direction lays low-temperature superheater (Lts) screen tube, cold segment of high-temperature first reheater (Csf), cold segment of high-temperature second reheater (Css), High temperature super-heater (Hts), hot segment of high-temperature first reheater (Hsf), hot segment of high-temperature second reheater (Hss).
+After Hsf and Hss the flue gas channel is divided into the front-duct flue and the back-duct flue.
+The front duct arranges low-temperature first reheater (Ltfr) and the front-duct economizer (Feco).
+The back duct arranges low-temperature second reheater (Ltsr) and the back-duct economizer (Beco).
+(air preheater)APH is arranged in vertical shaft.
 
-From the arrangement of heating surfaces of boiler, it can be seen that most heating surfaces of boiler is arranged in the furnace, while the horizontal flue and vertical shaft are only equipped with air preheating equipment.
-So the boiler can be divided into two parts: the boiler achieving heat absorption of water/steam in the furnace, and the APH to complete the air preheating.
+From the arrangement of heating transfer surfaces, the boiler can be divided into two parts: the part achieving heat absorption of water/steam process in the furnace, and the APH to complete the air preheat process.
+It can be seen that most heating surfaces of boiler is arranged in the furnace, while the horizontal flue and vertical shaft are only equipped with APH.
+So the horizontal flue and vertical shaft have sufficient space to install other equipments.
+
 \begin{figure}[htbp]
 \centering
-\includegraphics[width=0.5\textwidth]{fig/boiler_surface}
-\caption{Boiler internal heat exchangers layout} 
+\includegraphics[width=0.9\textwidth]{fig/boiler_surface.png}
+\caption{Boiler heat transfer surfaces layout} 
 \label{fig:boiler_surface}
@@
 
+Table~\ref{tab:reheater parameter} gives the temperature profiles of regenerative heaters and the air preheater, revealing their energy match level.
+For the APH, the temperature of flue gas at the inlet is 376$^\circ$C under, while the temperature of the air to be heated by the flue is 23$^\circ$C.
+The logarithm mean temperature difference (LMTD) of the APH is calculated to be 72$^\circ$C.
+Compared with the air preheater, the regenerative heaters have much lower LMTD from 6.88$^\circ$C-15.87$^\circ$C.
+According to the second law of thermodynamics, the bigger the temperature difference the greater the irreversible loss.
+So it needs to optimize the air preheat process to reduce energy loss of the system.
+AOC1 and AOC2 face the same problem of high LMTD compared with RHs.
+It's better to find a way to make double reheat USC system's high temperature extractions a reasonable arrangement.
+
 \begin{table}[htbp]
-\caption{Fluid parameters of heat exchangers and air preheater}
+\caption{Fluid parameters of regenerative heaters and air preheater}
 \label{tab:reheater parameter}
@@
 
-Table~\ref{tab:reheater parameter} gives the temperature profiles and exergy efficiency of regenerative heaters and the air preheater, revealing the energy match level of heat exchangers.
-For the APH, the temperature of flue gas at the inlet is 376$^\circ$C under design condition, while the temperature of the air to be heated by the flue is 23$^\circ$C.
-The logarithm mean temperature difference (LMTD) of the APH is calculated to be 72$^\circ$C.
-Compared with the air preheater, the regenerative heaters have lower LMTD.
-However, it is found that the temperature difference between the hot and cold stream at the inlet high temperature regenerative heaters is also relatively large, which causes irreversible loss. 
-To reduce the superheat degree of the 2nd and 4th extractions and to heat feedwater, two additional outer steam coolers are installed.
-Results show that the inlet temperature difference of HRH2 and HRH4 is greatly reduced, and the exergy efficiency is improved correspondingly.
-However, the inlet temperature difference between the cold and hot stream of other high temperature regenerative heaters remains very high.
-Moreover, because of the material restriction of the water wall, the temperature of feedwater at the inlet of boiler is restricted to 315$^\circ$C. 
-In the reference system, the first extraction has to be throttled to ensure the temperature of feedwater not exceeding the restriction.
-The pressure of the first extraction is throttled from 106.70 bar to 88.56 bar, and the temperature is decreased from 425.60$^\circ$C to 413.77$^\circ$C.
-The throttling of the first extraction will certainly cause extra irreversible loss.
+\subsection{Proposal of a novel system with EAPHs and LPEs}
+\label{sub2:prop novel sys}
 
-\subsection{Proposal of a novel system with EAPH and LPE}
-\label{sub2:prop novel sys}
-%添加为什么进行这种设计的解释，为什么设置LPE AOC APH的级数
-
-To reduce the energy loss caused by APH, a novel system is proposed, in which air is not heated by flue gas in the conventional air preheater, and 8 turbine-extraction-heated air preheaters (EAPH1-EAPH8) are adopted.
+To reduce the energy loss caused by APH, a novel system is proposed, in which air is not heated by flue gas in the conventional air preheater, but 8 turbine-extraction-heated air preheaters (EAPH1-EAPH8).
 The layout of the optimization system is presented in Fig.~\ref{fig:novel_system}.
 
-The new air preheater is similar with regenerative heaters in function.
-As shown in Fig.~\ref{fig:extraction_heat_APH} the extracted steam is sent to the regenerative heater to heat the condensate or feedwater, and then the drainage from the air preheater joins with that of corresponding regenerative heater.
+As shown in Fig.~\ref{fig:extraction_heat_APH}, the extracted steam divides into two parts, one is sent to the regenerative heater to heat the condensate or feedwater and the other one is sent to corresponding EAPH to heat air.
+The drainage from the air preheater joins with that of corresponding regenerative heater after finishing heat transfer .
+Steam distribution ratio is determined according to EAPH upper terminal temperature difference settled in the system.
 It should be mentioned that not all the extractions are available for air heating.
-The last two stage extractions' pressure are much lower than barometric pressure which makes it extremely difficult to maintain such low pressure environment inside the heat exchangers, and APH8 shall be shut down under low load for the same reason.
-Besides, to reduce the superheat degree of extractions entering the heat exchangers and to improve the air temperature, four additional outer steam coolers (AOC1-AOC4) are installed at the air side outlet of APH1.
-Since extractions from the 2nd to the 5th have great superheat degree, they are sent to AOCs in the order of temperature level.
-For example, the 2nd extraction has the highest temperature, and is applied to heat the air in the 1st AOC, and then the cooled steam from AOC1 is sent to HRH2 and air APH2 to heat the water and air respectively.
+The last two stage extractions' pressure are much lower than barometric pressure which has a great risk of air leakage into the steam, and APH8 shall be shut down under low load for the same reason.
+
+The AOCs in the reference system are designed to heat feedwater.
+Although AOC inlet steam has a great supper heat degree, the small heat exchanged makes feedwater have little temperature rise.
+So the LMTD is very high in AOCs.
+
+To reduce rise AOCs' exergy efficiency and the superheat degree of extractions entering the heat exchangers, four additional outer steam coolers (AOC1-AOC4) are installed at the air side outlet of EAPH1.
+Air side outlet of EAPH1 will sent to boiler as secondary air, which has small mass quantity and lower heat capacity compared with feedwater. 
+So the secondary air temperature can make a remarkable rise, and LMTD of AOCs can get down.
+Extractions from the 2nd to the 5th have very high temperature and great superheat degree, they are sent to AOCs in the order of temperature level.
+For example, the 2nd extraction has the highest temperature, and is applied to heat the air in the 1st AOC, and then the cooled steam from AOC1 is sent to HRH2 and air EAPH2 to heat the water and air respectively.
 
@@
 \centering
-\includegraphics[width=0.3\textwidth]{fig/extraction_heat_APH}%extraction_heat_APH
-\caption{Process flow diagram of RH and APH} 
+\includegraphics[width=0.3\textwidth]{fig/extracion_heat_APH.png}%extraction_heat_APH
+\caption{Process flow diagram of RH and EAPH} 
 \label{fig:extraction_heat_APH}
@@
 As shown in Fig~\ref{fig:novel_system}, the flue gas at the outlet of economizer is utilized to heat the condensate and feed water by four LPEs, which are paralleled to HRH2, HRH4, LRH6, and LRH8 respectively.
-Part of the condensate and feed water at the inlet of regenerative heater are sent to the LPE, then the heated water join with the main feedwater/condensate. 
-Considering the acid dew point temperature, the flue gas temperature at the outlet of the last LPE is set 95$^\circ$C. 
-The temperature of heated water from LPE is set little higher than the feedwater from the corresponding regenerative heater.%
+Part of the condensate and feed water at the inlet of regenerative heater are sent to the LPE, then the heated water join with corresponding regenerative heater's outlet water. 
+Considering the acid dew point temperature, the flue gas temperature at the outlet of the last LPE can be set 95$^\circ$C.
 
@@
 While use this software simulating systems, main equipments work flow parameters and some basic properties need to be settled.
-Cause designed based on the reference system, the novel system's main input parameters(such as live steam parameters, fist/second reheat steam parameters and turbine extractions parameters) keeps the same as reference system, which can be find in Table~\ref{tab:ref input} and Table~\ref{table:extractions_parameter}.
-Based on the practice, the upper temperature differences of novel systems' LPE, AOC and EAPH are settled to 30℃, 20℃ and 5℃. 
+Cause designed based on the reference system, the novel system's main input parameters(such as live steam parameters, fist/second reheat steam parameters and turbine extractions parameters) keeps the same as it, which can be find in Table~\ref{tab:ref input} and Table~\ref{table:extractions_parameter}.
+Based on the practice, the upper temperature differences of novel systems' LPE, AOC and EAPH are settled to 30$^\circ$C, 20$^\circ$C and 5$^\circ$C. 
 And other main components model details are give in Table~\ref{table:model_details}.
@@
 \midrule
-Boiler         			& Economizer out let flu temperature =376\textcelsius ;\tabularnewline
+Boiler         			& Economizer out let flue gas temperature =376\textcelsius ;\tabularnewline
  						& Slag temperature =850\textcelsius ;\tabularnewline
- 						& Combustion efficiency =0.99.\tabularnewline
+ 						& Combustion efficiency = 0.99.\tabularnewline
 Turbine 				& Isentropic efficiencies are from 0.83 to 0.93, \tabularnewline
  						& calculated from thermal equilibrium diagram.\tabularnewline
-Condenser 				& Upper terminal temperature difference=5\textcelsius .\tabularnewline
-Regenerative reheats 	& Upper terminal temperature differences are from -1.7\textcelsius{}to 2.2\textcelsius , \tabularnewline
- 						& calculated from thermal equilibrium diagram.\tabularnewline
+Condenser 				& Upper terminal temperature difference = 5\textcelsius .\tabularnewline
+Regenerative reheats 	& Upper terminal temperature differences are from -1.7\textcelsius{}  \tabularnewline
+ 						& to 2.2\textcelsius ,calculated from thermal equilibrium diagram.\tabularnewline
 \bottomrule
@@
 Usually, exergy destruction and exergy efficiency are chosen as evaluation indices of the thermal system or an individual component, 
-The general exergy balance of component can be expressed in the following form:
+The general exergy balance of component or system can be expressed in the following form:
 \begin{equation}
 \label{equation:1}
-\dot{I}=\sum\dot{X}{}_{in}-\sum\dot{X}{}_{out}+\sum\dot{W}{}_{in}-\sum\dot{W}{}_{out}
+\dot{I}=\sum\dot{Ex}{}_{in}-\sum\dot{Ex}{}_{out}+\sum\dot{W}{}_{in}-\sum\dot{W}{}_{out}
 \end{equation}
@@
 \label{equation:2}
-\eta=\frac{\dot{X}{}_{earned}}{\dot{X}{}_{cost}}
+\eta_{\uppercase\expandafter{\romannumeral2}}=\frac{\dot{Ex}{}_{earned}}{\dot{Ex}{}_{cost}}
 \end{equation}
@@
 \begin{table}
-\caption{Exergy analysis equations for plant components}
+\caption{Exergy analysis equations for power plant components}
 \label{tab:exergy equation}
@@
 \midrule
-Boiler & $\dot{I}_{boiler}=\dot{X}{}_{fuel}+\dot{X}{}_{in}-\dot{X}{}_{out}$ & $\eta_{\uppercase\expandafter{\romannumeral2},boiler}=\frac{\dot{X}{}_{out}-\dot{X}{}_{in}}{\dot{X}{}_{fuel}}$\tabularnewline
-Pump & $\dot{I}_{pump}=\dot{X}{}_{in}-\dot{X}{}_{out}+\dot{W}{}_{pump}$ & $\eta_{\uppercase\expandafter{\romannumeral2},pump}=1-\frac{\dot{I}_{pump}}{\dot{W}{}_{pump}}$\tabularnewline
-Heater & $\dot{I}_{heater}=\dot{X}{}_{in}-\dot{X}{}_{out}$ & $\eta_{\uppercase\expandafter{\romannumeral2},heater}=1-\frac{\dot{I}_{heater}}{\dot{X}{}_{in}}$\tabularnewline
-Turbine & $\dot{I}_{turbine}=\dot{X}{}_{in}-\dot{X}{}_{out}-\dot{W}{}_{el}$ & $\eta_{\uppercase\expandafter{\romannumeral2},turbine}=1-\frac{\dot{I}_{turbine}}{\dot{X}{}_{in}-\dot{X}{}_{out}}$\tabularnewline
-Condenser & $\dot{I}_{condenser}=\dot{X}{}_{in}-\dot{X}{}_{out}+\dot{W}{}_{p}$ & $\eta_{\uppercase\expandafter{\romannumeral2},boiler}=\frac{\dot{X}{}_{out}}{\dot{X}{}_{in}+\dot{W}{}_{p}}$\tabularnewline
-Cycle &$\dot{I}_{total}=\dot{X}{}_{fuel}-\dot{W}{}_{net,out}$ & $\eta_{\uppercase\expandafter{\romannumeral2},total}=\frac{\dot{W}{}_{net,out}}{\dot{X}{}_{fuel}}$\tabularnewline
+Boiler & $\dot{I}_{boiler}=\dot{Ex}{}_{fuel}+\dot{Ex}{}_{in}-\dot{Ex}{}_{out}$ & $\eta_{\uppercase\expandafter{\romannumeral2},boiler}=\frac{\dot{Ex}{}_{out}-\dot{Ex}{}_{in}}{\dot{Ex}{}_{fuel}}$\tabularnewline
+Pump & $\dot{I}_{pump}=\dot{Ex}{}_{in}-\dot{Ex}{}_{out}+\dot{W}{}_{pump}$ & $\eta_{\uppercase\expandafter{\romannumeral2},pump}=1-\frac{\dot{I}_{pump}}{\dot{W}{}_{pump}}$\tabularnewline
+Heater & $\dot{I}_{heater}=\dot{Ex}{}_{in}-\dot{Ex}{}_{out}$ & $\eta_{\uppercase\expandafter{\romannumeral2},heater}=1-\frac{\dot{I}_{heater}}{\dot{Ex}{}_{in}}$\tabularnewline
+Turbine & $\dot{I}_{turbine}=\dot{Ex}{}_{in}-\dot{Ex}{}_{out}-\dot{W}{}_{el}$ & $\eta_{\uppercase\expandafter{\romannumeral2},turbine}=1-\frac{\dot{I}_{turbine}}{\dot{Ex}{}_{in}-\dot{Ex}{}_{out}}$\tabularnewline
+Condenser & $\dot{I}_{condenser}=\dot{Ex}{}_{in}-\dot{Ex}{}_{out}+\dot{W}{}_{pump}$ & $\eta_{\uppercase\expandafter{\romannumeral2},boiler}=\frac{\dot{Ex}{}_{out}}{\dot{Ex}{}_{in}+\dot{W}{}_{pump}}$\tabularnewline
+Cycle &$\dot{I}_{total}=\dot{Ex}{}_{fuel}-\dot{W}{}_{net,out}$ & $\eta_{\uppercase\expandafter{\romannumeral2},total}=\frac{\dot{W}{}_{net,out}}{\dot{Ex}{}_{fuel}}$\tabularnewline
 \bottomrule
@@
 \label{equation:3}
-x=h-h_{0}-T_{0}\left(s-s_{0}\right)
+ex=h-h_{0}-T_{0}\left(s-s_{0}\right)
 \end{equation}
@@
 \begin{equation}
-\dot{X}=\dot{m}x=\dot{m}\left[h-h_{0}-T_{0}\left(s-s_{0}\right)\right]{}
+\dot{Ex}=\dot{m}x=\dot{m}\left[h-h_{0}-T_{0}\left(s-s_{0}\right)\right]{}
 \end{equation}
@@
 \begin{equation}
-x_{fuel}=LHV\left(1.0064+0.1519\frac{H}{C}+0.0616\frac{O}{C}+0.0429\frac{N}{C}\right)
+ex_{fuel}=LHV\left(1.0064+0.1519\frac{H}{C}+0.0616\frac{O}{C}+0.0429\frac{N}{C}\right)
 \end{equation}
-Where LHV refer to lower heating value of fuel, C, H, O, N refer to mass fractions of carbon, hydrogen, oxygen, nitrogen by element analysis.
+Where LHV refer to lower heating value of fuel, C, H, O, N refer to mass fraction of carbon, hydrogen, oxygen, nitrogen by element analysis.
 More details of power plant equipments' exergy  efficiency calculation can be found in Ref.~\cite{G2016Exergy}
@@
 In order to clearly analyze the effect of system optimization, this paper divides the double-reheat USC system into four main subsystems and a sum of all other equipments, valves and pips named "other".
-The four main subsystems are : boiler with out APH, turbines, air preheat subsystem and regenerative subsystem.
+The four main subsystems are: boiler with out APH, turbines, air preheat subsystem and regenerative subsystem.
 The equations mentioned above can also be used into exergy analysis of these four main subsystems.
@@
 Under design condition, the novel system brings an improvement of net generating power by 11.02 MW, and reduces SCE consumption by 5.5\,g/kWh.
-The power generation efficiency reaches 48.73\%, 1.04\% higher then that of reference system.
+The power generation efficiency reaches 48.73\%, and 1.04\% higher then that of reference system.
 Meanwhile, the exergy efficiency of novel system is 1.01\% higher, showing good exergy-saving effect.
@@
 The item "other" of novel system is higher then reference system, showing that the uncalculated components of systems have a increment of exergy destruction rate.
-Among the uncalculated components, the pips' amount increasing and work fluid mixing with parameters not match are the mainly reason why that part has a increment in exergy destruction rate.
+Among the uncalculated components, the pips' amount increasing and  parameters unmatched work fluid mixing are the main reason why that part has a increment in exergy destruction rate.
 
@@
 %本文是针对空预系统和回热系统的联合优化改造，所以本文将新系统和参考系统中的差变化，系统中设备的效率和用损变化进行了分析。
-To conduct in-depth analysis of both systems, research of the mainly optimized subsystems, air preheat subsystem and regenerative subsystem was conducted.
+To get in-depth analysis of both systems, research of the mainly optimized subsystems: air preheat subsystem and regenerative subsystem was conducted.
 Table~\ref{table:extraction_compare} gives the variation of mass flow rate of extractions.
@@
 
-%插入对QT图的解释和分析
 Air is heated by the EAPHs and AOCs in novel system from 23$^\circ$C to 363.33$^\circ$C. 
@@
 The red triangle and red hollow triangle instead for steam average temperature of EAPH and AOC. 
-In order to simplify the diagram, using saturate temperature of steam instead of EAPH's average temperature and using mean value of inlet and outlet temperature as AOC's average temperature.
+In order to simplify the diagram, using saturate temperature of steam instead of EAPH's average temperature and using mean temperature of inlet and outlet as AOC's average temperature.
 The figure indicates that  temperature difference of EAPHs is lower than that of APH, which makes exergy efficiency's improvement.
-The AOCs' temperature difference is high, but heat exchange is relatively small and so does the exergy destruction. 
+The AOCs' temperature difference is high, but heat exchange is relatively small, so does the exergy destruction. 
 So the air preheat subsystem  of novel system has a smaller exergy destruction rate and improvement on exergy efficiency.
@@
 According with Fig.~\ref{fig:APH_temper_compare}, the heat transfer temperature difference of EAPH8 is 26.95 $^\circ$C,and it has a larger heat exchanging quantity, both of which cause higher exergy destruction and exergy efficiency.
-It also indicates that, although the AOCs have large heat transfer temperature difference, their exergy efficiencies are still high and low exergy destruction rate.
+It also indicates that, although the AOCs have large heat transfer temperature difference, their exergy efficiencies are still high and  exergy destruction rates are low.
 
-Combing Fig.~\ref{fig:APH_temper_compare}  .~\ref{fig:novel_APH_exergy},the reason why the novel system's air preheat subsystem have a higher exergy efficiency and lower exergy destruction rate can be drawn，that the novel system's air preheat subsystem has a lower heat transfer temperature difference and reasonable extractions' superheat degree using.
+Combing Fig.~\ref{fig:APH_temper_compare}  and Fig.~\ref{fig:novel_APH_exergy}, the reason why the novel system's air preheat subsystem have a higher exergy efficiency and lower exergy destruction rate can be drawn that the novel system's air preheat subsystem has a lower heat transfer temperature difference and reasonable extractions' superheat degree using.
 
@@
 \end{figure}
-%插入对于回热系统的分析
-% 新系统总体用损失有所降低，内部损失分配发生了较大变化，deh损失由---到---，加热器由---到---。对于加热器和deh，由图（加入）于换热器其效率不变，但进入加热器工质减少导致损失减少。减少的水由lpe加热，lpe换热由图所示，效率较高，设计合理
-% The total exergy loss of the LPEs is 10.73MW, and the overall exergy efficiency is 91.62%, much higher than that of air preheater.
-As shown in Fig.6, the temperature difference of the LPEs is between 23 $^	rc$C to 42 $^	rc$C, less than that of the original air preheater.
-The LPE1 and LPE4 have the greatest exergy loss of all the LPEs, which mainly results from their great heat transfer rate.
-Besides the exergetic performance of the LPEs keeps falling along the flow direction of flue gas.
-This is because the higher temperature of the cold stream, the greater exergy efficiency, for the temperature difference changes little in heat transfer process.
-% The layout of the optimization system also changes the exergetic performance of regenerative heaters, shown in Fig.7.
-The total exergy loss of regenerative heaters is 11.60 MW, which is greatly reduced compared with that of the base model.
-On the one hand, owing to the heat injected by flue gas, less extracted steam is needed for the HRH2, HRH4, LRH6, and LRH8 which are paralleled with LPEs, which causes less exergy loss of corresponding regenerative heater.
-On the other hand, the LPEs heat condensate and feedwater to higher temperature level than the regenerative heaters, leading to less heat transfer rate of HRH1, HRH3, DEA and LRH7, which will also reduce the exergy loss.
-%There are three factors causing the improvement in exergetic performance.
-Firstly, for HRH1, HRH3, DEA and LRH7, due to higher temperature level of the water from LPE, the exergy of the inlet feedwater e_(c,i) increases, leading to the efficiency improvement.
-Secondly, the installation of AOCs causes the reduction of the superheat degree of the extracted steam entering the HRH3 and DEA, and reduce its exergy, namely e_(h,i).
-At last, compared the original regenerative heaters, an extral part of drainage from corresponding air preheater of optimization system is used to heat the feedwater.
-Compared with the extracted steam, the drainage from air preheaters has lower exergy, which reduce the irreversible loss to some extent.
 
-The regenerative subsystem of novel system uses LEPS paralleled connected with EAPH to absorb economizer outlet flu heat, and eliminates the AOCs originally used to heat feedwater.
-LPE inlet water are heated to the outlet temperature of corresponding outlet temperature of regenerative heater to mix up.
-With the extractions' parameters keeping still, the average heat transfer temperature difference of regenerative heaters change little.
+The regenerative subsystem of novel system uses LEPS paralleled connected with EAPH to absorb economizer outlet flue heat, and eliminates the AOCs originally used to heat feedwater.
+LPE inlet water are heated to the outlet temperature of corresponding RH outlet temperature of to mix up.
+With the extractions' parameters keeping still, the average heat transfer temperature difference of RHs change little.
 So their exergy efficiency keeps the same with reference system.
@@
 Fig.~\ref{fig:regenerative_subsys_compare} shows the regenerative subsystem's exergy destruction rate distribution comparison between the two systems.
-It can be found that the novel system' exergy destruction rate has a decrease and great changes have taken place in the destruction's distribution.
-In consequence of the follow diverting effects of LEPs, the exergy destruction rate of regenerative reheaters and DEA changes from 20.16 MW to 11.303 MW.
+It can be found that the novel system's exergy destruction rate has a decrease and great changes have taken place in the destruction's distribution.
+In consequence of the flow diverting effects of LEPs, the exergy destruction rate of regenerative reheaters and DEA changes from 20.16 MW to 11.303 MW.
 The LEPs exergy destruction rate reach to 10.25 MW, and Fig.~\ref{fig:LPE_exergy_LMDT} shows the LEPs' exergy efficiency and heat transfer LMTD.
@@
 \end{figure}
-  exergy destruction ratio (y$_{D}$) is used to measure the exergy destruction of 1\,MW power generation of unit by a subsystem, and its calculate formula is as follow:
+  exergy destruction ratio ($y_{D}$) is used to measure the exergy destruction of 1\,MW power generation of unit by a subsystem, and its calculate formula is as follow:
 \begin{equation}
@@
 A large exergy destruction ratio value indicates that the subsystem has more significant energy-saving effects and contributes more to the exergy-saving effect of the entire system.
-Fig.~\ref{fig:partload_subsys_exergyrate} shows the  exergy destruction ratio difference ($y_{D,refere}-y_{D,novel}$) between reference system and novel system.
+Fig.~\ref{fig:partload_subsys_exergyrate} shows the  exergy destruction ratio difference ($y_{D,reference}-y_{D,novel}$) between reference system and novel system.
 It indicates that the contribution of energy-saving effect decrease as follows: the boiler, air preheat subsystem, regenerative subsystem and steam turbine.
@@
 \includegraphics[width=0.6\textwidth]{fig/partload_subsys_exergyrate.png}
-\caption{!!!!Exergy destruction rate difference of subsystems in off-design conditions!!!!} 
+\caption{Exergy destruction rate difference of subsystems in off-design conditions} 
 \label{fig:partload_subsys_exergyrate}
@@
 %文章干了什么
-\textcolor{red}{This study presents an optimization design of cascaded utilization of energy for a 1000 MW double reheat ultra-supercritical unit.}
-Thermodynamic analysis is conducted to reveal the comprehensive effects of the optimization measures. 
-The optimization system is found to be effective in overcoming the imperfections, and may provide an effective method for the optimization of a double reheat system in USC unit.
+A novel system for a 1000\,MW double reheat ultra-supercritical unit is proposed which use turbine extractions to preheat air and low pressure economizers to replace air preheater originally installed in vertical shaft.
+Thermodynamic analysis is conducted to reveal the energy-saving effects and thermal performance changes of key components. 
+The novel system is found to be effective in overcoming the imperfections, and may provide an effective method for the optimization of  double reheat USC unit.
 The following conclusions are drawn from this study: 
  \begin{enumerate}[(1)]
-\item The thermodynamic analysis indicates that the cascaded utilization system decreases the temperature difference of in air heating and flue gas cooling process which achieves the cascaded utilization of energy, and the superheat degree of the 3rd and 5th is reduced greatly.
-Besides, more exhaust heat of the flue gas is recovered since the LPE cools the flue gas to lower temperature. 
-\item The layout in the cascaded utilization system changes the mass flow rates of extractions, which causes increment of output power of the generator and increment of the cold source loss.
-\item The optimization system improves the temperature of secondary air, which improves the fire condition in the combustion chamber.
- The temperature of secondary air under full load in the optimization model is 365 $^	rc$C, which is 34 $^	rc$C higher than the design value.
-\item For the first extraction, throttling loss is not existed while the feedwater of boiler improves little.  
-\item The optimization system theoretically brings remarkable energy saving effects.
-The simulation results show that the optimization system can reduce the SCE consumption by 5.6 g/kWh under full load, and can even bring a reduction of 2.9 g/kWh under 50\% THA load .
+ \item The novel system can improve power generation efficiency to 48.73\%, which is 1.04 percent higher then the reference system under design condition.And the exergy efficiency of novel system is 47.52\%, which is 1.01 percentage higher then the reference system.
+ \item The thermodynamic analysis indicates that the novel system decreases the temperature difference of air/flue-gas heat transfer process which achieves the cascaded utilization of energy, and the superheat degree of the 3rd and 5th is reduced greatly.
+\item The novel system changes the mass flow rates distribution of extractions, which causes increment of output power of the generator by 12.09 MW 
+\item The novel system improves the temperature of secondary air, which improves the fire condition in the combustion chamber.
+ The temperature of secondary air of reference system under full load is 365$^\circ$C, which is 34$^\circ$C higher than the reference system.
+\item The novel system theoretically brings remarkable energy saving effects even under off-design conditions.
+The simulation results show that the optimization system can reduce the SCE consumption by 5.49 g/kWh under design condition, and can even bring a reduction of 2.9 g/kWh under 50\% THA load.
 \end{enumerate}
-
+\section*{Acknowledgments}
+This study is supported by National Basic Research Program of China (Grant No. 2015CB251504).
 \section*{References}
@@
 
-\nomenclature[M]{$\dot{I}$}{Exergy destruction rate (MW)}%
-\nomenclature[S]{$in$}{inlet}%
-\nomenclature[S]{$out$}{outlet}%
+\nomenclature[M]{$\dot{I}$}{exergy destruction rate (MW)}%
+\nomenclature[M]{$\dot{Ex}$}{exergy rate (MW)}%
+\nomenclature[M]{$\dot{W}$}{work rate or power done by the system (MW)}%
+\nomenclature[M]{$\eta_{\uppercase\expandafter{\romannumeral2}}$}{exergy efficiency}%y D
+\nomenclature[M]{$y_{D}$}{exergy destruction ratio (MW/MW)}
+
+\nomenclature[M]{$ex$}{specific exergy (MJ/kg)}%
+
+\nomenclature[M]{$h$}{specific enthalpy (MJ/kg)}%
+\nomenclature[M]{$s$}{specific entropy (MJ/kg\,K)}%
+\nomenclature[M]{$T$}{temperature (K)}%
+\nomenclature[M]{$\dot{m}$}{mass flow rate (kg/s)}%
+
+\nomenclature[S]{$in$}{inlet component or system}%
+\nomenclature[S]{$out$}{outlet component or system}%
+
+\nomenclature{THA}{turbine heat acceptance}
+
 \nomenclature{AOC}{additional outer steam cooler}
+\nomenclature{SCE}{standard coal equivalent}
+\nomenclature{USC}{ultra-supercritical}
+\nomenclature{LPE}{low pressure economizer}
+\nomenclature{EAPH}{turbine-extraction-heated air preheater}
+\nomenclature{APH}{air preheater}
+
+\nomenclature{VHP}{super high pressure cylinder}
+\nomenclature{HP}{high pressure cylinder}
+\nomenclature{IP}{intermediate pressure cylinder}
+\nomenclature{LP}{low pressure cylinder}
+\nomenclature{ECO}{ economizer}
+
+\nomenclature{RH}{regenerative heater}
+\nomenclature{HRH}{high pressure regenerative heater}
+\nomenclature{LRH}{low pressure regenerative heater}
+\nomenclature{DEA}{deaerator}
+
+\nomenclature{LMTD}{logarithm mean temperature difference} 
+\nomenclature{LHV}{lower heating value of fuel}
+
+\nomenclature{C, H, O, N}{mass fraction of carbon, hydrogen, oxygen, nitrogen of coal}
 

### 2018-02-08 article.tex
修改了表中的一些数据错误 添加了作者和参考文献

@@
 
-\journal{Energy Conversion and Management}
+\journal{Applied Energy}
 
@@
 \ead{zhanglei@ncst.edu.cn}	
+\author[hust]{Jiayi Zhao}
 \author[hust]{Tao Yang\corref{cor1}}
 \ead{hust\_yt@hust.edu.cn}	
+\author[hust]{Yanping Zhang}
+\author[hust]{Wei Gao}
 
@@
 \address[ncst]{College of Metallurgy and Energy, NorthChina University of Science and and Technology, Tangshan 063009,China}
-\cortext[cor1]{Corresponding authors}
+\cortext[cor1]{Corresponding author}
 
@@
 
+The installation of LPE have some other benefit such as improve The electrostatic precipitator collection efficiency~\cite{Li2016Low}.
+
 Due to  boiler design and thermal system design belong to deferent research area, boiler has been studied as a whole and ignored the joint optimization of boiler heat transfer process and regenerative process.
@@
 The exhaust steam pressure of the steam turbine is set 4.5\,kPa.
-The simplified schematic of it is presented in Fig~\ref{fig:reference_system}.
+The simplified schematic of it is presented in Fig.~\ref{fig:reference_system}.
 
@@
 %从参考系统的锅炉虽然仍然采用Π型布置，但其内部受热面和传统一次再热锅炉有较大区别。
-The system's boiler heat transfer surfaces arrangement is shown in Fig~\ref{fig:boiler_surface}. 
+The system's boiler heat transfer surfaces arrangement is shown in Fig.~\ref{fig:boiler_surface}. 
 The boiler furnace is composited by the membrane wall, along flue gas flow direction lays low-temperature superheater (Lts) screen tube, cold segment of high-temperature first reheater (Csf), cold segment of high-temperature second reheater (Css), High temperature super-heater (Hts), hot segment of high-temperature first reheater (Hsf), hot segment of high-temperature second reheater (Hss).
@@
 Cause removing of the APH originally installed in the vertical shaft, the flue gas's heat needs to be absorbed by other means.
-As shown in Fig~\ref{fig:novel_system}, the flue gas at the outlet of economizer is utilized to heat the condensate and feed water by four LPEs, which are paralleled to HRH2, HRH4, LRH6, and LRH8 respectively.
+As shown in Fig.~\ref{fig:novel_system}, the flue gas at the outlet of economizer is utilized to heat the condensate and feed water by four LPEs, which are paralleled to HRH2, HRH4, LRH6, and LRH8 respectively.
 Part of the condensate and feed water at the inlet of regenerative heater are sent to the LPE, then the heated water join with corresponding regenerative heater's outlet water. 
@@
 %为了能够对优化系统与参考系统进行评估，揭示系统优化的内在机理，本文引入热力学第二定律的分析方法即用分析方法。
+Based on the second law of thermodynamics, exergy analysis method is widely used in power plant thermal system analysis and optimization~\cite{Si2017Exergy,Yang2013Comprehensive,Ahmadi2016Energy}
 Exergy analysis, is adopted to reveal the location, the magnitude and the sources of thermodynamic inefficiencies of the unit.
@@
 In order to clearly analyze the effect of system optimization, this paper divides the double-reheat USC system into four main subsystems and a sum of all other equipments, valves and pips named "other".
-The four main subsystems are: boiler with out APH, turbines, air preheat subsystem and regenerative subsystem.
+The four main subsystems are: boiler with out APH, turbine, air preheat subsystem and regenerative subsystem.
 The equations mentioned above can also be used into exergy analysis of these four main subsystems.
@@
 Air preheat subsystem's exergy destruction rate changes from 27.39\,MW to 16.55\,MW, having a 10.84\,MW decrement, having the largest Optimization ratio.
-In the mean time, turbines and regenerative subsystem have a relatively small change at about 1\,MW.
+In the mean time, turbine and regenerative subsystem have a relatively small change at about 1\,MW.
 
@@
 Other & 131.03 & 142.42 \tabularnewline
-Total & 1116.72 & 1127.54\tabularnewline
+Total & 1127.54 & 1116.72\tabularnewline
 \bottomrule

### 2018-02-22 article.tex
按照杨老师的要求进行了细微的调整，包括表格的错误

@@
 
-To reduce the superheat degree of the extractions, Xu et al.~\cite{Xu2015Optimum} investigated the thermal performance of the steam and water cycle with single reheat after the installation of an additional outer steam cooler (AOC).
+To reduce the superheat degree of the extractions, Xu et al.~\cite{Xu2015Optimum,Zhou2014A} investigated the thermal performance of the steam and water cycle with single reheat after the installation of an additional outer steam cooler (AOC).
 Results show that the AOC is an effective method to reduce the superheat degree and improve the efficiency of the unit.

### 2018-02-22 article.tex
润色后的文献第一稿

--- 2018-02-04 article.tex
@@
 
-\title{A novel 1000\,MW double-reheat ultra supercritical system with turbine-extraction-heated air preheaters and low temperature economizers}
+\title{A novel 1000\,MW double-reheat ultra supercritical system with turbine-extraction-heated air preheaters and low-temperature economizers}
 
@@
 \ead{zhanglei@ncst.edu.cn}	
-\author[hust]{Tao Yang\corref{cor1}}
+\author[hust]{Jiayi Zhao}
+\author[hust]{Tao Yang\corref{cor1}} %I am not sure how to delete the extra comma after Yang's name--there is a comma after the "a" superscript that needs to be removed.
 \ead{hust\_yt@hust.edu.cn}	
+\author[hust]{Yanping Zhang}
+\author[hust]{Wei Gao}
 
-\address[hust]{School of Energy and Power Engineering, Huazhong University of Science and Technology, Wuhan 430074,China}
-\address[ncst]{College of Metallurgy and Energy, NorthChina University of Science and and Technology, Tangshan 063009,China}
-\cortext[cor1]{Corresponding authors}
+\address[hust]{School of Energy and Power Engineering, Huazhong University of Science and Technology, Wuhan 430074, China}
+\address[ncst]{College of Metallurgy and Energy, North China University of Science and Technology, Tangshan 063009, China}
+\cortext[cor1]{Corresponding author}
 
 \begin{abstract}%修改到300字以内
-Double-reheat ultra-supercritical (USC) unit has received extensive attention for its high efficiency and energy-saving effect.
-The optimal design of its thermal system is still under study.
-Herein, an optimized system for reasonable fluid heat transfer temperature matching and higher efficiency was proposed.
-The novel system used turbine extractions as heat sources of air preheaters and low-pressure economizers to absorb economizer outlet flue gas’ heat, which realized the join optimization of air preheat process and regenerative system.
-Models were built to compare energetic performance of the novel system and reference system.
-In addition, thermodynamic analyses under partial load operation conditions was conducted. 
-Exergy analysis method was used to identify exergy destruction changes of transformed parts and analyze the cause of the change.
-Result shows the novel system can largely decrease exergy destruction rate of air preheat process and improve the system's thermal performance.
-Furthermore, the novel system increases the temperature of secondary air and reduces the overall superheat degree of several extractions.
-Theoretically, the novel system with a overall exergy efficiency of 48.73\%  and reduces the SCE consumption by nearly 5.5\,g/kWh under THA load when the temperature of the flue gas entering the electrostatic precipitator is set to 95$^\circ$C.
-Moreover, the novel system can still has advantages in coal saving under partial load condition.
-Results indicate that the novel system could improves the performance of double-reheat USC unit and may provide a theoretical basis for its optimization.
+The double-reheat ultra-supercritical (USC) unit has received significant attention because of its high efficiency and energy-saving effects.
+The optimal design of the unit's thermal system is still under consideration, however.
+In this paper, an optimized system for reasonable fluid heat transfer temperature-matching and higher efficiency is proposed.
+This novel system uses turbine extractions as heat sources for air preheaters and low-pressure economizers to absorb economizer outlet flue gas heat, thereby realizing the joint optimization of the air preheat process and the regenerative system.
+Models were built to compare the energetic performance of the novel system and that of the reference system.
+In addition, thermodynamic analyses under partial load operation conditions were conducted. 
+Exergy analysis was used to identify the exergy destruction changes of the transformed parts and to analyze the cause of the changes.
+The results show that the novel system largely decreased the exergy destruction rate of the air preheat process and improved the system's thermal performance.
+Furthermore, the novel system increased the temperature of secondary air and reduced the overall superheat degree of several extractions.
+Theoretically, with an overall exergy efficiency of 48.73\%, the novel system can reduce SCE
+%I don't think the "SCE" acronym has been introduced yet. Write it out in full here? 
+consumption by nearly 5.5\,g/kWh under the THA load
+%Same for THA---write out in full?
+if the temperature of the flue gas entering the electrostatic precipitator is set to 95$^\circ$C.
+Moreover, the novel system has advantages for coal-saving under the partial load condition.
+Ultimately, the results indicate that the novel system can improve the performance of the double-reheat USC unit and may provide a theoretical basis for its optimization.
 
@@
 \begin{keyword}
-Double reheat \sep Ultra-supercritical power plant \sep Exergy analysis \sep air preheat process \sep Thermodynamic analyses
+Double-reheat \sep ultra-supercritical power plant \sep exergy analysis \sep air preheat process \sep thermodynamic analysis
 \end{keyword}
@@
 \label{sec1:intro}
-Coal is still the main fossil fuel resources for electricity production in the world according to~\cite{Ouedraogo2013Energy}. 
-In China, coal–fired power generation accounts for more than 70\% of the total electricity generation and subsequently contribute almost 50\%, 37\%, 33\% and 55\% to the SO$_X$, NO$_X$, dust and CO$_X$ emission volumes respectively~\cite{Zhang2010Analysis}.
-Statics show that China has been the largest producer and consumer of energy all over the world since 2013~\cite{Petroleum2014BP}. 
-For 2016 as a whole, Chinese coal production fell by 7.9\% and the price of steam coal increased by over 60\%~\cite{Petroleum2017BP}. 
-Improve system efficiency and reducing coal consumption is still the main task of power plant design.
-Nowadays, ultra-supercritical (USC) power plants with large capacity and high parameter are considered to be feasible means to save energy and have rapidly developed word-wide.
-The double reheat USC unit is a new generation of USC unit which can improve the thermal performance compared with single reheat units~\cite{Zhao2017Exergy}. 
-According to Ref.~\cite{Zhao2017Exergy}, a double reheat unit with the inlet parameter 30.0\,MPa/600/620/620$^\circ$C improves the heat efficiency by 2.4\%-2.6\%, compared with a common used USC unit with the inlet parameter 25.0\,MPa/600/600$^\circ$C.
- The U.S. built the first double reheat unit with main parameter 34.4 MPa/649/566/566$^\circ$C in 1960s.
- Two 700 MW double reheat USC units in Japan were put into operation in 1990. 
- Since 2012, five  double reheat USC units  began to build in China, and three of them put it into operation in 2015.
- Over the past few decades, the double reheat USC units have received more and more attention for its rapid development all over the world.
+Coal is still the main fossil fuel resource for the production of electricity globally, according to~\cite{Ouedraogo2013Energy}. 
+In China, coal–fired power generation accounts for more than 70\% of the total electricity generation and subsequently contributes almost 50\%, 37\%, 33\%, and 55\% to the SO$_X$, NO$_X$, dust, and CO$_X$ emission volumes, respectively~\cite{Zhang2010Analysis}.
+Statistics show that China has been the largest producer and consumer of energy worldwide since 2013~\cite{Petroleum2014BP}. 
+In 2016, Chinese coal production fell by 7.9\% and the price of steam coal increased by over 60\%~\cite{Petroleum2017BP}. 
+Improving system efficiency and reducing coal consumption remain the primary tasks to be considered in power plant design.
+Nowadays ultra-supercritical (USC) power plants with large capacities and high parameters are considered to be feasible ways to save energy; as such, their usage has spread rapidly worldwide.
+The double-reheat USC unit is a new generation of USC unit that can improve thermal performance when compared with a single reheat unit~\cite{Zhao2017Exergy}. 
+According to~\cite{Zhao2017Exergy}, a double reheat unit with the inlet parameter 30.0\,MPa/600/620/620$^\circ$C improves the heat efficiency by 2.4\%-2.6\% when compared with a commonly used USC unit with the inlet parameter 25.0\,MPa/600/600$^\circ$C.
+ The United States built the first double-reheat unit with the main parameter 34.4 MPa/649/566/566$^\circ$C in the 1960s.
+ Two 700 MW double-reheat USC units were put into operation in Japan in 1990. 
+ The process of building five double-reheat USC units began in China in 2012, and three of these units were put into operation in 2015.
+ Over the past few decades, double-reheat USC units have received increasing attention due to their rapid development worldwide.
 
-Though the high live steam pressure and temperature of USC unit improves its efficiency, there are still some imperfections which limit the improvement of its performance . 
-In order to make an in-depth analysis of the system, Zhao Z et al.~\cite{Zhao2017Exergy} studied the exergy distribution system for a 1000\,MW double reheat USC power plant and provided the main reasons that led to exergy destruction on the steam turbine.
-Rashidi et al.~\cite{Rashidi2014Thermodynamic} investigated the thermodynamic analysis of a double reheat steam power plant.
-According to Ref.~\cite{Wu2014Component}, component and process based exergy evaluation was performed on a coal-fired power plant in China, which provides guidance for energy-saving strategies.
-It pointed out that the exergy destruction in the heat transfer process accounts for the largest proportion.
+Though the high live steam pressure and temperature of the USC unit improve its efficiency, there are still some imperfections that limit the improvement of the unit's performance. 
+In order to perform an in-depth analysis of the system, Zhao Z et al.~\cite{Zhao2017Exergy} studied the exergy distribution system for a 1000\,MW double-reheat USC power plant and determined the main causes of exergy destruction on the steam turbine.
+Rashidi et al.~\cite{Rashidi2014Thermodynamic} performed a thermodynamic analysis of a double-reheat steam power plant.
+According to Ref.~\cite{Wu2014Component}, component- and process-based exergy evaluations were performed on a coal-fired power plant in China, thereby helping researchers to identify energy-saving strategies.
+It was pointed out that the exergy destruction in the heat transfer process accounts for the largest proportion.
+%largest proportion of what? Of exergy destruction overall?
 
-Compared with common USC system, double-reheat system has some characteristic problems, such as double reheat ratio chose and great superheat degree of the first several extractions.
-And some common problems, such as the high boiler exhaust temperature, which leads to unreasonable energy-level matching and great exergy destruction.
+Compared with the common USC system, the double-reheat system has some typical problems, such as the double-reheat ratio that is chosen and the high superheat degree of the first several extractions.
+Other common problems include the high boiler exhaust temperature, which leads to unreasonable energy-level matching and significant exergy destruction.
 
-To chose a reasonable reheat parameters, Zhou et al.~\cite{Zhou2016Parametric} carried out parametric analysis and system optimization in double reheat ultra-supercritical power plants based on exergy analysis and economic analysis.
-The result shows reasonable reheat parameters and reheat stage number can improve  double reheat system's performance.
+To identify reasonable reheat parameters, Zhou et al.~\cite{Zhou2016Parametric} carried out a parametric analysis and system optimization of double-reheat ultra-supercritical power plants based on exergy analysis and economic analysis.
+The results showed that reasonable reheat parameters and reheat stage numbers can improve the double-reheat system's performance.
 
-To reduce the superheat degree of the extractions, Xu et al.~\cite{Xu2015Optimum} investigated the thermal performance of the steam and water cycle with single reheat after the installation of an additional outer steam cooler (AOC).
-Results show that the AOC is an effective method to reduce the superheat degree and improve the efficiency of the unit.
-Li et al.~\cite{Li2014Thermodynamic} proposed a system adopting 10-stage extractions and two outer steam coolers. 
-The result of thermodynamic and techno-economic analyses shows this system can reduce cost of electricity to 55.89 USD/MWh.
-Besides, Kjaer~\cite{Kjaer2010A} proposed a regenerative steam turbine to utilize the superheat degree of the extractions.
-In this design, part of the extraction from the high pressure turbine enters the additional regenerative steam turbine not the regenerative heater.
+To reduce the superheat degree of the extractions, Xu et al.~\cite{Xu2015Optimum} investigated the thermal performance of the steam and water cycle with a single reheat after the installation of an additional outer steam cooler (AOC).
+The results showed that the AOC is an effective method of reducing the superheat degree and improving the efficiency of the unit.
+Li et al.~\cite{Li2014Thermodynamic} proposed a system that uses ten-stage extractions and two outer steam coolers. 
+The results of the thermodynamic and techno-economic analyses showed that this system can lower the cost of electricity to 55.89 USD/MWh.
+In addition, Kjaer~\cite{Kjaer2010A} proposed a regenerative steam turbine for utilizing the superheat degree of the extractions.
+In this design, part of the extraction from the high pressure turbine enters the additional regenerative steam turbine rather than the regenerative heater.
 Extractions from the intermediate pressure turbine are replaced by those from the regenerative steam turbine.
-The superheat degree of the extraction is significantly reduced in this design, and the exergy destruction of regenerative heaters is reduced, which results in an overall improvement in efficiency.
+The superheat degree of the extraction is significantly reduced in this design and the exergy destruction of regenerative heaters is likewise reduced, thereby resulting in an overall improvement in efficiency.
 
-To reuse the energy of the exhaust flue gas, Xu et al.~\cite{Xu2013Techno} proposed a low pressure economizer (LPE) based on the data of some 1000\,MW typical power generation units in China and four possible arrangements of the LPE installation were proposed to compare its energy-saving effects.
-Results indicated that LPE connected with higher temperature section of the condensate line brings more reduction of standard coal equivalent (SCE).
-Wang et al.~\cite{Wang2012Application} investigated the energy and water saving and the reduction of CO$_2$ after the installation of LPE.
-Results show that the optimized measures can bring a reduction of SCE by 2-4\,g/kWh.
-Stevanovic et al.~\cite{Stevanovic2014Efficiency} proposed an additional high pressure economizer installed at a long term running lignite-fired power plant.
-Results show that more than 30\,MW of the flue gas waste heat is recovered, which brings an improvement in gross efficiency by 0.53\% and 9.4\,MW extra output power.
-Xu et al~\cite{Xu2013A} made the air preheater divided into two stages to reduce the temperature difference in heat transfer process.
-Besides, a LPE is installed between the two air preheaters to obtain an appropriate flue gas temperature range.
-Thermodynamic and Technic-economic analysis are conducted to reveal the performance improvement.
-It was found that the SCE consumption can be reduced by 6.7\,g/kWh.
+To reuse the energy of the exhaust flue gas, Xu et al.~\cite{Xu2013Techno} proposed a low-pressure economizer (LPE) based on data compiled from some typical 1000\,MW power generation units in China.
+Four possible arrangements for LPE installation were proposed and their energy-saving effects were compared.
+The results indicated that the LPE connected with the higher-temperature section of the condensate line created a greater reduction in the standard coal equivalent (SCE). %"greatest"? 
+Wang et al.~\cite{Wang2012Application} investigated energy- and water-saving measures and the reduction of CO$_2$ after the installation of an LPE.
+The results showed that the optimized measures can reduce SCE by 2-4\,g/kWh.
+Stevanovic et al.~\cite{Stevanovic2014Efficiency} proposed an additional high-pressure economizer installed at a long-term running lignite-fired power plant.
+The results showed that more than 30\,MW of the flue gas waste heat was recovered, creating an improvement in gross efficiency of 0.53\% and 9.4\,MW extra output power.
+Xu et al.~\cite{Xu2013A} divided the air preheater into two stages to reduce the temperature difference in the heat transfer process.
+%"divided the air preheater process"? Or was the preheater itself actually divided?
+A LPE was also installed between the two air preheaters to obtain an appropriate flue gas temperature range.
+Thermodynamic and technic-economic analyses were conducted to reveal the performance improvement.
+It was found that the SCE consumption was reduced by 6.7\,g/kWh. %"techno-economic" is used earlier in the paper. Which expression is correct?
 
-Due to  boiler design and thermal system design belong to deferent research area, boiler has been studied as a whole and ignored the joint optimization of boiler heat transfer process and regenerative process.
+The installation of an LPE has some other benefits, such as improvements in electrostatic precipitator collection efficiency~\cite{Li2016Low}.
 
-In this paper, a novel system based on a 1000\,MW double reheat USC reference system  is proposed to realize boiler and regenerative system energy cascade utilization. 
-The novel system realized reasonable temperature matching of flue gas, air, extraction steam and condensate water by using turbine-extraction-heating air preheaters (EAPHs) and LPEs.
-Specifically, the main works of this study include: (1)Modeling the novel system and reference system with EBSILON® Professional; (2) Using exergy analysis to compare both systems' exergy efficiency , exergy destruction distribution and subsystems performance change;(3) Analyzing both systems' thermal performance under off-design conditions.
+Given that boiler design and thermal system design belong to different research areas, boiler design is studied as a whole apart from the joint optimization of the boiler heat transfer process and regenerative process.
 
-\section{System optimization of double reheat USC system}
+In this paper, a novel system based on a 1000\,MW double-reheat USC reference system is proposed to realize boiler and regenerative system energy cascade utilization. 
+The novel system realized the reasonable temperature-matching of flue gas, air, extraction steam, and condensate water by using turbine-extraction-heating air preheaters (EAPHs) and LPEs.
+Specifically, this study included the following tasks: (1) modeling the novel system and reference system with EBSILON® Professional; (2) using exergy analysis to compare both systems' exergy efficiency, exergy destruction distribution, and subsystem performance change; and (3) analyzing both systems' thermal performances under off-design conditions.
+
+\section{Optimization of the double-reheat USC system}
 \label{sec2:system intro}
-\subsection{Reference system on operation} % (fold)
+\subsection{Reference system in operation} % (fold)
 \label{sub2:ref intro}
-A typical coal-fired double reheat USC power plant in operation is chosen as the reference unit.
-The parameter settings at maximize continuous power are 310\,bar/600$^\circ$C for the main steam, 610$^\circ$C for the reheat steam pressure, 33.5\% for the proportion of the single reheat steam pressure to the main steam pressure, and 33\% for the proportion of the double reheat steam pressure to the single reheat steam pressure~\cite{Zhao2017Exergy}.
-The output power of the reference system under the design condition is 1000 MW.
-The unit consists of one super high pressure cylinder (VHP), one high pressure cylinder (HP), one intermediate pressure cylinder (IP), and two low pressure cylinders (LPs).
-Regenerative system with four high pressure regenerative heaters (HRHs), five low pressure regenerative heaters (LRHs), and one deaerator (DEA) are adopted.
-Besides, two additional outer steam coolers (AOC1, AOC2) are used to cool two extractions due to its high super-heating degree.
-The exhaust steam pressure of the steam turbine is set 4.5\,kPa.
-The simplified schematic of it is presented in Fig~\ref{fig:reference_system}.
+A typical coal-fired double-reheat USC power plant in operation was chosen as the reference unit.
+The parameter settings at maximum continuous power were 310\,bar/600$^\circ$C for the main steam, 610$^\circ$C for the reheat steam pressure, 33.5\% for the proportion of single-reheat steam pressure to main steam pressure, and 33\% for the proportion of double-reheat steam pressure to single-reheat steam pressure~\cite{Zhao2017Exergy}.
+The output power of the reference system under the design condition was 1000 MW.
+The unit consisted of one super-high pressure cylinder (VHP), one high-pressure cylinder (HP), one intermediate-pressure cylinder (IP), and two low-pressure cylinders (LPs).
+A regenerative system with four high-pressure regenerative heaters (HRHs), five low-pressure regenerative heaters (LRHs), and one deaerator (DEA) was adopted.
+In addition, two additional outer steam coolers (AOC1, AOC2) were used to cool two extractions due to their high super-heat degree.
+The exhaust steam pressure of the steam turbine was set to 4.5\,kPa.
+Its simplified schematic is presented in Fig.~\ref{fig:reference_system}.
 
@@
 %从参考系统的锅炉虽然仍然采用Π型布置，但其内部受热面和传统一次再热锅炉有较大区别。
-The system's boiler heat transfer surfaces arrangement is shown in Fig~\ref{fig:boiler_surface}. 
-The boiler furnace is composited by the membrane wall, along flue gas flow direction lays low-temperature superheater (Lts) screen tube, cold segment of high-temperature first reheater (Csf), cold segment of high-temperature second reheater (Css), High temperature super-heater (Hts), hot segment of high-temperature first reheater (Hsf), hot segment of high-temperature second reheater (Hss).
-After Hsf and Hss the flue gas channel is divided into the front-duct flue and the back-duct flue.
-The front duct arranges low-temperature first reheater (Ltfr) and the front-duct economizer (Feco).
-The back duct arranges low-temperature second reheater (Ltsr) and the back-duct economizer (Beco).
-(air preheater)APH is arranged in vertical shaft.
+The system's boiler heat transfer surface arrangement is shown in Fig.~\ref{fig:boiler_surface}. 
+The boiler furnace is composed of the membrane wall; along the flue gas flow direction lie the low-temperature superheater (Lts) screen tube, the cold segment of the first high-temperature reheater (Csf), the cold segment of the second high-temperature reheater (Css), the high-temperature super-heater (Hts), the hot segment of the first high-temperature reheater (Hsf), and the hot segment of the second high-temperature reheater (Hss).
+After Hsf and Hss, the flue gas channel is divided into the front-duct flue and the back-duct flue.
+The front duct arranges the first low-temperature reheater (Ltfr) and the front-duct economizer (Feco).
+The back duct arranges the second low-temperature reheater (Ltsr) and the back-duct economizer (Beco).
+The air preheater (APH) is arranged in the vertical shaft. %What does "arranges" mean in these sentences?
 
-From the arrangement of heating transfer surfaces, the boiler can be divided into two parts: the part achieving heat absorption of water/steam process in the furnace, and the APH to complete the air preheat process.
-It can be seen that most heating surfaces of boiler is arranged in the furnace, while the horizontal flue and vertical shaft are only equipped with APH.
-So the horizontal flue and vertical shaft have sufficient space to install other equipments.
+From the arrangement of the heating transfer surfaces, the boiler can be divided into two parts: the part performing the heat absorption for the water/steam process in the furnace and the APH that completes the air preheat process.
+It can be seen that most heating surfaces of the boiler are arranged in the furnace, while the horizontal flue and vertical shaft are only equipped with APH.
+This means that the horizontal flue and vertical shaft leave sufficient space for the installation of other equipment.
 
@@
 \includegraphics[width=0.9\textwidth]{fig/boiler_surface.png}
-\caption{Boiler heat transfer surfaces layout} 
+\caption{Boiler heat transfer surface layout} 
 \label{fig:boiler_surface}
@@
 \begin{table}[htbp]
-\caption{The main input parameter of reference system }
+\caption{Main input parameters of the reference system }
 \label{tab:ref input}
@@
 
-Table~\ref{tab:reheater parameter} gives the temperature profiles of regenerative heaters and the air preheater, revealing their energy match level.
-For the APH, the temperature of flue gas at the inlet is 376$^\circ$C under, while the temperature of the air to be heated by the flue is 23$^\circ$C.
-The logarithm mean temperature difference (LMTD) of the APH is calculated to be 72$^\circ$C.
-Compared with the air preheater, the regenerative heaters have much lower LMTD from 6.88$^\circ$C-15.87$^\circ$C.
-According to the second law of thermodynamics, the bigger the temperature difference the greater the irreversible loss.
-So it needs to optimize the air preheat process to reduce energy loss of the system.
-AOC1 and AOC2 face the same problem of high LMTD compared with RHs.
-It's better to find a way to make double reheat USC system's high temperature extractions a reasonable arrangement.
+Table~\ref{tab:reheater parameter} gives the temperature profiles of the regenerative heaters and the air preheater, revealing their energy match level.
+For the APH, the temperature of the flue gas at the inlet is less than 376$^\circ$C,  
+ while the temperature of the air to be heated by the flue is 23$^\circ$C.
+The logarithm mean temperature difference (LMTD) of the APH is calculated as 72$^\circ$C.
+Compared with the air preheater, the regenerative heaters have much lower LMTDs, ranging from 6.88$^\circ$C-15.87$^\circ$C.
+According to the second law of thermodynamics, the greater the temperature difference, the greater the irreversible loss.
+Therefore, the air preheat process needs to be optimized to reduce the energy loss of the system.
+AOC1 and AOC2 have the same problem of high LMTDs compared with RHs.
+It is important to determine how to make the double-reheat USC system's high temperature extractions a reasonable arrangement.
 
 \begin{table}[htbp]
-\caption{Fluid parameters of regenerative heaters and air preheater}
+\caption{Fluid parameters of regenerative heaters and air preheater} %Should "air preheater" be plural here?
 \label{tab:reheater parameter}
@@
 
-\subsection{Proposal of a novel system with EAPHs and LPEs}
+\subsection{Proposal for a novel system with EAPHs and LPEs}
 \label{sub2:prop novel sys}
 
-To reduce the energy loss caused by APH, a novel system is proposed, in which air is not heated by flue gas in the conventional air preheater, but 8 turbine-extraction-heated air preheaters (EAPH1-EAPH8).
+To reduce the energy loss caused by APH, a novel system is proposed in which air is not heated by flue gas in the conventional air preheater.
+Rather, eight turbine-extraction-heated air preheaters (EAPH1-EAPH8) are used.
 The layout of the optimization system is presented in Fig.~\ref{fig:novel_system}.
 
-As shown in Fig.~\ref{fig:extraction_heat_APH}, the extracted steam divides into two parts, one is sent to the regenerative heater to heat the condensate or feedwater and the other one is sent to corresponding EAPH to heat air.
-The drainage from the air preheater joins with that of corresponding regenerative heater after finishing heat transfer .
-Steam distribution ratio is determined according to EAPH upper terminal temperature difference settled in the system.
-It should be mentioned that not all the extractions are available for air heating.
-The last two stage extractions' pressure are much lower than barometric pressure which has a great risk of air leakage into the steam, and APH8 shall be shut down under low load for the same reason.
+As shown in Fig.~\ref{fig:extraction_heat_APH}, the extracted steam is divided in half, with one half sent to the regenerative heater to heat the condensate or feedwater and the other half sent to the corresponding EAPH to heat the air.
+The drainage from the air preheater joins with that of the corresponding regenerative heater after the heat transfer has been completed.
+The steam distribution ratio is determined according to the EAPH upper terminal temperature difference settled in the system.
+It should be noted that not all of the extractions are available for air heating.
+The last two stage extractions' pressure values are much lower than their barometric pressure values, which suggests a great risk of air leakage into the steam.
+APH8 must be shut down under low load for the same reason.
 
 The AOCs in the reference system are designed to heat feedwater.
-Although AOC inlet steam has a great supper heat degree, the small heat exchanged makes feedwater have little temperature rise.
-So the LMTD is very high in AOCs.
+Although AOC inlet steam has a great supper heat degree %superheat?
+, the small amount of heat exchanged makes the feedwater's temperature rise only slightly.
+The LMTD is very high in AOCs.
 
-To reduce rise AOCs' exergy efficiency and the superheat degree of extractions entering the heat exchangers, four additional outer steam coolers (AOC1-AOC4) are installed at the air side outlet of EAPH1.
-Air side outlet of EAPH1 will sent to boiler as secondary air, which has small mass quantity and lower heat capacity compared with feedwater. 
-So the secondary air temperature can make a remarkable rise, and LMTD of AOCs can get down.
-Extractions from the 2nd to the 5th have very high temperature and great superheat degree, they are sent to AOCs in the order of temperature level.
-For example, the 2nd extraction has the highest temperature, and is applied to heat the air in the 1st AOC, and then the cooled steam from AOC1 is sent to HRH2 and air EAPH2 to heat the water and air respectively.
+To reduce rise AOCs' exergy efficiency and the superheat degree of extractions entering the heat exchangers,
+%Here do you mean to "reduce the possibility of an increase in AOCs'..."?
+four additional outer steam coolers (AOC1-AOC4) are installed at the air side outlet of EAPH1.
+The air side outlet of EAPH1 is sent to the boiler as secondary air, which has a smaller mass and lower heat capacity compared with the feedwater. 
+The secondary air temperature thus can increase remarkably, while the LMTD of AOCs can decrease.
+The second through the fifth extractions have very high temperatures and great superheat degrees; they are sent to the AOCs in the order of their temperature levels.
+For example, the second extraction has the highest temperature and is applied to heat the air in the first AOC.
+Then the cooled steam from AOC1 is sent to HRH2 and air EAPH2 to heat the water and air, respectively.
+%Should "air EAPH2" be simply "EAPH2"?
 
@@
 
-Cause removing of the APH originally installed in the vertical shaft, the flue gas's heat needs to be absorbed by other means.
-As shown in Fig~\ref{fig:novel_system}, the flue gas at the outlet of economizer is utilized to heat the condensate and feed water by four LPEs, which are paralleled to HRH2, HRH4, LRH6, and LRH8 respectively.
-Part of the condensate and feed water at the inlet of regenerative heater are sent to the LPE, then the heated water join with corresponding regenerative heater's outlet water. 
-Considering the acid dew point temperature, the flue gas temperature at the outlet of the last LPE can be set 95$^\circ$C.
+Because of the removal of the APH originally installed in the vertical shaft, the flue gas's heat needs to be absorbed by other means.
+As shown in Fig.~\ref{fig:novel_system}, the flue gas at the outlet of the economizer is utilized by four LPEs to heat the condensate and feedwater; these LPEs are parallel to HRH2, HRH4, LRH6, and LRH8, respectively.
+%Rather than "are parallel to," perhaps "correspond with"?
+Part of the condensate and feedwater at the inlet of the regenerative heater is sent to the LPE; then the heated water joins with the corresponding regenerative heater's outlet water. 
+Given the acid dew point temperature, the flue gas temperature at the outlet of the last LPE can be set to 95$^\circ$C.
 
@@
 % \label{sec3:modle est and eval}
-\section{Model description and Thermodynamic metric}
+\section{Model description and thermodynamic metrics}
 \label{ssub:model_establishment_and_system_analysis_method}
 
-\subsection{Model establish method and main assumption}
+\subsection{Model establishment method and main assumptions}
 \label{ssub3:modle description}
@@
 %添加模型中基本部件的特性 添加个表格
-In this paper, the thermodynamic cycle of the thermal system under different loads are simulated with EBSILON® Professional.
-EBSILON is a power plant simulation tool which can calculate thermodynamic quantities and widely used in power plant system model establishment and analysis~\cite{Li2015Integrated,Yao2017Multi}. 
-The simulation model gives the detailed data with high degree of reliability to calculate the thermodynamic state.
-While use this software simulating systems, main equipments work flow parameters and some basic properties need to be settled.
-Cause designed based on the reference system, the novel system's main input parameters(such as live steam parameters, fist/second reheat steam parameters and turbine extractions parameters) keeps the same as it, which can be find in Table~\ref{tab:ref input} and Table~\ref{table:extractions_parameter}.
-Based on the practice, the upper temperature differences of novel systems' LPE, AOC and EAPH are settled to 30$^\circ$C, 20$^\circ$C and 5$^\circ$C. 
-And other main components model details are give in Table~\ref{table:model_details}.
+In this paper, the thermodynamic cycle of the thermal system under different loads is simulated using EBSILON® Professional.
+EBSILON is a power plant simulation tool that can calculate thermodynamic quantities. It is widely used in power plant system model establishment and analysis~\cite{Li2015Integrated,Yao2017Multi}. 
+The simulation model yields detailed data with a high degree of reliability in calculating the thermodynamic state.
+When using this software simulation system, the main equipment's work flow parameters and some basic properties need to be settled.
+Because it is designed based on the reference system, the novel system's main input parameters (such as live steam parameters, first/second reheat steam parameters, and turbine extraction parameters) remain the same as those that are shown in Table~\ref{tab:ref input} and Table~\ref{table:extractions_parameter}.
+Based on the practice,
+%What is "the practice"? 
+the upper temperature differences of the novel system's LPE, AOC and EAPH are settled to 30$^\circ$C, 20$^\circ$C, and 5$^\circ$C. 
+The details of the model's other main components are given in Table~\ref{table:model_details}.
 
 \begin{table}
-\caption{Model details of main components}
+\caption{Details of model's main components}
 \label{table:model_details}
@@
 \midrule
-Boiler         			& Economizer out let flue gas temperature =376\textcelsius ;\tabularnewline
- 						& Slag temperature =850\textcelsius ;\tabularnewline
- 						& Combustion efficiency = 0.99.\tabularnewline
-Turbine 				& Isentropic efficiencies are from 0.83 to 0.93, \tabularnewline
- 						& calculated from thermal equilibrium diagram.\tabularnewline
-Condenser 				& Upper terminal temperature difference = 5\textcelsius .\tabularnewline
-Regenerative reheats 	& Upper terminal temperature differences are from -1.7\textcelsius{}  \tabularnewline
- 						& to 2.2\textcelsius ,calculated from thermal equilibrium diagram.\tabularnewline
+Boiler         			& Economizer outlet flue gas temperature = 376\textcelsius \tabularnewline
+ 						& Slag temperature = 850\textcelsius \tabularnewline
+ 						& Combustion efficiency = 0.99\tabularnewline
+Turbine 				& Isentropic efficiencies range from 0.83 to 0.93, \tabularnewline
+ 						& calculated from the thermal equilibrium diagram\tabularnewline
+Condenser 				& Upper terminal temperature difference = 5\textcelsius \tabularnewline
+Regenerative reheats 	& Upper terminal temperature differences range from -1.7\textcelsius{}  \tabularnewline
+ 						& to 2.2\textcelsius, calculated from the thermal equilibrium diagram.\tabularnewline
 \bottomrule
@@
 
-On the off-design conditions, EBSIOLON's simulation and parameter calculation of the equipment, such as turbine, is based on experimental characteristics of units.
-However, only turbine's off-design characteristic curves can actually be obtained,and boiler's and heat exchangers' data can not be gotten.
-It has to be replaced by built-in data.
-It’s needed to assume that the difference between the built-in data and the actual data to meet the error requirements.
-The following assumptions need to be made in order to be able to simulate correctly.
+Under off-design conditions, EBSILON's simulation and parameter calculations for equipment such as turbines are based on the experimental characteristics of the units.
+However, only the turbine's off-design characteristic curves can actually be obtained, while the data for the boiler and heat exchangers cannot be determined.
+This data thus has to be replaced by built-in data.
+It is necessary to assume the difference between the built-in data and the actual data to meet the error requirements.
+%What assumption is being made about the difference in the line above?
+The following assumptions need to be made in order to be able to correctly perform a simulation.
 \begin{enumerate}[(1)]
-\item Both novel and reference systems are operated in stable condition.
-\item The thermal efficiency of the equipment is calculated from the thermal balance of the input and output parameters of the components, assuming that the calculation error requirement can be met.
-\item According to the heat map, set the upper and lower end difference of the heat exchanger as a fixed value, and do not change during different load conditions' simulation.
-\item Do not take the pips' complexity and equipment’s installation difficulty of the novel system as consideration.
+\item Both the novel and reference systems are operated under stable conditions.
+\item The thermal efficiency of the equipment is calculated from the thermal balance of the input and output parameters of the components, assuming that the calculation error requirement is met.
+\item According to the heat map, the upper and lower end differences of the heat exchanger are set as fixed values and do not change during different load conditions' simulation.
+\item The pips' complexity and the installation difficulty of the novel system's equipment is not taken into consideration.
 \end{enumerate}
-More detail descriptions of the thermaldynamic model of involved components can be found in Ref.~\cite{Yao2017Multi}.
+A more detailed description of the thermaldynamic model of the components can be found in Ref.~\cite{Yao2017Multi}. %Should this be "thermodynamic," rather than "thermaldynamic"?
 
 \begin{table}
-\caption{The turbine extractions parameters on design condition}
+\caption{Turbine extractions' parameters under the design condition}
 \label{table:extractions_parameter}
@@
 
-\subsection{Thermodynamic metric} %(fold)
+\subsection{Thermodynamic metrics} %(fold)
 \label{ssub3:analsys method} 
 %为了能够对优化系统与参考系统进行评估，揭示系统优化的内在机理，本文引入热力学第二定律的分析方法即用分析方法。
-Exergy analysis, is adopted to reveal the location, the magnitude and the sources of thermodynamic inefficiencies of the unit.
-Usually, exergy destruction and exergy efficiency are chosen as evaluation indices of the thermal system or an individual component, 
-The general exergy balance of component or system can be expressed in the following form:
+Based on the second law of thermodynamics, the exergy analysis method has been widely used in power plant thermal system analysis and optimization~\cite{Si2017Exergy,Yang2013Comprehensive,Ahmadi2016Energy}
+Exergy analysis is adopted to reveal the location, the magnitude, and the sources of a unit's thermodynamic inefficiencies.
+Exergy destruction and exergy efficiency are usually chosen as evaluation indices for the thermal system or an individual component within the system. 
+The general exergy balance of a system or its component can be expressed in the following form:
 \begin{equation}
@@
 
-Exergy efficiency can be calculated in the following form:
+Exergy efficiency can be calculated using the following form:
 \begin{equation}
@@
 \end{equation}
-For different equipment under stable operating conditions, equation~\ref{equation:1}, ~\ref{equation:2} have different forms as shown in Table~\ref{tab:exergy equation}~\cite{Aljundi2009Energy}
+For different equipment under stable operating conditions, Equations~\ref{equation:1} and ~\ref{equation:2} have different forms, as shown in Table~\ref{tab:exergy equation}~\cite{Aljundi2009Energy}
 
@@
 
-For flue gas, air, water and steam, the specific exergy can be calculated by equation~\ref{equation:3}.
+For flue gas, air, water, and steam, the specific exergy can be calculated using Equation~\ref{equation:3}.
 
@@
 \end{equation}
-Then the total exergy rate associated with ﬂuid stream becomes:
+Then the total exergy rate associated with the ﬂuid stream becomes:
+%Should "stream" be replaced by "steam"? 
 \begin{equation}
@@
 \end{equation}
-The fuel specific exergy calculate method~\cite{Yan2016The} can be expressed as.
+The fuel-specific exergy calculation method~\cite{Yan2016The} can be expressed as:
 \begin{equation}
@@
 \end{equation}
-Where LHV refer to lower heating value of fuel, C, H, O, N refer to mass fraction of carbon, hydrogen, oxygen, nitrogen by element analysis.
-More details of power plant equipments' exergy  efficiency calculation can be found in Ref.~\cite{G2016Exergy}
+where LHV refers to the lower heating value of fuel, and C, H, O, and N refer to the mass fractions of carbon, hydrogen, oxygen, and nitrogen according to element analysis.
+More details about the power plant equipment's exergy efficiency calculation can be found in Ref.~\cite{G2016Exergy}
 
-In order to clearly analyze the effect of system optimization, this paper divides the double-reheat USC system into four main subsystems and a sum of all other equipments, valves and pips named "other".
-The four main subsystems are: boiler with out APH, turbines, air preheat subsystem and regenerative subsystem.
-The equations mentioned above can also be used into exergy analysis of these four main subsystems.
-For the "other" part, this paper used counter balance analysis method to calculate its exergy destruction rate, which means subtract the share of the four main subsystems from the total exergy destruction.
-The exergy destruction rate can be calculated by using equation as follows:
+In order to clearly analyze the effects of system optimization, this paper divides the double-reheat USC system into four main subsystems, while all other equipment, valves, and pips is together labeled "other."
+The four main subsystems are the boiler without APH, the turbine, the air preheat subsystem, and the regenerative subsystem.
+The equations mentioned above can be used to perform exergy analyses of these four main subsystems.
+For the "other" category, this paper used a counterbalance analysis method to calculate the exergy destruction rate.
+This meant subtracting the share of the four main subsystems from the total exergy destruction.
+The exergy destruction rate can be calculated as follows:
 
@@
 %对word版本的分布进行了较大的改动，需要继续调节
-\subsection{Thermodynamic comparison in design condition}
+\subsection{Thermodynamic comparison under design condition}
 \label{ssub:desing_compare}
 %表四
-The comparison of thermal dynamic performance between these two systems is given in Table~\ref{table:thermal performance compare}. 
-Under design condition, the novel system brings an improvement of net generating power by 11.02 MW, and reduces SCE consumption by 5.5\,g/kWh.
-The power generation efficiency reaches 48.73\%, and 1.04\% higher then that of reference system.
-Meanwhile, the exergy efficiency of novel system is 1.01\% higher, showing good exergy-saving effect.
+The comparison of the thermal dynamic performances of these two systems is given in Table~\ref{table:thermal performance compare}. %Should this be "thermodynamic" rather than "thermal dynamic"? 
+Under the design condition, the novel system yields an improvement in net generating power of 11.02 MW and reduces SCE consumption by 5.5\,g/kWh.
+Power generation efficiency reaches 48.73\%, which is 1.04\% higher than that of the reference system.
+Meanwhile, the exergy efficiency of the novel system is 1.01\% higher, showing a good exergy-saving effect.
+%"higher than that of the reference system"?
 
@@
 Generating efficiency (\%) & 47.69 & 48.73\tabularnewline
-Addition in generating efficiency (\%) &  & 1.04\tabularnewline
+Addition in generating efficiency (\%) &  & 1.04\tabularnewline %"Increase" rather than "Addition"? 
 Standard coal consumption rate (g/kWh) & 257.59 & 252.10\tabularnewline
@@
 Exergy efficiency (\%) & 46.51 & 47.52\tabularnewline
-Addition in exergy efficiency (\%) &  & 1.01\tabularnewline
+Increase in exergy efficiency (\%) &  & 1.01\tabularnewline
 \bottomrule
@@
 % 根据用损失对比表从新进行分析，从为什么锅炉空预器效率提高，其他不变或者降低说起
-Table~\ref{table:system exergy campare} gives the results of subsystem exergy analysis of the two system. 
-It is found that the novel system has an improvement in exergetic performance by an decrease of 10.82\,MW of total exergy destruction rate.
-Exergy destruction rate of boiler accounts for the highest proportion and decrease most (11.04\,MW).
-Air preheat subsystem's exergy destruction rate changes from 27.39\,MW to 16.55\,MW, having a 10.84\,MW decrement, having the largest Optimization ratio.
-In the mean time, turbines and regenerative subsystem have a relatively small change at about 1\,MW.
+Table~\ref{table:system exergy campare} shows the results of the subsystem exergy analysis of the two systems. 
+It was found that the novel system yields an improvement in exergetic performance by a decrease of 10.82\,MW in the total exergy destruction rate.
+The exergy destruction rate of the boiler accounts for the highest proportion and decreases most (11.04\,MW). %Highest proportion of what? Decrease of what?
+The air preheat subsystem's exergy destruction rate changes from 27.39\,MW to 16.55\,MW, having a 10.84\,MW decrement and the largest optimization ratio. %What is "decrement"?
+In the meantime, the turbine and regenerative subsystem experience a relatively small change at about 1\,MW.  %Do they each have a change or do they together have one change?
 
-The item "other" of novel system is higher then reference system, showing that the uncalculated components of systems have a increment of exergy destruction rate.
-Among the uncalculated components, the pips' amount increasing and  parameters unmatched work fluid mixing are the main reason why that part has a increment in exergy destruction rate.
+The "other" category of the novel system is higher
+%higher in what?
+than that of the reference system, showing that the uncalculated components of systems have an increment of exergy destruction rate. %What is "an increment of exergy destruction rate"?
+Among the uncalculated components, the pips' increase and parameters unmatched work fluid mixing
+%I'm not sure what "parameters unmatched work fluid mixing" means---clarify?
+are the main reasons that that part has an increment in exergy destruction rate.
 
 \begin{table}
-\caption{Exergy destruction rate comparison of reference and novel systems }
+\caption{Exergy destruction rate comparison for reference and novel systems }
 \label{table:system exergy campare}
@@
 \toprule 
-Items & Reference System\,(MW) & Novel System\,(MW)\tabularnewline
+Items & Reference system\,(MW) & Novel system\,(MW)\tabularnewline
 \midrule 
-Boiler(without AP) & 883.26 & 872.22\tabularnewline
+Boiler (without AP) & 883.26 & 872.22\tabularnewline
 Turbine & 63.33 & 63.97\tabularnewline
@@
 %本文是针对空预系统和回热系统的联合优化改造，所以本文将新系统和参考系统中的差变化，系统中设备的效率和用损变化进行了分析。
-To get in-depth analysis of both systems, research of the mainly optimized subsystems: air preheat subsystem and regenerative subsystem was conducted.
-Table~\ref{table:extraction_compare} gives the variation of mass flow rate of extractions.
-As illustrated in Table~\ref{table:extraction_compare}, mass flow rate of the 1st, 3rd, 5th and 8th extractions of the novel system is more than that of the reference system, and the rest extractions except the last two, has the opposite variation.
-It can be found that the impact of system optimization on extraction is twofold: air is heated by extractions, which will cause an increment in mass flow, and the use of LPE can saves extractions so the total extraction mass flow keeps almost unchanged.
+To gain an in-depth understanding of both systems, a study of the main optimized subsystems, the air preheat subsystem, and the regenerative subsystem, was conducted.
+Table~\ref{table:extraction_compare} shows the variations in the mass flow rates of extractions.
+As illustrated in Table~\ref{table:extraction_compare}, the mass flow rates of the first, third, fifth, and eighth extractions of the novel system were greater than those of the reference system, and the rest of the extractions, with the exception of the final two, showed the opposite variation.
+%What does "the opposite variation" mean?
+Thus, the impact of system optimization on extraction is twofold: air is heated by extractions, which causes an increment in mass flow, and the use of LPE can save extractions so the total extraction mass flow remains nearly unchanged.
+%What does it mean to "save extractions"?
 
-The sum of 4th to 10th extractions mass flow increases from 138.46 kg/s to 145.07 kg/s, and the 8th extraction increase 13.9 kg/s.
-The mass flow increase of low pressure extractions implies that novel system can modify the quantity distribution of extractions.
+The sum of the increase in mass flow for the fourth to tenth extractions ranges from 138.46 kg/s to 145.07 kg/s, while the eighth extraction increases by 13.9 kg/s.
+The mass flow increase for the low-pressure extractions implies that the novel system can modify the quantity distribution of extractions.
 
@@
 \begin{table}
-\caption{Extractions comparison of reference and novel systems}
+\caption{Extraction comparison between reference and novel systems}
 \label{table:extraction_compare}
@@
 
-Air is heated by the EAPHs and AOCs in novel system from 23$^\circ$C to 363.33$^\circ$C. 
-A majority of outlet air of EAPH6 is send to miler as primary air, and rest of air is heated to 363.33$^\circ$C.
-Fig.~\ref{fig:APH_temper_compare} shows air preheat process' temperature difference between hot and cold fluid of novel and reference systems.
-The red triangle and red hollow triangle instead for steam average temperature of EAPH and AOC. 
-In order to simplify the diagram, using saturate temperature of steam instead of EAPH's average temperature and using mean temperature of inlet and outlet as AOC's average temperature.
-The figure indicates that  temperature difference of EAPHs is lower than that of APH, which makes exergy efficiency's improvement.
-The AOCs' temperature difference is high, but heat exchange is relatively small, so does the exergy destruction. 
-So the air preheat subsystem  of novel system has a smaller exergy destruction rate and improvement on exergy efficiency.
-One the other hand, The total heat exchange and secondary air temperature of novel system is higher then these of reference system, which make the boiler's exergy efficiency's improvement.
+Air is heated by the EAPHs and AOCs in the novel system from 23$^\circ$C to 363.33$^\circ$C. 
+A majority of the outlet air of EAPH6 is sent to miler as primary air, and the rest of the air is heated to 363.33$^\circ$C. %What does "miler" mean?
+Fig.~\ref{fig:APH_temper_compare} shows the air preheat process's temperature difference between the hot and cold fluid of the novel and reference systems.
+The red triangle and the red hollow triangle instead for the average steam temperature of EAPH and AOC.
+%I'm not sure what "instead" means in the above sentence. Could you clarify?
+In order to simplify the diagram, the saturate temperature of steam instead of the EAPH's average temperature can be used.
+The mean temperature of the inlet and outlet should be used as the AOC's average temperature.
+The figure indicates that the temperature difference of EAPHs is lower than that of APH, which suggests an improvement in exergy efficiency.
+The AOCs' temperature difference is high, but as the heat exchange is relatively small, so is the exergy destruction. 
+Therefore, the air preheat subsystem of the novel system has a lower exergy destruction rate and improved exergy efficiency.
+On the other hand, the total heat exchange and secondary air temperature of the novel system are higher than those of the reference system, which indicates improvement in the boiler's exergy efficiency.
 
@@
 \includegraphics[width=0.6\textwidth]{fig/APH_temper_compare.png}
-\caption{T-Q diagram of Air preheat subsystems} 
+\caption{T-Q diagram of air preheat subsystems} 
 \label{fig:APH_temper_compare}
@@
 
-Fig.~\ref{fig:APH_temper_compare} shows EAPHs and AOCs's exergy analysis results. 
-Except EAPH8，the exergy efficiency of EAPHs and AOCs is higher than 82\%, and the APH8 has the greatest exergy loss and lowest efficiency of all the air preheaters. 
-According with Fig.~\ref{fig:APH_temper_compare}, the heat transfer temperature difference of EAPH8 is 26.95 $^\circ$C,and it has a larger heat exchanging quantity, both of which cause higher exergy destruction and exergy efficiency.
-It also indicates that, although the AOCs have large heat transfer temperature difference, their exergy efficiencies are still high and  exergy destruction rates are low.
+Fig.~\ref{fig:APH_temper_compare} shows EAPHs and AOCs' exergy analysis results. 
+With the exception of EAPH8，the EAPHs and AOCs have exergy efficiency values higher than 82\%. APH8 has the greatest exergy loss and lowest efficiency of all the air preheaters. 
+According to Fig.~\ref{fig:APH_temper_compare}, the heat transfer temperature difference of EAPH8 is 26.95 $^\circ$C,and EAPH8 has a greater heat exchanging quantity, both of which cause higher exergy destruction and exergy efficiency.
+%Less exergy efficiency?
+This also indicates that although the AOCs have a large heat transfer temperature difference, their exergy efficiencies are still high and their exergy destruction rates are low.
 
-Combing Fig.~\ref{fig:APH_temper_compare}  and Fig.~\ref{fig:novel_APH_exergy}, the reason why the novel system's air preheat subsystem have a higher exergy efficiency and lower exergy destruction rate can be drawn that the novel system's air preheat subsystem has a lower heat transfer temperature difference and reasonable extractions' superheat degree using.
+Combining Fig.~\ref{fig:APH_temper_compare} and Fig.~\ref{fig:novel_APH_exergy}, we can see that the reason that the novel system's air preheat subsystem
+%Should this be "subsystems," plural?
+have a higher exergy efficiency and lower exergy destruction rate is that the novel system's air preheat subsystem has a lower heat transfer temperature difference and reasonable extractions' superheat degree using.
+%I'm not sure what the final part of this sentence means. What is "reasonable extractions' superheat degree using"? Is there a word missing?
 
@@
 \includegraphics[width=0.8\textwidth]{fig/novel_APH_exergy.png}
-\caption{Exergy destruction and efficiency of air preheat subsystem of novel system} %图中的纵坐标需要修改
+\caption{Exergy destruction and efficiency of the novel system's air preheat subsystem} %图中的纵坐标需要修改
 \label{fig:novel_APH_exergy}
@@
 
-The regenerative subsystem of novel system uses LEPS paralleled connected with EAPH to absorb economizer outlet flue heat, and eliminates the AOCs originally used to heat feedwater.
-LPE inlet water are heated to the outlet temperature of corresponding RH outlet temperature of to mix up.
-With the extractions' parameters keeping still, the average heat transfer temperature difference of RHs change little.
-So their exergy efficiency keeps the same with reference system.
+The regenerative subsystem of the novel system uses LEPS
+%Should this be "LPEs"? Or if this is a new acronym, write out on first usage.
+paralleled connected with EAPH to absorb the economizer's outlet flue heat and eliminate the AOCs originally used to heat feedwater.
+%What does "paralleled connected" mean?
+LPE inlet water is heated to the temperature of the corresponding RH outlet temperature of to mix up.
+%What does "of to mix up" mean?
+Keeping the extractions' parameters constant, the average heat transfer temperature difference of the RHs changes little.
+This means that their exergy efficiency is the same as that of the reference system.
 
-Fig.~\ref{fig:regenerative_subsys_compare} shows the regenerative subsystem's exergy destruction rate distribution comparison between the two systems.
-It can be found that the novel system's exergy destruction rate has a decrease and great changes have taken place in the destruction's distribution.
-In consequence of the flow diverting effects of LEPs, the exergy destruction rate of regenerative reheaters and DEA changes from 20.16 MW to 11.303 MW.
-The LEPs exergy destruction rate reach to 10.25 MW, and Fig.~\ref{fig:LPE_exergy_LMDT} shows the LEPs' exergy efficiency and heat transfer LMTD.
+Fig.~\ref{fig:regenerative_subsys_compare} shows the regenerative subsystem's exergy destruction rate distribution between the two systems.
+It can be seen that the novel system's exergy destruction rate decreased and great changes have taken place in the destruction's distribution.
+Because of the flow-diverting effects of LEPs,%LPEs?
+the exergy destruction rate of regenerative reheaters and DEA changes from 20.16 MW to 11.303 MW.
+%What does "DEA" stand for?
+The LEPs' %LPEs?
+exergy destruction rate reaches 10.25 MW, and Fig.~\ref{fig:LPE_exergy_LMDT} shows the LEPs'
+%LPEs?
+exergy efficiency and heat transfer LMTD.
 As shown in Fig.~\ref{fig:LPE_exergy_LMDT}, the highest efficiency one is LPE1 with 93.50\%, and the lowest efficiency one is LPE4 with 87.44\%. 
-The LEPs' overall exergy efficiency is 91.62\%, much higher than that of flu-air heat transfer of reference system, and the temperature difference of the LPEs is between 23$^\circ$C to 42$^\circ$C.
+The LEPs'
+%LPEs'?
+overall exergy efficiency is 91.62\%, which is much higher than that of the flue-air heat transfer of the reference system, and the temperature difference of the LPEs is between 23$^\circ$C and 42$^\circ$C.
 
@@
 
-\subsection{Thermodynamic comparison in off-design conditions}
+\subsection{Thermodynamic comparison under off-design conditions}
 \label{ssub:offdesing_compare}
-Considering that large USC power plants' operation under partial load conditions, it is necessary to study the thermal performance of double reheat USC power plants under off-design conditions.
-Four typical operation conditions, THA load, 75\% THA load, 50\% THA load, and 40\% THA load conditions, were chosen for thermodynamic analyses. 
-Fig.~\ref{fig:partload_efficiency} shows novel and reference systems' exergy efficiency under different load conditions.The exergy efficiencies of both systems decrease as the load decrease.
-The exergy efficiencies of both systems are 47.52\% and 46.51\% under THA load condition.
-Compared with reference system, novel system's exergy efficiency has the increment of 1.01 percentage points, and reduces SCE consumption by 5.5\,g/kWh.
-Under the 75\% THA condition, the optimized system was 46.56\% and the reference system was 45.90\%, the exergy
-efficiency decrease to 0.66\%. 
+Given large USC power plants' operation under partial load conditions, it is necessary to study the thermal performance of double-reheat USC power plants under off-design conditions.
+Four typical operation conditions--THA load, 75\% THA load, 50\% THA load, and 40\% THA load--were chosen for thermodynamic analysis. 
+Fig.~\ref{fig:partload_efficiency} shows the novel and reference systems' exergy efficiency under different load conditions. The exergy efficiencies of both systems decrease as the load decreases.
+The exergy efficiencies of the systems are 47.52\% and 46.51\% under the THA load condition.
+Compared with the reference system, the novel system's exergy efficiency has the increment of 1.01 percentage points and reduces SCE consumption by 5.5\,g/kWh.
+%What does "has the increment of 1.01" mean?
+Under the 75\% THA load condition, the optimized system %The exergy destruction rate of the optimized system?
+is 46.56\% and the reference system is 45.90\%, and exergy efficiency decreases to 0.66\%. 
 When the load is equal to 50\% THA, the efficiency difference is 0.43\%.
-This implies that the novel system can increase exergy efficiency under partial load, but it has more advantages for double reheat power plant undertaking base load.
+This implies that the novel system can increase exergy efficiency under partial load, but it has more advantages for double-reheat power plants with base loads.
 
@@
 \includegraphics[width=0.6\textwidth]{fig/partload_efficiency.png}
-\caption{Exergy efficiency comparison in off-design conditions} 
+\caption{Exergy efficiency comparison under off-design conditions} 
 \label{fig:partload_efficiency}
 \end{figure}
-  exergy destruction ratio ($y_{D}$) is used to measure the exergy destruction of 1\,MW power generation of unit by a subsystem, and its calculate formula is as follow:
+  The exergy destruction ratio ($y_{D}$) is used to measure the exergy destruction of a 1\,MW power generation of a unit by a subsystem. It is calculated as follows:
 \begin{equation}
@@
 % 同时需要指出，由于锅炉本身的用损失很大，所以变负荷对锅炉本身用效率影响很小,而对空预子系统的影响较大。
-A large exergy destruction ratio value indicates that the subsystem has more significant energy-saving effects and contributes more to the exergy-saving effect of the entire system.
-Fig.~\ref{fig:partload_subsys_exergyrate} shows the  exergy destruction ratio difference ($y_{D,reference}-y_{D,novel}$) between reference system and novel system.
-It indicates that the contribution of energy-saving effect decrease as follows: the boiler, air preheat subsystem, regenerative subsystem and steam turbine.
-As the load decreases from THA load condition, it can be seen that the load change has the greatest effect on the boiler, while the change of load condition barely affects the steam turbine.
-While the load is reduced to 40\%THA, the four subsystems of the novel system are still have lower exergy destruction rate than those of the reference system.
-However the calculated value of these subsystem decrease and exergy destruction rate increase of other uncalculated components make the novel system's exergy-saving effect decrease.
-According to the data of Table~\ref{table:system exergy campare}, it should be pointed out that due to the great exergy destruction of the boiler, the decrease of load has little effect on the exergy efficiency of it.But the air preheat subsystem is most effected.
+A large exergy destruction ratio value indicates that the subsystem has more significant energy-saving effects and contributes more to the exergy-saving effects of the entire system.
+Fig.~\ref{fig:partload_subsys_exergyrate} shows the exergy destruction ratio difference ($y_{D,reference}-y_{D,novel}$) between the reference system and the novel system.
+This indicates that the contribution to energy-saving effects decreases as follows: the boiler, the air preheat subsystem, the regenerative subsystem, and the steam turbine.
+As the load decreases from the THA load condition, it can be seen that the load change has the greatest effect on the boiler, while the change in the load condition barely affects the steam turbine.
+When the load is reduced to 40\%THA, the four subsystems of the novel system still have lower exergy destruction rates than those of the reference system.
+However, the calculated values of these subsystem decrease, 
+%Do the edits to the above sentence look right to you?
+and the exergy destruction rate increase among the other uncalculated components causes the novel system's exergy-saving effects to decrease.
+According to the data presented in Table~\ref{table:system exergy campare}, given the great exergy destruction of the boiler, the decrease in load has little effect on the boiler's exergy efficiency.
+The air preheat subsystem experiences the greatest effect.
 
@@
 \includegraphics[width=0.6\textwidth]{fig/partload_subsys_exergyrate.png}
-\caption{Exergy destruction rate difference of subsystems in off-design conditions} 
+\caption{Difference in subsystems' exergy destruction rates under off-design conditions} 
 \label{fig:partload_subsys_exergyrate}
@@
 %文章干了什么
-A novel system for a 1000\,MW double reheat ultra-supercritical unit is proposed which use turbine extractions to preheat air and low pressure economizers to replace air preheater originally installed in vertical shaft.
-Thermodynamic analysis is conducted to reveal the energy-saving effects and thermal performance changes of key components. 
-The novel system is found to be effective in overcoming the imperfections, and may provide an effective method for the optimization of  double reheat USC unit.
-The following conclusions are drawn from this study: 
+This paper proposed a novel system for a 1000\,MW double-reheat ultra-supercritical unit that uses turbine extractions to preheat air and low-pressure economizers to replace the air preheater originally installed in vertical shaft.
+Thermodynamic analysis was conducted to reveal the energy-saving effects and thermal performance changes of key components. 
+The novel system was found to be effective in overcoming the imperfections
+%"overcoming the reference system's imperfections"? 
+and may prove an effective method for the optimization of the double-reheat USC unit.
+The following conclusions can be drawn from this study: 
  \begin{enumerate}[(1)]
- \item The novel system can improve power generation efficiency to 48.73\%, which is 1.04 percent higher then the reference system under design condition.And the exergy efficiency of novel system is 47.52\%, which is 1.01 percentage higher then the reference system.
- \item The thermodynamic analysis indicates that the novel system decreases the temperature difference of air/flue-gas heat transfer process which achieves the cascaded utilization of energy, and the superheat degree of the 3rd and 5th is reduced greatly.
-\item The novel system changes the mass flow rates distribution of extractions, which causes increment of output power of the generator by 12.09 MW 
-\item The novel system improves the temperature of secondary air, which improves the fire condition in the combustion chamber.
- The temperature of secondary air of reference system under full load is 365$^\circ$C, which is 34$^\circ$C higher than the reference system.
-\item The novel system theoretically brings remarkable energy saving effects even under off-design conditions.
-The simulation results show that the optimization system can reduce the SCE consumption by 5.49 g/kWh under design condition, and can even bring a reduction of 2.9 g/kWh under 50\% THA load.
+ \item The novel system can improve power generation efficiency up to 48.73\%, which is 1.04 percent higher than that of the reference system under the design condition.
+The exergy efficiency of the novel system is 47.52\%, which is 1.01 percent higher than that of the reference system.
+ \item Thermodynamic analysis indicates that the novel system leads to a decrease in the temperature difference of the air/flue-gas heat transfer process, leading to the cascaded utilization of energy and great reductions in the superheat degree of the third and fifth.
+ %"third and fifth extractions"?
+\item The novel system changes the mass flow rates of the distribution of extractions, which causes an increment of output power of the generator by 12.09 MW.
+%I'm not sure what this sentence means.
+What does it mean to "cause an increment of output power"?
+Is output power increasing?
+\item The novel system improves the temperature of the secondary air, which improves the fire condition in the combustion chamber.
+ The temperature of the secondary air of the reference system under full load is 365$^\circ$C, which is 34$^\circ$C higher than that of the reference system.
+\item The novel system theoretically yields remarkable energy-saving effects even under off-design conditions.
+The simulation results show that the optimized system can reduce SCE consumption by 5.49 g/kWh under the design condition and can even lead to a reduction of 2.9 g/kWh under 50\% THA load.
 \end{enumerate}
 \section*{Acknowledgments}
-This study is supported by National Basic Research Program of China (Grant No. 2015CB251504).
+This study was supported by the National Basic Research Program of China (Grant No. 2015CB251504).
 \section*{References}

### 2018-02-25 article.tex
对润色版本中提出的问题进行了修改

@@
 \author[hust]{Jiayi Zhao}
-\author[hust]{Tao Yang\corref{cor1}} %I am not sure how to delete the extra comma after Yang's name--there is a comma after the "a" superscript that needs to be removed.
+\author[hust]{Tao Yang\corref{cor1}}
 \ead{hust\_yt@hust.edu.cn}	
@@
 
-\begin{abstract}%修改到300字以内
+\begin{abstract}
 The double-reheat ultra-supercritical (USC) unit has received significant attention because of its high efficiency and energy-saving effects.
@@
 Furthermore, the novel system increased the temperature of secondary air and reduced the overall superheat degree of several extractions.
-Theoretically, with an overall exergy efficiency of 48.73\%, the novel system can reduce SCE
-%I don't think the "SCE" acronym has been introduced yet. Write it out in full here? 
-consumption by nearly 5.5\,g/kWh under the THA load
-%Same for THA---write out in full?
-if the temperature of the flue gas entering the electrostatic precipitator is set to 95$^\circ$C.
+Theoretically, with an overall exergy efficiency of 48.73\%, the novel system can reduce standard coal equivalent consumption by nearly 5.5\,g/kWh under the turbine heat acceptance load if the temperature of the flue gas entering the electrostatic precipitator is set to 95$^\circ$C.
 Moreover, the novel system has advantages for coal-saving under the partial load condition.
@@
 According to Ref.~\cite{Wu2014Component}, component- and process-based exergy evaluations were performed on a coal-fired power plant in China, thereby helping researchers to identify energy-saving strategies.
-It was pointed out that the exergy destruction in the heat transfer process accounts for the largest proportion.
-%largest proportion of what? Of exergy destruction overall?
+It was pointed out that the exergy destruction in the heat transfer process accounts for the largest proportion of exergy destruction overall.
 
@@
 Li et al.~\cite{Li2014Thermodynamic} proposed a system that uses ten-stage extractions and two outer steam coolers. 
-The results of the thermodynamic and techno-economic analyses showed that this system can lower the cost of electricity to 55.89 USD/MWh.
+The results of the thermodynamic and Technical-economic analyses showed that this system can lower the cost of electricity to 55.89 USD/MWh.
 In addition, Kjaer~\cite{Kjaer2010A} proposed a regenerative steam turbine for utilizing the superheat degree of the extractions.
@@
 Four possible arrangements for LPE installation were proposed and their energy-saving effects were compared.
-The results indicated that the LPE connected with the higher-temperature section of the condensate line created a greater reduction in the standard coal equivalent (SCE). %"greatest"? 
+The results indicated that the LPE connected with the higher-temperature section of the condensate line created a greatest reduction in the standard coal equivalent (SCE).  
 Wang et al.~\cite{Wang2012Application} investigated energy- and water-saving measures and the reduction of CO$_2$ after the installation of an LPE.
@@
 Xu et al.~\cite{Xu2013A} divided the air preheater into two stages to reduce the temperature difference in the heat transfer process.
-%"divided the air preheater process"? Or was the preheater itself actually divided?
 A LPE was also installed between the two air preheaters to obtain an appropriate flue gas temperature range.
-Thermodynamic and technic-economic analyses were conducted to reveal the performance improvement.
-It was found that the SCE consumption was reduced by 6.7\,g/kWh. %"techno-economic" is used earlier in the paper. Which expression is correct?
+Thermodynamic and technical-economic analyses were conducted to reveal the performance improvement.
+It was found that the SCE consumption was reduced by 6.7\,g/kWh.
 
-The installation of an LPE has some other benefits, such as improvements in electrostatic precipitator collection efficiency~\cite{Li2016Low}.
+The installation of an LPE also has some  other benefits, such as improvements in electrostatic precipitator collection efficiency~\cite{Li2016Low}.
 
@@
 \label{sec2:system intro}
-\subsection{Reference system in operation} % (fold)
+\subsection{Reference system in operation}
 \label{sub2:ref intro}
@@
 \end{figure}
-%从参考系统的锅炉虽然仍然采用Π型布置，但其内部受热面和传统一次再热锅炉有较大区别。
+
 The system's boiler heat transfer surface arrangement is shown in Fig.~\ref{fig:boiler_surface}. 
@@
 After Hsf and Hss, the flue gas channel is divided into the front-duct flue and the back-duct flue.
-The front duct arranges the first low-temperature reheater (Ltfr) and the front-duct economizer (Feco).
-The back duct arranges the second low-temperature reheater (Ltsr) and the back-duct economizer (Beco).
-The air preheater (APH) is arranged in the vertical shaft. %What does "arranges" mean in these sentences?
+The first low-temperature reheater (Ltfr) and the front-duct economizer (Feco) is arranged in the front duct.
+The second low-temperature reheater (Ltsr) and the back-duct economizer (Beco) is arranged The back duct .
+The air preheater (APH) is arranged in the vertical shaft.
 
@@
 The AOCs in the reference system are designed to heat feedwater.
-Although AOC inlet steam has a great supper heat degree %superheat?
-, the small amount of heat exchanged makes the feedwater's temperature rise only slightly.
+Although AOC inlet steam has a great superheat degree, the small amount of heat exchanged makes the feedwater's temperature rise only slightly.
 The LMTD is very high in AOCs.
 
-To reduce rise AOCs' exergy efficiency and the superheat degree of extractions entering the heat exchangers,
-%Here do you mean to "reduce the possibility of an increase in AOCs'..."?
+To rise AOCs' exergy efficiency and to reduce the superheat degree of extractions entering the heat exchangers,
 four additional outer steam coolers (AOC1-AOC4) are installed at the air side outlet of EAPH1.
@@
 For example, the second extraction has the highest temperature and is applied to heat the air in the first AOC.
-Then the cooled steam from AOC1 is sent to HRH2 and air EAPH2 to heat the water and air, respectively.
-%Should "air EAPH2" be simply "EAPH2"?
+Then the cooled steam from AOC1 is sent to HRH2 and EAPH2 to heat the water and air, respectively.
 
@@
 \centering
-\includegraphics[width=0.3\textwidth]{fig/extracion_heat_APH.png}%extraction_heat_APH
+\includegraphics[width=0.3\textwidth]{fig/extracion_heat_APH.png}
 \caption{Process flow diagram of RH and EAPH} 
@@
 Because of the removal of the APH originally installed in the vertical shaft, the flue gas's heat needs to be absorbed by other means.
-As shown in Fig.~\ref{fig:novel_system}, the flue gas at the outlet of the economizer is utilized by four LPEs to heat the condensate and feedwater; these LPEs are parallel to HRH2, HRH4, LRH6, and LRH8, respectively.
-%Rather than "are parallel to," perhaps "correspond with"?
+As shown in Fig.~\ref{fig:novel_system}, the flue gas at the outlet of the economizer is utilized by four LPEs to heat the condensate and feedwater; these LPEs are correspond with HRH2, HRH4, LRH6, and LRH8, respectively.
 Part of the condensate and feedwater at the inlet of the regenerative heater is sent to the LPE; then the heated water joins with the corresponding regenerative heater's outlet water. 
@@
 
-% \section{Model establishment and thermodynamic evaluation} % (fold)
-% \label{sec3:modle est and eval}
 \section{Model description and thermodynamic metrics}
@@
 \label{ssub3:modle description}
-%对模型中如何基于现有系统进行的改造，和哪些数据不发生变化进行说明
-%添加模型中基本部件的特性 添加个表格
+
 In this paper, the thermodynamic cycle of the thermal system under different loads is simulated using EBSILON® Professional.
@@
 Because it is designed based on the reference system, the novel system's main input parameters (such as live steam parameters, first/second reheat steam parameters, and turbine extraction parameters) remain the same as those that are shown in Table~\ref{tab:ref input} and Table~\ref{table:extractions_parameter}.
-Based on the practice,
-%What is "the practice"? 
-the upper temperature differences of the novel system's LPE, AOC and EAPH are settled to 30$^\circ$C, 20$^\circ$C, and 5$^\circ$C. 
+According to the experience of engine, the upper temperature differences of the novel system's LPE, AOC and EAPH are settled to 30$^\circ$C, 20$^\circ$C, and 5$^\circ$C. 
 The details of the model's other main components are given in Table~\ref{table:model_details}.
@@
 However, only the turbine's off-design characteristic curves can actually be obtained, while the data for the boiler and heat exchangers cannot be determined.
-This data thus has to be replaced by built-in data.
-It is necessary to assume the difference between the built-in data and the actual data to meet the error requirements.
-%What assumption is being made about the difference in the line above?
+This data thus has to be replaced by software built-in data.
 The following assumptions need to be made in order to be able to correctly perform a simulation.
@@
 \end{enumerate}
-A more detailed description of the thermaldynamic model of the components can be found in Ref.~\cite{Yao2017Multi}. %Should this be "thermodynamic," rather than "thermaldynamic"?
-
+A more detailed description of the thermodynamic model of the components can be found in Ref.~\cite{Yao2017Multi}. 
 \begin{table}
@@
 
-\subsection{Thermodynamic metrics} %(fold)
+\subsection{Thermodynamic metrics} 
 \label{ssub3:analsys method}
-%为了能够对优化系统与参考系统进行评估，揭示系统优化的内在机理，本文引入热力学第二定律的分析方法即用分析方法。
+
 Based on the second law of thermodynamics, the exergy analysis method has been widely used in power plant thermal system analysis and optimization~\cite{Si2017Exergy,Yang2013Comprehensive,Ahmadi2016Energy}
@@
 \end{equation}
-Then the total exergy rate associated with the ﬂuid stream becomes:
-%Should "stream" be replaced by "steam"? 
+Then the total exergy rate associated with ﬂuid becomes:
+
 \begin{equation}
@@
 \label{sub:Thermodynamic_evaluation}
-%对word版本的分布进行了较大的改动，需要继续调节
+
 \subsection{Thermodynamic comparison under design condition}
 \label{ssub:desing_compare}
-%表四
-The comparison of the thermal dynamic performances of these two systems is given in Table~\ref{table:thermal performance compare}. %Should this be "thermodynamic" rather than "thermal dynamic"? 
+
+The comparison of the thermodynamic performances of these two systems is given in Table~\ref{table:thermal performance compare}.
 Under the design condition, the novel system yields an improvement in net generating power of 11.02 MW and reduces SCE consumption by 5.5\,g/kWh.
 Power generation efficiency reaches 48.73\%, which is 1.04\% higher than that of the reference system.
-Meanwhile, the exergy efficiency of the novel system is 1.01\% higher, showing a good exergy-saving effect.
-%"higher than that of the reference system"?
+Meanwhile, the exergy efficiency of the novel system is 1.01\% higher than that of the reference system too, showing a good exergy-saving effect.
 
@@
 Generating efficiency (\%) & 47.69 & 48.73\tabularnewline
-Addition in generating efficiency (\%) &  & 1.04\tabularnewline %"Increase" rather than "Addition"? 
+Increase in generating efficiency (\%) &  & 1.04\tabularnewline 
 Standard coal consumption rate (g/kWh) & 257.59 & 252.10\tabularnewline
@@
 \end{table}
-% 根据用损失对比表从新进行分析，从为什么锅炉空预器效率提高，其他不变或者降低说起
+
 Table~\ref{table:system exergy campare} shows the results of the subsystem exergy analysis of the two systems. 
 It was found that the novel system yields an improvement in exergetic performance by a decrease of 10.82\,MW in the total exergy destruction rate.
-The exergy destruction rate of the boiler accounts for the highest proportion and decreases most (11.04\,MW). %Highest proportion of what? Decrease of what?
-The air preheat subsystem's exergy destruction rate changes from 27.39\,MW to 16.55\,MW, having a 10.84\,MW decrement and the largest optimization ratio. %What is "decrement"?
-In the meantime, the turbine and regenerative subsystem experience a relatively small change at about 1\,MW.  %Do they each have a change or do they together have one change?
+The exergy destruction rate of the boiler accounts for the highest proportion of overall and its exergy destruction rate drops most (11.04\,MW).
+The air preheat subsystem's exergy destruction rate changes from 27.39\,MW to 16.55\,MW, having a 10.84\,MW decline and the largest optimization ratio. 
+In the meantime, the turbine and regenerative subsystem experience a relatively small change of exergy destruction rate, and the value of each is at about 1\,MW.
+%Do they each have a change or do they together have one change?
 
-The "other" category of the novel system is higher
-%higher in what?
-than that of the reference system, showing that the uncalculated components of systems have an increment of exergy destruction rate. %What is "an increment of exergy destruction rate"?
-Among the uncalculated components, the pips' increase and parameters unmatched work fluid mixing
-%I'm not sure what "parameters unmatched work fluid mixing" means---clarify?
-are the main reasons that that part has an increment in exergy destruction rate.
+The exergy destruction rate of "other" category of the novel system is higher than that of the reference system, showing that the uncalculated components of systems have an increase of exergy destruction rate.
+Among the uncalculated components, the number of pips' increase and work fluids' mixing in the valves are the main reasons that that part has an increment in exergy destruction rate.
 
@@
 
-% 下面两段话需要根据图修改
-
-%本文是针对空预系统和回热系统的联合优化改造，所以本文将新系统和参考系统中的差变化，系统中设备的效率和用损变化进行了分析。
 To gain an in-depth understanding of both systems, a study of the main optimized subsystems, the air preheat subsystem, and the regenerative subsystem, was conducted.
 Table~\ref{table:extraction_compare} shows the variations in the mass flow rates of extractions.
-As illustrated in Table~\ref{table:extraction_compare}, the mass flow rates of the first, third, fifth, and eighth extractions of the novel system were greater than those of the reference system, and the rest of the extractions, with the exception of the final two, showed the opposite variation.
-%What does "the opposite variation" mean?
-Thus, the impact of system optimization on extraction is twofold: air is heated by extractions, which causes an increment in mass flow, and the use of LPE can save extractions so the total extraction mass flow remains nearly unchanged.
-%What does it mean to "save extractions"?
+As illustrated in Table~\ref{table:extraction_compare}, the mass flow rates of the first, third, fifth, and eighth extractions of the novel system were greater than those of the reference system, and the rest of the extractions except the final two ones were lower then those of the reference system.
+Thus, the impact of system optimization on extraction is twofold: air is heated by extractions, which causes an increase in extractions' mass flow, and the use of LPE can decrease it, so the total extraction mass flow remains nearly unchanged.
 
@@
 
-%新系统优化可二次再热后蒸汽的抽汽，使8th抽汽量增加
 \begin{table}
@@
 Air is heated by the EAPHs and AOCs in the novel system from 23$^\circ$C to 363.33$^\circ$C. 
-A majority of the outlet air of EAPH6 is sent to miler as primary air, and the rest of the air is heated to 363.33$^\circ$C. %What does "miler" mean?
+A majority of the outlet air of EAPH6 is sent to coal pulverizer as primary air, and the rest of the air is heated to 363.33$^\circ$C.
+
 Fig.~\ref{fig:APH_temper_compare} shows the air preheat process's temperature difference between the hot and cold fluid of the novel and reference systems.
-The red triangle and the red hollow triangle instead for the average steam temperature of EAPH and AOC.
-%I'm not sure what "instead" means in the above sentence. Could you clarify?
+The red triangle represent the average steam temperature of EAPH and the red hollow triangle represent the average steam temperature of AOC.
 In order to simplify the diagram, the saturate temperature of steam instead of the EAPH's average temperature can be used.
@@
 With the exception of EAPH8，the EAPHs and AOCs have exergy efficiency values higher than 82\%. APH8 has the greatest exergy loss and lowest efficiency of all the air preheaters. 
-According to Fig.~\ref{fig:APH_temper_compare}, the heat transfer temperature difference of EAPH8 is 26.95 $^\circ$C,and EAPH8 has a greater heat exchanging quantity, both of which cause higher exergy destruction and exergy efficiency.
-%Less exergy efficiency?
+According to Fig.~\ref{fig:APH_temper_compare}, the heat transfer temperature difference of EAPH8 is 26.95 $^\circ$C,and EAPH8 has a greater heat exchanging quantity, both of which cause higher exergy destruction and less exergy efficiency.
 This also indicates that although the AOCs have a large heat transfer temperature difference, their exergy efficiencies are still high and their exergy destruction rates are low.
 
-Combining Fig.~\ref{fig:APH_temper_compare} and Fig.~\ref{fig:novel_APH_exergy}, we can see that the reason that the novel system's air preheat subsystem
-%Should this be "subsystems," plural?
-have a higher exergy efficiency and lower exergy destruction rate is that the novel system's air preheat subsystem has a lower heat transfer temperature difference and reasonable extractions' superheat degree using.
-%I'm not sure what the final part of this sentence means. What is "reasonable extractions' superheat degree using"? Is there a word missing?
+Combining Fig.~\ref{fig:APH_temper_compare} and Fig.~\ref{fig:novel_APH_exergy}, we can see that the reason that the novel system's air preheat subsystem has a higher exergy efficiency and lower exergy destruction rate is that the novel system's air preheat subsystem has a lower heat transfer temperature difference and the extractions' steam superheat is effectively used.
 
@@
 \includegraphics[width=0.8\textwidth]{fig/novel_APH_exergy.png}
-\caption{Exergy destruction and efficiency of the novel system's air preheat subsystem} %图中的纵坐标需要修改
+\caption{Exergy destruction and efficiency of the novel system's air preheat subsystem} 
 \label{fig:novel_APH_exergy}
@@
 
-The regenerative subsystem of the novel system uses LEPS
-%Should this be "LPEs"? Or if this is a new acronym, write out on first usage.
-paralleled connected with EAPH to absorb the economizer's outlet flue heat and eliminate the AOCs originally used to heat feedwater.
-%What does "paralleled connected" mean?
-LPE inlet water is heated to the temperature of the corresponding RH outlet temperature of to mix up.
-%What does "of to mix up" mean?
+The regenerative subsystem of the novel system uses LPES connected parallel with EAPH to absorb the economizer's outlet flue heat and eliminate the AOCs originally used to heat feedwater.
+LPE inlet water is heated to the temperature of the corresponding RH outlet temperature.
 Keeping the extractions' parameters constant, the average heat transfer temperature difference of the RHs changes little.
@@
 It can be seen that the novel system's exergy destruction rate decreased and great changes have taken place in the destruction's distribution.
-Because of the flow-diverting effects of LEPs,%LPEs?
-the exergy destruction rate of regenerative reheaters and DEA changes from 20.16 MW to 11.303 MW.
-%What does "DEA" stand for?
-The LEPs' %LPEs?
-exergy destruction rate reaches 10.25 MW, and Fig.~\ref{fig:LPE_exergy_LMDT} shows the LEPs'
-%LPEs?
+Because of the flow-diverting effects of LPEs,the exergy destruction rate of regenerative reheaters and DEA changes from 20.16 MW to 11.303 MW.
+
+The LPEs exergy destruction rate reaches 10.25 MW, and Fig.~\ref{fig:LPE_exergy_LMDT} shows the LEPs'
 exergy efficiency and heat transfer LMTD.
 As shown in Fig.~\ref{fig:LPE_exergy_LMDT}, the highest efficiency one is LPE1 with 93.50\%, and the lowest efficiency one is LPE4 with 87.44\%. 
-The LEPs'
-%LPEs'?
-overall exergy efficiency is 91.62\%, which is much higher than that of the flue-air heat transfer of the reference system, and the temperature difference of the LPEs is between 23$^\circ$C and 42$^\circ$C.
+The LPEs' overall exergy efficiency is 91.62\%, which is much higher than that of the flue-air heat transfer of the reference system, and the temperature difference of the LPEs is between 23$^\circ$C and 42$^\circ$C.
 
@@
 Given large USC power plants' operation under partial load conditions, it is necessary to study the thermal performance of double-reheat USC power plants under off-design conditions.
-Four typical operation conditions--THA load, 75\% THA load, 50\% THA load, and 40\% THA load--were chosen for thermodynamic analysis. 
+Four typical operation conditions--turbine heat acceptance (THA) load, 75\% THA load, 50\% THA load, and 40\% THA load--were chosen for thermodynamic analysis. 
 Fig.~\ref{fig:partload_efficiency} shows the novel and reference systems' exergy efficiency under different load conditions. The exergy efficiencies of both systems decrease as the load decreases.
 The exergy efficiencies of the systems are 47.52\% and 46.51\% under the THA load condition.
-Compared with the reference system, the novel system's exergy efficiency has the increment of 1.01 percentage points and reduces SCE consumption by 5.5\,g/kWh.
-%What does "has the increment of 1.01" mean?
-Under the 75\% THA load condition, the optimized system %The exergy destruction rate of the optimized system?
-is 46.56\% and the reference system is 45.90\%, and exergy efficiency decreases to 0.66\%. 
+Compared with the reference system, the novel system's exergy efficiency has a increase of 1.01 percent and reduces SCE consumption by 5.5\,g/kWh.
+Under the 75\% THA load condition, The exergy destruction rate of the optimized system is 46.56\% and the reference system is 45.90\%, and exergy efficiency decreases to 0.66\%. 
 When the load is equal to 50\% THA, the efficiency difference is 0.43\%.
@@
 
-% 用损率差大表明该子系统的节能效果更显著，同时对整个系统的节能效果贡献更大。
-% 由图10可以得到新系统引起节能效果从大到小依次为：锅炉、空预系统、回热系统和汽轮机。
-% 当负荷从THA逐渐降低可以看到，降负荷对锅炉影响最大，而负荷变化对汽轮机系统影响接近于零。
-% 负荷降低到40%，四个子系统优化效果虽然降低但累计值依然优于参考系统，但由于符合降低引起的oher系统用损失的升高导致优化系统相对与参考系统效率增加为0.01%，几乎没有优化效果
-% 同时需要指出，由于锅炉本身的用损失很大，所以变负荷对锅炉本身用效率影响很小,而对空预子系统的影响较大。
 A large exergy destruction ratio value indicates that the subsystem has more significant energy-saving effects and contributes more to the exergy-saving effects of the entire system.
@@
 When the load is reduced to 40\%THA, the four subsystems of the novel system still have lower exergy destruction rates than those of the reference system.
-However, the calculated values of these subsystem decrease, 
-%Do the edits to the above sentence look right to you?
-and the exergy destruction rate increase among the other uncalculated components causes the novel system's exergy-saving effects to decrease.
+However, the exergy-saving effect of these four subsystems decrease, and the exergy destruction rate increase among the other uncalculated components causes the novel system's exergy-saving effects to decrease.
 According to the data presented in Table~\ref{table:system exergy campare}, given the great exergy destruction of the boiler, the decrease in load has little effect on the boiler's exergy efficiency.
@@
 
-% subsubsection subsubsection_name (end)
+\section{Conclusion}
 
-\section{Conclusion}
-%文章干了什么
 This paper proposed a novel system for a 1000\,MW double-reheat ultra-supercritical unit that uses turbine extractions to preheat air and low-pressure economizers to replace the air preheater originally installed in vertical shaft.
 Thermodynamic analysis was conducted to reveal the energy-saving effects and thermal performance changes of key components. 
-The novel system was found to be effective in overcoming the imperfections
-%"overcoming the reference system's imperfections"? 
+The novel system was found to be effective in overcoming the reference system's imperfections 
 and may prove an effective method for the optimization of the double-reheat USC unit.
@@
 The exergy efficiency of the novel system is 47.52\%, which is 1.01 percent higher than that of the reference system.
- \item Thermodynamic analysis indicates that the novel system leads to a decrease in the temperature difference of the air/flue-gas heat transfer process, leading to the cascaded utilization of energy and great reductions in the superheat degree of the third and fifth.
- %"third and fifth extractions"?
-\item The novel system changes the mass flow rates of the distribution of extractions, which causes an increment of output power of the generator by 12.09 MW.
-%I'm not sure what this sentence means.
-What does it mean to "cause an increment of output power"?
-Is output power increasing?
+ \item Thermodynamic analysis indicates that the novel system leads to a decrease in the temperature difference of the air/flue-gas heat transfer process, leading to the cascaded utilization of energy and great reductions in the superheat degree of the third and fifth extractions.
+\item The novel system changes the mass flow rates of the distribution of extractions, which causes the generator output power increasing by 12.09 MW. 
 \item The novel system improves the temperature of the secondary air, which improves the fire condition in the combustion chamber.

### 2018-02-28 article.tex
LPE改成了LTE

@@
 The double-reheat ultra-supercritical (USC) unit has received significant attention because of its high efficiency and energy-saving effects.
-The optimal design of the unit's thermal system is still under consideration, however.
-In this paper, an optimized system for reasonable fluid heat transfer temperature-matching and higher efficiency is proposed.
-This novel system uses turbine extractions as heat sources for air preheaters and low-pressure economizers to absorb economizer outlet flue gas heat, thereby realizing the joint optimization of the air preheat process and the regenerative system.
+The optimal design of the USC unit's thermal system is still under consideration, however.
+In this paper, an optimized system for reasonable fluid heat transfer temperature-matching and higher efficiency is proposed .
+This novel system uses turbine extractions as heat sources for air preheaters and low-temperature economizers to absorb economizer outlet flue gas heat, thereby realizing the joint optimization of the air preheat process and the regenerative system.
 Models were built to compare the energetic performance of the novel system and that of the reference system.
@@
 In addition, Kjaer~\cite{Kjaer2010A} proposed a regenerative steam turbine for utilizing the superheat degree of the extractions.
-In this design, part of the extraction from the high pressure turbine enters the additional regenerative steam turbine rather than the regenerative heater.
-Extractions from the intermediate pressure turbine are replaced by those from the regenerative steam turbine.
+In this design, part of the extraction from the turbine high pressure cylinder enters the additional regenerative steam turbine rather than the regenerative heater.
+Extractions from the turbine intermediate pressure cylinder are replaced by those from the regenerative steam turbine.
 The superheat degree of the extraction is significantly reduced in this design and the exergy destruction of regenerative heaters is likewise reduced, thereby resulting in an overall improvement in efficiency.
@@
 In this paper, a novel system based on a 1000\,MW double-reheat USC reference system is proposed to realize boiler and regenerative system energy cascade utilization. 
-The novel system realized the reasonable temperature-matching of flue gas, air, extraction steam, and condensate water by using turbine-extraction-heating air preheaters (EAPHs) and LPEs.
+The novel system realized the reasonable temperature-matching of flue gas, air, extraction steam, and condensate water by using turbine-extraction-heating air preheaters (EAPHs) and low temperature economizer (LTEs).
 Specifically, this study included the following tasks: (1) modeling the novel system and reference system with EBSILON® Professional; (2) using exergy analysis to compare both systems' exergy efficiency, exergy destruction distribution, and subsystem performance change; and (3) analyzing both systems' thermal performances under off-design conditions.
@@
 
-\subsection{Proposal for a novel system with EAPHs and LPEs}
+\subsection{Proposal for a novel system with EAPHs and LTEs}
 \label{sub2:prop novel sys}
@@
 Because of the removal of the APH originally installed in the vertical shaft, the flue gas's heat needs to be absorbed by other means.
-As shown in Fig.~\ref{fig:novel_system}, the flue gas at the outlet of the economizer is utilized by four LPEs to heat the condensate and feedwater; these LPEs are correspond with HRH2, HRH4, LRH6, and LRH8, respectively.
-Part of the condensate and feedwater at the inlet of the regenerative heater is sent to the LPE; then the heated water joins with the corresponding regenerative heater's outlet water. 
-Given the acid dew point temperature, the flue gas temperature at the outlet of the last LPE can be set to 95$^\circ$C.
+As shown in Fig.~\ref{fig:novel_system}, the flue gas at the outlet of the economizer is utilized by four LTEs to heat the condensate and feedwater; these LTEs are correspond with HRH2, HRH4, LRH6, and LRH8, respectively.
+Part of the condensate and feedwater at the inlet of the regenerative heater is sent to the LTE; then the heated water joins with the corresponding regenerative heater's outlet water. 
+Given the acid dew point temperature, the flue gas temperature at the outlet of the last LTE can be set to 95$^\circ$C.
 
@@
 Because it is designed based on the reference system, the novel system's main input parameters (such as live steam parameters, first/second reheat steam parameters, and turbine extraction parameters) remain the same as those that are shown in Table~\ref{tab:ref input} and Table~\ref{table:extractions_parameter}.
-According to the experience of engine, the upper temperature differences of the novel system's LPE, AOC and EAPH are settled to 30$^\circ$C, 20$^\circ$C, and 5$^\circ$C. 
+According to the experience of engine, the upper temperature differences of the novel system's LTE, AOC and EAPH are settled to 30$^\circ$C, 20$^\circ$C, and 5$^\circ$C. 
 The details of the model's other main components are given in Table~\ref{table:model_details}.
@@
 \midrule
-Boiler         			& Economizer outlet flue gas temperature = 376\textcelsius \tabularnewline
- 						& Slag temperature = 850\textcelsius \tabularnewline
+Boiler         			& Economizer outlet flue gas temperature = 376$^\circ$C \tabularnewline
+ 						& Slag temperature = 850$^\circ$C \tabularnewline
  						& Combustion efficiency = 0.99\tabularnewline
@@
  						& calculated from the thermal equilibrium diagram\tabularnewline
-Condenser 				& Upper terminal temperature difference = 5\textcelsius \tabularnewline
-Regenerative reheats 	& Upper terminal temperature differences range from -1.7\textcelsius{}  \tabularnewline
- 						& to 2.2\textcelsius, calculated from the thermal equilibrium diagram.\tabularnewline
+Condenser 				& Upper terminal temperature difference = 5$^\circ$C \tabularnewline
+Regenerative reheats 	& Upper terminal temperature differences range from -1.7$^\circ$C{}  \tabularnewline
+ 						& to 2.2$^\circ$C, calculated from the thermal equilibrium diagram.\tabularnewline
 \bottomrule
@@
 As illustrated in Table~\ref{table:extraction_compare}, the mass flow rates of the first, third, fifth, and eighth extractions of the novel system were greater than those of the reference system, and the rest of the extractions except the final two ones were lower then those of the reference system.
-Thus, the impact of system optimization on extraction is twofold: air is heated by extractions, which causes an increase in extractions' mass flow, and the use of LPE can decrease it, so the total extraction mass flow remains nearly unchanged.
+Thus, the impact of system optimization on extraction is twofold: air is heated by extractions, which causes an increase in extractions' mass flow, and the use of LTE can decrease it, so the total extraction mass flow remains nearly unchanged.
 
@@
 
-The regenerative subsystem of the novel system uses LPES connected parallel with EAPH to absorb the economizer's outlet flue heat and eliminate the AOCs originally used to heat feedwater.
-LPE inlet water is heated to the temperature of the corresponding RH outlet temperature.
+The regenerative subsystem of the novel system uses LTES connected parallel with EAPH to absorb the economizer's outlet flue heat and eliminate the AOCs originally used to heat feedwater.
+LTE inlet water is heated to the temperature of the corresponding RH outlet temperature.
 Keeping the extractions' parameters constant, the average heat transfer temperature difference of the RHs changes little.
@@
 It can be seen that the novel system's exergy destruction rate decreased and great changes have taken place in the destruction's distribution.
-Because of the flow-diverting effects of LPEs,the exergy destruction rate of regenerative reheaters and DEA changes from 20.16 MW to 11.303 MW.
+Because of the flow-diverting effects of LTEs,the exergy destruction rate of regenerative reheaters and DEA changes from 20.16 MW to 11.303 MW.
 
-The LPEs exergy destruction rate reaches 10.25 MW, and Fig.~\ref{fig:LPE_exergy_LMDT} shows the LEPs'
-exergy efficiency and heat transfer LMTD.
-As shown in Fig.~\ref{fig:LPE_exergy_LMDT}, the highest efficiency one is LPE1 with 93.50\%, and the lowest efficiency one is LPE4 with 87.44\%. 
-The LPEs' overall exergy efficiency is 91.62\%, which is much higher than that of the flue-air heat transfer of the reference system, and the temperature difference of the LPEs is between 23$^\circ$C and 42$^\circ$C.
+The LTEs exergy destruction rate reaches 10.25 MW, and Fig.~\ref{fig:LPE_exergy_LMDT} shows the LTEs' exergy efficiency and heat transfer LMTD.
+As shown in Fig.~\ref{fig:LPE_exergy_LMDT}, the highest efficiency one is LTE1 with 93.50\%, and the lowest efficiency one is LTE4 with 87.44\%. 
+The LTEs' overall exergy efficiency is 91.62\%, which is much higher than that of the flue-air heat transfer of the reference system, and the temperature difference of the LTEs is between 23$^\circ$C and 42$^\circ$C.
 
@@
 \includegraphics[width=0.6\textwidth]{fig/LPE_exergy_LMTD.png}
-\caption{Exergy efficiency and LMTD of LPEs} 
+\caption{Exergy efficiency and LMTD of LTEs} 
 \label{fig:LPE_exergy_LMDT}
@@
 
-This paper proposed a novel system for a 1000\,MW double-reheat ultra-supercritical unit that uses turbine extractions to preheat air and low-pressure economizers to replace the air preheater originally installed in vertical shaft.
+This paper proposed a novel system for a 1000\,MW double-reheat ultra-supercritical unit that uses turbine extractions to preheat air and low-temperature economizers to replace the air preheater originally installed in vertical shaft.
 Thermodynamic analysis was conducted to reveal the energy-saving effects and thermal performance changes of key components. 
@@
 \nomenclature{USC}{ultra-supercritical}
+\nomenclature{LTE}{low temperature economizer}
 \nomenclature{LPE}{low pressure economizer}

### 2018-03-02 article.tex
提交APEN版本，修改了图片的大小和字号，添加了highlight

@@
 \usepackage{caption} 
-\usepackage{color}%临时添加,
+\usepackage{color}%
 \usepackage{amssymb,hyperref,booktabs,multirow,multicol,ifthen}
@@
 \ifthenelse{\equal{#1}{M}}{\item[\textbf{Mathematical symbols}]}{
-}%几个类别需要几个括号
+}%
 }
@@
 }
-}%几个类别需要几个括号
-}%对应1]
+}%
+}%
 \makenomenclature
@@
 
-\title{A novel 1000\,MW double-reheat ultra supercritical system with turbine-extraction-heated air preheaters and low-temperature economizers}
+\title{A novel 1000\,MW double-reheat ultra-supercritical system with turbine-extraction-heated air preheaters and low-temperature economizers}
 
@@
 \ead{hust\_yt@hust.edu.cn}	
+\author[hust]{Sheng Guo}
 \author[hust]{Yanping Zhang}
@@
 \begin{abstract}
-The double-reheat ultra-supercritical (USC) unit has received significant attention because of its high efficiency and energy-saving effects.
-The optimal design of the USC unit's thermal system is still under consideration, however.
-In this paper, an optimized system for reasonable fluid heat transfer temperature-matching and higher efficiency is proposed .
+The double-reheat ultra-supercritical (USC) coal-fired power unit has received significant attention because of its high efficiency and energy-saving effects.
+The optimal design of the unit's thermal system is still under consideration, however.
+In this paper, an optimized system for reasonable fluid heat transfer temperature-matching and higher efficiency is proposed based on a typical double-reheat USC unit.
 This novel system uses turbine extractions as heat sources for air preheaters and low-temperature economizers to absorb economizer outlet flue gas heat, thereby realizing the joint optimization of the air preheat process and the regenerative system.
@@
 The double-reheat USC unit is a new generation of USC unit that can improve thermal performance when compared with a single reheat unit~\cite{Zhao2017Exergy}. 
-According to~\cite{Zhao2017Exergy}, a double reheat unit with the inlet parameter 30.0\,MPa/600/620/620$^\circ$C improves the heat efficiency by 2.4\%-2.6\% when compared with a commonly used USC unit with the inlet parameter 25.0\,MPa/600/600$^\circ$C.
+According to~\cite{Zhao2017Exergy}, a double-reheat unit with the inlet parameter 30.0\,MPa/600/620/620$^\circ$C improves the heat efficiency by 2.4\%-2.6\% when compared with a commonly used USC unit with the inlet parameter 25.0\,MPa/600/600$^\circ$C.
  The United States built the first double-reheat unit with the main parameter 34.4 MPa/649/566/566$^\circ$C in the 1960s.
@@
 The first low-temperature reheater (Ltfr) and the front-duct economizer (Feco) is arranged in the front duct.
-The second low-temperature reheater (Ltsr) and the back-duct economizer (Beco) is arranged The back duct .
+The second low-temperature reheater (Ltsr) and the back-duct economizer (Beco) is arranged in the back duct.
 The air preheater (APH) is arranged in the vertical shaft.
@@
 It can be seen that most heating surfaces of the boiler are arranged in the furnace, while the horizontal flue and vertical shaft are only equipped with APH.
-This means that the horizontal flue and vertical shaft leave sufficient space for the installation of other equipment.
+This means that the horizontal flue gas duct and vertical shaft have sufficient space for the installation of other system optimization equipment.
 
@@
 Because it is designed based on the reference system, the novel system's main input parameters (such as live steam parameters, first/second reheat steam parameters, and turbine extraction parameters) remain the same as those that are shown in Table~\ref{tab:ref input} and Table~\ref{table:extractions_parameter}.
-According to the experience of engine, the upper temperature differences of the novel system's LTE, AOC and EAPH are settled to 30$^\circ$C, 20$^\circ$C, and 5$^\circ$C. 
+According to the experience of power plant design, the upper temperature differences of the novel system's LTE, AOC and EAPH are settled to 30$^\circ$C, 20$^\circ$C, and 5$^\circ$C. 
 The details of the model's other main components are given in Table~\ref{table:model_details}.
@@
 Condenser 				& Upper terminal temperature difference = 5$^\circ$C \tabularnewline
-Regenerative reheats 	& Upper terminal temperature differences range from -1.7$^\circ$C{}  \tabularnewline
- 						& to 2.2$^\circ$C, calculated from the thermal equilibrium diagram.\tabularnewline
+Regenerative reheats 	& Upper terminal temperature differences range from  \tabularnewline
+ 						& -1.7$^\circ$C{} to 2.2$^\circ$C, calculated from the thermal\tabularnewline
+ 						& equilibrium diagram.\tabularnewline
 \bottomrule
@@
 \multirow{2}{*}{Extractions} & Pressure & Temperature & \multirow{2}{*}{Extractions} & Pressure & Temperature\tabularnewline
- & (bar) & (℃) &  & (bar) & (℃)\tabularnewline
+ & (bar) & ($^\circ$C) &  & (bar) & ($^\circ$C)\tabularnewline
 \midrule
@@
 Air is heated by the EAPHs and AOCs in the novel system from 23$^\circ$C to 363.33$^\circ$C. 
-A majority of the outlet air of EAPH6 is sent to coal pulverizer as primary air, and the rest of the air is heated to 363.33$^\circ$C.
+Part of the outlet air of EAPH6 is sent to coal pulverizer as primary air, and the rest of the air is heated to 363.33$^\circ$C as secondary air.
 
@@
 \centering
-\includegraphics[width=0.6\textwidth]{fig/APH_temper_compare.png}
+\includegraphics[width=0.8\textwidth]{fig/APH_temper_compare.png}
 \caption{T-Q diagram of air preheat subsystems} 
@@
 \centering
-\includegraphics[width=0.6\textwidth]{fig/regenerative_subsys_compare.png}
+\includegraphics[width=0.8\textwidth]{fig/regenerative_subsys_compare.png}
 \caption{Exergy destruction comparison of regenerative subsystems} 
@@
 \centering
-\includegraphics[width=0.6\textwidth]{fig/LPE_exergy_LMTD.png}
+\includegraphics[width=0.8\textwidth]{fig/LPE_exergy_LMTD.png}
 \caption{Exergy efficiency and LMTD of LTEs} 
@@
 \centering
-\includegraphics[width=0.6\textwidth]{fig/partload_efficiency.png}
+\includegraphics[width=0.8\textwidth]{fig/partload_efficiency.png}
 \caption{Exergy efficiency comparison under off-design conditions} 
@@
 As the load decreases from the THA load condition, it can be seen that the load change has the greatest effect on the boiler, while the change in the load condition barely affects the steam turbine.
-When the load is reduced to 40\%THA, the four subsystems of the novel system still have lower exergy destruction rates than those of the reference system.
+When the load is reduced to 40\% THA, the four subsystems of the novel system still have lower exergy destruction rates than those of the reference system.
 However, the exergy-saving effect of these four subsystems decrease, and the exergy destruction rate increase among the other uncalculated components causes the novel system's exergy-saving effects to decrease.
@@
 \centering
-\includegraphics[width=0.6\textwidth]{fig/partload_subsys_exergyrate.png}
+\includegraphics[width=0.8\textwidth]{fig/partload_subsys_exergyrate.png}
 \caption{Difference in subsystems' exergy destruction rates under off-design conditions} 

### 2018-03-03 cover_letter.tex
coverletter 和 对修改回信的latex文件，添加杨涛签名

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Long Lined Cover Letter
% LaTeX Template
% Version 1.0 (1/6/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Matthew J. Miller
% http://www.matthewjmiller.net/howtos/customized-cover-letter-scripts/
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt,stdletter,dateno,sigleft]{newlfm} % Extra options: 'sigleft' for a left-aligned signature, 'stdletternofrom' to remove the from address, 'letterpaper' for US letter paper - consult the newlfm class manual for more options

\usepackage{charter} % Use the Charter font for the document text
\usepackage{changepage}
\usepackage{color}

\usepackage{ amssymb }

%\newsavebox{\Luiuc}\sbox{\Luiuc}{\parbox[b]{1.75in}{\vspace{0.5in}
%\includegraphics[width=1.2\linewidth]{logo.png}}} % Company/institution logo at the top left of the page
%\makeletterhead{Uiuc}{\Lheader{\usebox{\Luiuc}}}

%\newlfmP{sigsize=50pt} % Slightly decrease the height of the signature field
\newlfmP{addrfromphone} % Print a phone number under the sender's address
\newlfmP{addrfromemail} % Print an email address under the sender's address
\PhrPhone{Phone} % Customize the "Telephone" text
\PhrEmail{Email} % Customize the "E-mail" text

%\lthUiuc % Print the company/institution logo

%----------------------------------------------------------------------------------------
%	YOUR NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

 % Name
\signature{\\\includegraphics[width=4cm]{1.png}\\Tao Yang}
\addrfrom{
\today\\[12pt] % Date
1037 Luoyu Road \\ % Address
Wuhan, Hubei, China, 430074
}
\phonefrom{+86 15032905712}
\emailfrom{hust_yt@hust.edu.cn} % Email address

%----------------------------------------------------------------------------------------
%	ADDRESSEE AND GREETING/CLOSING
%----------------------------------------------------------------------------------------
\greetto{Dear editor,} % Greeting text
\closeline{Sincerely yours,} % Closing text

\nameto{$\langle$ Applied Energy$\rangle$} % Addressee of the letter above the to address

\addrto{
$\langle$ A novel 1000\,MW double-reheat ultra-supercritical system with \\
turbine-extraction-heated air preheaters and low-temperature economizers$\rangle$\\ % To address
}

%----------------------------------------------------------------------------------------

\begin{document}
\begin{newlfm}

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------

I enclose a manuscript entitled `A novel 1000 MW double-reheat ultra-supercritical system with turbine-extraction-heated air preheaters and low-temperature economizers'. 
All of the authors agree to the submission of this paper.

This paper belongs to the field of energy system analysis and optimization using exergy analysis method.

The manuscript includes 25 pages, 8 tables, and 10 figures prepared using Latex. 
The latex source files have been upload in a zip file.

We respectfully submit that the following individuals would be suitable peer reviewers based on their expertise in the field:
\\
\\
Inmaculada Arauzo, Universidad de Zaragoza (Spain), E-mail: iarauzo@unizar.es

Danmei Xie, Wuhan University (China), E-mail: dmxie@whu.edu.cn

Daotong Chong, Xi'an Jiao tong University (China),E-mail: dtchong@mail.xjtu.edu.cn
\\
\\

I confirm that I have mentioned all the organizations that found my research in the acknowledgment section of my submission, including grant numbers.
And the manuscript has not been published before nor submitted to another journal for the consideration of publication.

%----------------------------------------------------------------------------------------

\end{newlfm}
\end{document}

### 2018-04-04 article.tex
无改动
引言部分进行了部分修改，添加了几篇参考文献

@@
 \label{sec1:intro}
-Coal is still the main fossil fuel resource for the production of electricity globally, according to~\cite{Ouedraogo2013Energy}. 
-In China, coal–fired power generation accounts for more than 70\% of the total electricity generation and subsequently contributes almost 50\%, 37\%, 33\%, and 55\% to the SO$_X$, NO$_X$, dust, and CO$_X$ emission volumes, respectively~\cite{Zhang2010Analysis}.
+
+By the end of 2017, China's installed capacity of generating units was 1 billion 780 million kilowatts, of which coal-fired units accounted for more than 50\% of the total installed capacity of the country.
+In China, coal–fired power generation accounts for more than 70\% of the total electricity generation and subsequently contributes almost 50\%, 37\%, 33\%, and 55\% to the SO$_X$, NO$_X$, dust, and CO$_X$ emission volumes, respectively~\cite{Zhang2010Analysis} ~\cite{2018}.
 Statistics show that China has been the largest producer and consumer of energy worldwide since 2013~\cite{Petroleum2014BP}. 
-In 2016, Chinese coal production fell by 7.9\% and the price of steam coal increased by over 60\%~\cite{Petroleum2017BP}. 
+In 2016, Chinese coal production fell by 7.9\% and the price of steam coal increased by over 60\%~\cite{2017}. 
 Improving system efficiency and reducing coal consumption remain the primary tasks to be considered in power plant design.
@@
 The layout of the optimization system is presented in Fig.~\ref{fig:novel_system}.
+E1-E10 represent the 1st to 10th extraction of steam turbine.
 
@@
 four additional outer steam coolers (AOC1-AOC4) are installed at the air side outlet of EAPH1.
+The 2nd to 5th extractions are selected as heating sources of AOCs for thier high superheat degree~\cite{Xu2015Optimum,Wang2016}.
+After heating the AOCs, the turbine extractions are sent to corresponding regenerative heaters.
+
+In order to match the extractions temperature and the feedwater temperature, the heating steam of AOC1-AOC4 employ 2nd, 4th, 5th and 3rd extraction respectively.
+
 The air side outlet of EAPH1 is sent to the boiler as secondary air, which has a smaller mass and lower heat capacity compared with the feedwater. 

### 2018-04-20 article.tex
引言部分的修改（未完成）

@@
 
-By the end of 2017, China's installed capacity of generating units was 1 billion 780 million kilowatts, of which coal-fired units accounted for more than 50\% of the total installed capacity of the country.
-In China, coal–fired power generation accounts for more than 70\% of the total electricity generation and subsequently contributes almost 50\%, 37\%, 33\%, and 55\% to the SO$_X$, NO$_X$, dust, and CO$_X$ emission volumes, respectively~\cite{Zhang2010Analysis} ~\cite{2018}.
-Statistics show that China has been the largest producer and consumer of energy worldwide since 2013~\cite{Petroleum2014BP}. 
-In 2016, Chinese coal production fell by 7.9\% and the price of steam coal increased by over 60\%~\cite{2017}. 
+By the end of 2017, China's installed capacity of generating units was 1,780 million kW, of which coal-fired units accounted for more than 50\% of the total installed capacity~\cite{2018}, and coal–fired power generation accounts for almost 50\%, 37\%, 33\%, and 55\% to the SO$_X$, NO$_X$, dust, and CO$_X$ emission volumes, respectively, in China~\cite{Zhang2010Analysis}.
+In 2016, Chinese steam coal price increased by over 60\%~\cite{2017} which caused a great burden on coal-fired power generation enterprises. 
 Improving system efficiency and reducing coal consumption remain the primary tasks to be considered in power plant design.
-Nowadays ultra-supercritical (USC) power plants with large capacities and high parameters are considered to be feasible ways to save energy; as such, their usage has spread rapidly worldwide.
-The double-reheat USC unit is a new generation of USC unit that can improve thermal performance when compared with a single reheat unit~\cite{Zhao2017Exergy}. 
-According to~\cite{Zhao2017Exergy}, a double-reheat unit with the inlet parameter 30.0\,MPa/600/620/620$^\circ$C improves the heat efficiency by 2.4\%-2.6\% when compared with a commonly used USC unit with the inlet parameter 25.0\,MPa/600/600$^\circ$C.
- The United States built the first double-reheat unit with the main parameter 34.4 MPa/649/566/566$^\circ$C in the 1960s.
- Two 700 MW double-reheat USC units were put into operation in Japan in 1990. 
- The process of building five double-reheat USC units began in China in 2012, and three of these units were put into operation in 2015.
- Over the past few decades, double-reheat USC units have received increasing attention due to their rapid development worldwide.
 
-Though the high live steam pressure and temperature of the USC unit improve its efficiency, there are still some imperfections that limit the improvement of the unit's performance. 
-In order to perform an in-depth analysis of the system, Zhao Z et al.~\cite{Zhao2017Exergy} studied the exergy distribution system for a 1000\,MW double-reheat USC power plant and determined the main causes of exergy destruction on the steam turbine.
-Rashidi et al.~\cite{Rashidi2014Thermodynamic} performed a thermodynamic analysis of a double-reheat steam power plant.
-According to Ref.~\cite{Wu2014Component}, component- and process-based exergy evaluations were performed on a coal-fired power plant in China, thereby helping researchers to identify energy-saving strategies.
-It was pointed out that the exergy destruction in the heat transfer process accounts for the largest proportion of exergy destruction overall.
+% Nowadays ultra-supercritical (USC) power plants with large capacities and high parameters are considered to be feasible ways to save energy; as such, their usage has spread rapidly worldwide.
+% The double-reheat USC unit is a new generation of USC unit that can improve thermal performance when compared with a single reheat unit~\cite{Zhao2017Exergy}. 
+% According to~\cite{Zhao2017Exergy}, a double-reheat unit with the inlet parameter 30.0\,MPa/600/620/620$^\circ$C improves the heat efficiency by 2.4\%-2.6\% when compared with a commonly used USC unit with the inlet parameter 25.0\,MPa/600/600$^\circ$C.
+%  The United States built the first double-reheat unit with the main parameter 34.4 MPa/649/566/566$^\circ$C in the 1960s.
+%  Two 700 MW double-reheat USC units were put into operation in Japan in 1990. 
+%  The process of building five double-reheat USC units began in China in 2012, and three of these units were put into operation in 2015.
+%  Over the past few decades, double-reheat USC units have received increasing attention due to their rapid development worldwide.
 
-Compared with the common USC system, the double-reheat system has some typical problems, such as the double-reheat ratio that is chosen and the high superheat degree of the first several extractions.
-Other common problems include the high boiler exhaust temperature, which leads to unreasonable energy-level matching and significant exergy destruction.
+ 为了能够提高热电厂的循环效率，研究人员不断对火电厂系统进行改进优化。
+ Sven Kjaer et al.~\cite{Kjaer2010A} considered that those investigations can be grouped along three side tracks, i.e.
+the temperature track, which employs higher live steam parameters such as 30-35 MPa, above 700$^\circ$C in the future~\cite{Bugge2014High}, the component track, which improves the efficiency of key equipment such as boiler~\cite{Rosen2008Improving} and turbine~\cite{Zhang2016Optimization}, and the Carnot track, which makes efforts to reduce the defection of the real cycle of the power plant~\cite{Liu2018}.
 
-To identify reasonable reheat parameters, Zhou et al.~\cite{Zhou2016Parametric} carried out a parametric analysis and system optimization of double-reheat ultra-supercritical power plants based on exergy analysis and economic analysis.
-The results showed that reasonable reheat parameters and reheat stage numbers can improve the double-reheat system's performance.
-
-To reduce the superheat degree of the extractions, Xu et al.~\cite{Xu2015Optimum} investigated the thermal performance of the steam and water cycle with a single reheat after the installation of an additional outer steam cooler (AOC).
-The results showed that the AOC is an effective method of reducing the superheat degree and improving the efficiency of the unit.
-Li et al.~\cite{Li2014Thermodynamic} proposed a system that uses ten-stage extractions and two outer steam coolers. 
-The results of the thermodynamic and Technical-economic analyses showed that this system can lower the cost of electricity to 55.89 USD/MWh.
-In addition, Kjaer~\cite{Kjaer2010A} proposed a regenerative steam turbine for utilizing the superheat degree of the extractions.
-In this design, part of the extraction from the turbine high pressure cylinder enters the additional regenerative steam turbine rather than the regenerative heater.
-Extractions from the turbine intermediate pressure cylinder are replaced by those from the regenerative steam turbine.
-The superheat degree of the extraction is significantly reduced in this design and the exergy destruction of regenerative heaters is likewise reduced, thereby resulting in an overall improvement in efficiency.
+对锅炉烟气余热的利用一直以来都是系统优化的重点。近年来部分学者提出的利用锅炉烟气加热给水方法提高系统效率，在该思路的指导下多种系统形式被提出：
 
@@
 
-Given that boiler design and thermal system design belong to different research areas, boiler design is studied as a whole apart from the joint optimization of the boiler heat transfer process and regenerative process.
+二次再热也已经作为一种有效提高系统效率的方式被深入研究并进行深入分析：
+
+To identify reasonable reheat parameters, Zhou et al.~\cite{Zhou2016Parametric} carried out a parametric analysis and system optimization of double-reheat ultra-supercritical power plants based on exergy analysis and economic analysis.
+The results showed that reasonable reheat parameters and reheat stage numbers can improve the double-reheat system's performance.
+
+To reduce the superheat degree of the extractions, Xu et al.~\cite{Xu2015Optimum} investigated the thermal performance of the steam and water cycle with a single reheat after the installation of an additional outer steam cooler (AOC).
+The results showed that the AOC is an effective method of reducing the superheat degree and improving the efficiency of the unit.
+Li et al.~\cite{Li2014Thermodynamic} proposed a system that uses ten-stage extractions and two outer steam coolers. 
+The results of the thermodynamic and Technical-economic analyses showed that this system can lower the cost of electricity to 55.89 USD/MWh.
+In addition, Kjaer~\cite{Kjaer2010A} proposed a regenerative steam turbine for utilizing the superheat degree of the extractions.
+In this design, part of the extraction from the turbine high pressure cylinder enters the additional regenerative steam turbine rather than the regenerative heater.
+Extractions from the turbine intermediate pressure cylinder are replaced by those from the regenerative steam turbine.
+The superheat degree of the extraction is significantly reduced in this design and the exergy destruction of regenerative heaters is likewise reduced, thereby resulting in an overall improvement in efficiency.
+
+% Compared with the common USC system, the double-reheat system has some typical problems, such as the double-reheat ratio that is chosen and the high superheat degree of the first several extractions.
+% Other common problems include the high boiler exhaust temperature, which leads to unreasonable energy-level matching and significant exergy destruction.
+
+% Though the high live steam pressure and temperature of the USC unit improve its efficiency, there are still some imperfections that limit the improvement of the unit's performance. 
+为了能够对系统进行更加进一步的优化，用分析的方法被应用到热力系统优化中
+In order to perform an in-depth analysis of the system, Zhao Z et al.~\cite{Zhao2017Exergy} studied the exergy distribution system for a 1000\,MW double-reheat USC power plant and determined the main causes of exergy destruction on the steam turbine.
+Rashidi et al.~\cite{Rashidi2014Thermodynamic} performed a thermodynamic analysis of a double-reheat steam power plant.
+According to Ref.~\cite{Wu2014Component}, component- and process-based exergy evaluations were performed on a coal-fired power plant in China, thereby helping researchers to identify energy-saving strategies.
+It was pointed out that the exergy destruction in the heat transfer process accounts for the largest proportion of exergy destruction overall.
+
+现有研究往往关注与烟气余热温度与给水温度相匹配，并没有对锅炉中原有受热面进行优化。而通过火用分析，热力系统中锅炉损失占总用损失的70%，空预器的损失和整个回热系统的损失相当。
+通过实现空气、汽轮机抽汽、锅炉省煤器出口烟气和冷凝水温度相匹配，够降低低锅炉用损失，提高系统效率。
+这一点对于二次再热系统尤为重要，随着近年来二次再热机组在世界范围研究和投入使用，其高效收到的广泛的认可，但是由于再热后抽汽的过热度提高，导致抽汽和给水温度不匹配造成的用损失也更加显著。
+所以在二次再热机组上进行多工质温度匹配分析对机组节能更具有潜力。
+
+% Given that boiler design and thermal system design belong to different research areas, boiler design is studied as a whole apart from the joint optimization of the boiler heat transfer process and regenerative process.
 

### 2018-04-25 article.tex
继续修改引言部分

@@
 
- 为了能够提高热电厂的循环效率，研究人员不断对火电厂系统进行改进优化。
+In order to improve the power generation efficiency of thermal power plants, researchers have carried out a number of investigations.
 Sven Kjaer et al.~\cite{Kjaer2010A} considered that those investigations can be grouped along three side tracks, i.e.
@@
 
-对锅炉烟气余热的利用一直以来都是系统优化的重点。近年来部分学者提出的利用锅炉烟气加热给水方法提高系统效率，在该思路的指导下多种系统形式被提出：
+Among the methods of optimzing the thermal cycle of power plant, the double-reheat USC unit is attractiong increasing number of attention and developing rapidly worldwide. 
+The double-reheat USC unit is a new generation of USC unit that can improve thermal performance when compared with a single reheat unit. 
+According to~\cite{Zhao2017Exergy}, a double-reheat unit with the inlet parameter 30.0\,MPa/600/620/620$^\circ$C improves the heat efficiency by 2.4\%-2.6\% when compared with a commonly used USC unit with the inlet parameter 25.0\,MPa/600/600$^\circ$C.
+The United States built the first double-reheat unit with the main parameter 34.4 MPa/649/566/566$^\circ$C in the 1960s.
+Two 700 MW double-reheat USC units were put into operation in Japan in 1990. 
+The process of building five double-reheat USC units began in China in 2012, and three of these units were put into operation in 2015.
+
+Although the double-reheat USC unit can improve the system efficiency, it also bring some other problems, such as the superheat degree of extractions after first- and second- reheater are extremly high which cause high exergy lose of regenerative heaters.
+And the increased volume flow after second-reheater needs extra-large low-pressure cylinder~\cite{nicol2015application}.
+
+Liu et al.~\cite{Liu2017} investigated a 660 MW double-reheat unit and calculated the coal consumption decrease if the overheats of No.5 to No.10 extractions could be recovered.
+Wang et al.~\cite{Wang2016} studied 1000MW double-reheat USC system adopting outer steam coolers to utilize the superheat of extraction steam and the influence of different extraction schemes on system efficiency.
+% Zhou et al.~\cite{Zhou2016Parametric} carried out a parametric analysis and system optimization of double-reheat ultra-supercritical power plants based on exergy analysis and economic analysis. 
+% The results showed that reasonable reheat parameters and reheat stage numbers can improve the double-reheat system's performance.
+% Xu et al.~\cite{Xu2015Optimum} investigated the thermal performance of the steam and water cycle with a double reheat after the installation of an additional outer steam cooler (AOC).
+The results showed that the AOC is an effective method of reducing the superheat degree and improving the efficiency of the unit.
+Li et al.~\cite{Li2014Thermodynamic} proposed a system that uses ten-stage extractions and two outer steam coolers. 
+The results of the thermodynamic and technical-economic analyses showed that this system can lower the cost of electricity to 55.89 USD/MWh.
+In addition, Kjaer~\cite{Kjaer2010A} proposed a regenerative steam turbine for utilizing the superheat degree of the extractions.
+In this design, part of the extraction from the turbine high pressure cylinder enters the additional regenerative steam turbine rather than the regenerative heater.
+Extractions from the turbine intermediate pressure cylinder are replaced by those from the regenerative steam turbine.
+The superheat degree of the extraction is significantly reduced in this design and the exergy destruction of regenerative heaters is likewise reduced, thereby resulting in an overall improvement in efficiency.
+Xu et al.~\cite{Xu2015Optimum} compared two superheat utilization systems, one is with additional outer steam cooler (AOC) and the other one is with regenerative steam turbine.
+The results showed that the system with regenerative steam turbine had a better techno-economic performance.
+
+%虽然能够对蒸汽过热度进行利用，但是回热系统中换热器温差依旧很大。而利用锅炉烟气加热给水能够减少回热系统的换热温差
+
+%对锅炉烟气余热的利用一直以来都是系统优化的重点。近年来部分学者提出的利用锅炉烟气加热给水方法提高系统效率，在该思路的指导下多种系统形式被提出：
 
@@
 
-二次再热也已经作为一种有效提高系统效率的方式被深入研究并进行深入分析：
-
-To identify reasonable reheat parameters, Zhou et al.~\cite{Zhou2016Parametric} carried out a parametric analysis and system optimization of double-reheat ultra-supercritical power plants based on exergy analysis and economic analysis.
-The results showed that reasonable reheat parameters and reheat stage numbers can improve the double-reheat system's performance.
-
-To reduce the superheat degree of the extractions, Xu et al.~\cite{Xu2015Optimum} investigated the thermal performance of the steam and water cycle with a single reheat after the installation of an additional outer steam cooler (AOC).
-The results showed that the AOC is an effective method of reducing the superheat degree and improving the efficiency of the unit.
-Li et al.~\cite{Li2014Thermodynamic} proposed a system that uses ten-stage extractions and two outer steam coolers. 
-The results of the thermodynamic and Technical-economic analyses showed that this system can lower the cost of electricity to 55.89 USD/MWh.
-In addition, Kjaer~\cite{Kjaer2010A} proposed a regenerative steam turbine for utilizing the superheat degree of the extractions.
-In this design, part of the extraction from the turbine high pressure cylinder enters the additional regenerative steam turbine rather than the regenerative heater.
-Extractions from the turbine intermediate pressure cylinder are replaced by those from the regenerative steam turbine.
-The superheat degree of the extraction is significantly reduced in this design and the exergy destruction of regenerative heaters is likewise reduced, thereby resulting in an overall improvement in efficiency.
-
-% Compared with the common USC system, the double-reheat system has some typical problems, such as the double-reheat ratio that is chosen and the high superheat degree of the first several extractions.
-% Other common problems include the high boiler exhaust temperature, which leads to unreasonable energy-level matching and significant exergy destruction.
-
-% Though the high live steam pressure and temperature of the USC unit improve its efficiency, there are still some imperfections that limit the improvement of the unit's performance. 
+现有研究往往关注与烟气余热温度与给水温度相匹配，并没有对锅炉中原有受热面进行优化。
 为了能够对系统进行更加进一步的优化，用分析的方法被应用到热力系统优化中
@@
 
-现有研究往往关注与烟气余热温度与给水温度相匹配，并没有对锅炉中原有受热面进行优化。而通过火用分析，热力系统中锅炉损失占总用损失的70%，空预器的损失和整个回热系统的损失相当。
+而通过火用分析，热力系统中锅炉损失占总用损失的70%，而空预器的损失和整个回热系统的损失相当。
+降低空预器的用损失是实现系统用效率提升的重点
 通过实现空气、汽轮机抽汽、锅炉省煤器出口烟气和冷凝水温度相匹配，够降低低锅炉用损失，提高系统效率。
-这一点对于二次再热系统尤为重要，随着近年来二次再热机组在世界范围研究和投入使用，其高效收到的广泛的认可，但是由于再热后抽汽的过热度提高，导致抽汽和给水温度不匹配造成的用损失也更加显著。
+这一点对于二次再热系统尤为重要，
 所以在二次再热机组上进行多工质温度匹配分析对机组节能更具有潜力。
+
+% Compared with the common USC system, the double-reheat system has some typical problems, such as the double-reheat ratio that is chosen and the high superheat degree of the first several extractions.
+% Other common problems include the high boiler exhaust temperature, which leads to unreasonable energy-level matching and significant exergy destruction.
+
+% Though the high live steam pressure and temperature of the USC unit improve its efficiency, there are still some imperfections that limit the improvement of the unit's performance.
 

### 2018-04-25 article.tex
基本完成引言部分的修改

@@
 
-% Nowadays ultra-supercritical (USC) power plants with large capacities and high parameters are considered to be feasible ways to save energy; as such, their usage has spread rapidly worldwide.
-% The double-reheat USC unit is a new generation of USC unit that can improve thermal performance when compared with a single reheat unit~\cite{Zhao2017Exergy}. 
-% According to~\cite{Zhao2017Exergy}, a double-reheat unit with the inlet parameter 30.0\,MPa/600/620/620$^\circ$C improves the heat efficiency by 2.4\%-2.6\% when compared with a commonly used USC unit with the inlet parameter 25.0\,MPa/600/600$^\circ$C.
-%  The United States built the first double-reheat unit with the main parameter 34.4 MPa/649/566/566$^\circ$C in the 1960s.
-%  Two 700 MW double-reheat USC units were put into operation in Japan in 1990. 
-%  The process of building five double-reheat USC units began in China in 2012, and three of these units were put into operation in 2015.
-%  Over the past few decades, double-reheat USC units have received increasing attention due to their rapid development worldwide.
-
 In order to improve the power generation efficiency of thermal power plants, researchers have carried out a number of investigations.
@@
 Wang et al.~\cite{Wang2016} studied 1000MW double-reheat USC system adopting outer steam coolers to utilize the superheat of extraction steam and the influence of different extraction schemes on system efficiency.
-% Zhou et al.~\cite{Zhou2016Parametric} carried out a parametric analysis and system optimization of double-reheat ultra-supercritical power plants based on exergy analysis and economic analysis. 
-% The results showed that reasonable reheat parameters and reheat stage numbers can improve the double-reheat system's performance.
-% Xu et al.~\cite{Xu2015Optimum} investigated the thermal performance of the steam and water cycle with a double reheat after the installation of an additional outer steam cooler (AOC).
 The results showed that the AOC is an effective method of reducing the superheat degree and improving the efficiency of the unit.
@@
 The results showed that the system with regenerative steam turbine had a better techno-economic performance.
+Although the above research can make use of extractions' high superheat degree, the loss in the regenerative subsystem is still very large.
 
-%虽然能够对蒸汽过热度进行利用，但是回热系统中换热器温差依旧很大。而利用锅炉烟气加热给水能够减少回热系统的换热温差
-
-%对锅炉烟气余热的利用一直以来都是系统优化的重点。近年来部分学者提出的利用锅炉烟气加热给水方法提高系统效率，在该思路的指导下多种系统形式被提出：
-
-To reuse the energy of the exhaust flue gas, Xu et al.~\cite{Xu2013Techno} proposed a low-pressure economizer (LPE) based on data compiled from some typical 1000\,MW power generation units in China. 
+In order to reduce the loss of the regenerative subsystem and use the heat of the boiler flue gas, the method of heating feed-water by boiler flue gas is proposed to improve the efficiency of the thermal system.
+Under the guidance of this idea, many kinds of system forms have been proposed.
+Xu et al.~\cite{Xu2013Techno} proposed a low-pressure economizer (LPE) based on data compiled from some typical 1000\,MW power generation units in China. 
 Four possible arrangements for LPE installation were proposed and their energy-saving effects were compared.
@@
 It was found that the SCE consumption was reduced by 6.7\,g/kWh.
-
 The installation of an LPE also has some  other benefits, such as improvements in electrostatic precipitator collection efficiency~\cite{Li2016Low}.
 
-现有研究往往关注与烟气余热温度与给水温度相匹配，并没有对锅炉中原有受热面进行优化。
-为了能够对系统进行更加进一步的优化，用分析的方法被应用到热力系统优化中
-In order to perform an in-depth analysis of the system, Zhao Z et al.~\cite{Zhao2017Exergy} studied the exergy distribution system for a 1000\,MW double-reheat USC power plant and determined the main causes of exergy destruction on the steam turbine.
+The existing research of boiler flue gas heating feedwater has realized the matching of flue gas temperature and feedwater temperature.
+In order to further optimize the system, the exergy analytical method is applied to the double reheat USC system by some researchers.
+Zhao Z et al.~\cite{Zhao2017Exergy} studied the exergy distribution system for a 1000\,MW double-reheat USC power plant and determined the main causes of exergy destruction on the steam turbine.
 Rashidi et al.~\cite{Rashidi2014Thermodynamic} performed a thermodynamic analysis of a double-reheat steam power plant.
@@
 It was pointed out that the exergy destruction in the heat transfer process accounts for the largest proportion of exergy destruction overall.
+The largest part of the exergy loss is boiler, and the exergy loss of boiler's air preheater is equivalent to that of the whole regenerative subsystem.
+Reducing the loss of air preheater is the key to improve the system's efficiency.
 
-而通过火用分析，热力系统中锅炉损失占总用损失的70%，而空预器的损失和整个回热系统的损失相当。
-降低空预器的用损失是实现系统用效率提升的重点
-通过实现空气、汽轮机抽汽、锅炉省煤器出口烟气和冷凝水温度相匹配，够降低低锅炉用损失，提高系统效率。
-这一点对于二次再热系统尤为重要，
-所以在二次再热机组上进行多工质温度匹配分析对机组节能更具有潜力。
-
-% Compared with the common USC system, the double-reheat system has some typical problems, such as the double-reheat ratio that is chosen and the high superheat degree of the first several extractions.
-% Other common problems include the high boiler exhaust temperature, which leads to unreasonable energy-level matching and significant exergy destruction.
-
-% Though the high live steam pressure and temperature of the USC unit improve its efficiency, there are still some imperfections that limit the improvement of the unit's performance.
-
-% Given that boiler design and thermal system design belong to different research areas, boiler design is studied as a whole apart from the joint optimization of the boiler heat transfer process and regenerative process.
-
-In this paper, a novel system based on a 1000\,MW double-reheat USC reference system is proposed to realize boiler and regenerative system energy cascade utilization. 
+In this paper, the heat exchanging temperature match of air, turbine extractions, boiler economizer outlet flue gas and feedwater was fist proposed based on the existing researchof boiler flue gas heating feedwater, which could reduce the exergy loss of boiler and improve system efficiency.
+This is remarkable effect for the double reheat thermal system. 
+A novel system based on a 1000\,MW double-reheat USC reference system is proposed to realize boiler and regenerative system energy cascade utilization. 
 The novel system realized the reasonable temperature-matching of flue gas, air, extraction steam, and condensate water by using turbine-extraction-heating air preheaters (EAPHs) and low temperature economizer (LTEs).

### 2018-05-04 article.tex
完成对引言部分的修改，继续提交版本

@@
 The United States built the first double-reheat unit with the main parameter 34.4 MPa/649/566/566$^\circ$C in the 1960s.
-Two 700 MW double-reheat USC units were put into operation in Japan in 1990. 
+Two 700\,MW double-reheat USC units were put into operation in Japan in 1990. 
 The process of building five double-reheat USC units began in China in 2012, and three of these units were put into operation in 2015.
@@
 
-Liu et al.~\cite{Liu2017} investigated a 660 MW double-reheat unit and calculated the coal consumption decrease if the overheats of No.5 to No.10 extractions could be recovered.
-Wang et al.~\cite{Wang2016} studied 1000MW double-reheat USC system adopting outer steam coolers to utilize the superheat of extraction steam and the influence of different extraction schemes on system efficiency.
-The results showed that the AOC is an effective method of reducing the superheat degree and improving the efficiency of the unit.
-Li et al.~\cite{Li2014Thermodynamic} proposed a system that uses ten-stage extractions and two outer steam coolers. 
+Liu et al.~\cite{Liu2017} investigated a 660\,MW double-reheat unit and calculated the coal consumption decrease if the overheats of No.5 to No.10 extractions could be recovered.
+Wang et al.~\cite{Wang2016} studied 1000\,MW double-reheat USC system adopting outer steam coolers to utilize the superheat of extraction steam and the influence of different extraction schemes on system efficiency.
+The results showed that the  outer steam cooler (AOC) is an effective method of reducing the superheat degree and improving the efficiency of the unit.
+Li et al.~\cite{Li2014Thermodynamic} proposed a system that used ten-stage extractions and two AOCs. 
 The results of the thermodynamic and technical-economic analyses showed that this system can lower the cost of electricity to 55.89 USD/MWh.
@@
 Extractions from the turbine intermediate pressure cylinder are replaced by those from the regenerative steam turbine.
-The superheat degree of the extraction is significantly reduced in this design and the exergy destruction of regenerative heaters is likewise reduced, thereby resulting in an overall improvement in efficiency.
-Xu et al.~\cite{Xu2015Optimum} compared two superheat utilization systems, one is with additional outer steam cooler (AOC) and the other one is with regenerative steam turbine.
+The superheat degree of the extraction was significantly reduced in this design and the exergy destruction of regenerative heaters was likewise reduced, thereby resulting in an overall improvement in efficiency.
+Xu et al.~\cite{Xu2015Optimum} compared two superheat utilization systems, one was with additional AOCs and the other one was with regenerative steam turbine.
 The results showed that the system with regenerative steam turbine had a better techno-economic performance.
@@
 In order to further optimize the system, the exergy analytical method is applied to the double reheat USC system by some researchers.
-Zhao Z et al.~\cite{Zhao2017Exergy} studied the exergy distribution system for a 1000\,MW double-reheat USC power plant and determined the main causes of exergy destruction on the steam turbine.
+Zhao et al.~\cite{Zhao2017Exergy} studied the exergy distribution system for a 1000\,MW double-reheat USC power plant and determined the main causes of exergy destruction on the steam turbine.
 Rashidi et al.~\cite{Rashidi2014Thermodynamic} performed a thermodynamic analysis of a double-reheat steam power plant.
@@
 
-In this paper, the heat exchanging temperature match of air, turbine extractions, boiler economizer outlet flue gas and feedwater was fist proposed based on the existing researchof boiler flue gas heating feedwater, which could reduce the exergy loss of boiler and improve system efficiency.
-This is remarkable effect for the double reheat thermal system. 
+In this paper, the temperature match of air, turbine extractions, boiler economizer outlet flue gas and feedwater was fist proposed based on the existing research of boiler flue gas heating feedwater, which could reduce the exergy loss of boiler and much more effective for the double reheat thermal system.
 A novel system based on a 1000\,MW double-reheat USC reference system is proposed to realize boiler and regenerative system energy cascade utilization. 

### 2019-03-18 article.tex
修改锅炉设计文件

@@
 Furthermore, the novel system increased the temperature of secondary air and reduced the overall superheat degree of several extractions.
-Theoretically, with an overall exergy efficiency of 48.73\%, the novel system can reduce standard coal equivalent consumption by nearly 5.5\,g/kWh under the turbine heat acceptance load if the temperature of the flue gas entering the electrostatic precipitator is set to 95$^\circ$C.
+Theoretically, with an overall exergy efficiency of 48.73\%, the novel system can reduce standard coal equivalent consumption by nearly 5.5\,g/kWh under the turbine heat acceptance load.
 Moreover, the novel system has advantages for coal-saving under the partial load condition.
@@
 Reducing the loss of air preheater is the key to improve the system's efficiency.
+
+In recent years, some scholars have researched the possibility of using turbine extractions to heat the air of the boiler in the system.
+
+Fan et al.~\cite{Fan2018}  optimized a 1000MW double-reheat unit system. 
+A novel cycle with nine-stage air heaters are arranged on the steam pipelines between the turbine and regenerative heater is designed, and set the low-temperature economizer at the position of the original tail flue air preheater.
+By performing thermodynamic and thermal economic analysis, cycle net efficiency is increased by 0.61~\%, and the system investment payback period has reached 15 years.
+
+Li et al.~\cite{Liu2018} utilized turbine extractions to heat air in the optimization of a 1000 MW single reheat system. 
+The Optimized system power generation efficiency achieves 48.35~\%, which is 1.27~\% points higher than that of reference unit.
+
+The research results show that the use of turbine extractions to heat the air can significantly reduce the air temperature difference between the air preheater, increase the feed water temperature and secondary air temperature, and improve system efficiency.
+
+At present, the system optimization scheme using turbine extractions heating air adopts the method of setting a  parallel low-temperature economizer at the position of the original air preheater to utilize the waste heat of the tail flue.
+In this scheme, the introduction of a high-pressure condensate pump increases the complexity of the system, which greatly increases the initial investment and maintenance costs, and also increases the system power consumption and reduces the system economy.
+
+It is necessary to optimize the feedwater heating system using waste heat from the tail flue without the additional high-pressure condensate pump.
 
@@
 Part of the condensate and feedwater at the inlet of the regenerative heater is sent to the LTE; then the heated water joins with the corresponding regenerative heater's outlet water. 
-Given the acid dew point temperature, the flue gas temperature at the outlet of the last LTE can be set to 95$^\circ$C.
+Given the acid dew point temperature, the flue gas temperature at the outlet of the last LTE can be set to 117$^\circ$C.
 
@@
 \item The pips' complexity and the installation difficulty of the novel system's equipment is not taken into consideration.
+\item Both of the reference and novel system's boiler exhaust gas temperature is set to be 117$^\circ$C.
 \end{enumerate}
